---
title: "2_16SmiRNAs_stats"
author: "Jessica A. Dozois"
date: "2024-04-25"
output: html_document
---
#Loading librairies
```{r librairies}
install.packages("pacman")
pacman::p_load(data.table,ggplot2,dplyr,vegan,ggrepel,here,writexl,devtools)
```

#Importation
Importing abundance data frame and mapping file.
```{r Importation}
ASV_df<-read.table(file=here("Raw_Data","feature_table_filt_combi.tsv"), header=T, sep="\t", comment.char = "", check.names = F) #8703 obs 277 variables
ASV_df$`#FEATURE_ID` <- paste0("ASV#",ASV_df$`#FEATURE_ID`)
rownames(ASV_df)<-ASV_df$`#FEATURE_ID` # Feature ID as row names
ASV_df<-ASV_df[,-1] #removing the Feature Id column
ASV_df2<-ASV_df[!grepl('Chloroplast', ASV_df$taxonomy),]#8558 obs 276 variables #remove Chloroplasts
ASV_df3<-ASV_df2[!grepl('Mitochondria', ASV_df2$taxonomy),]##8449 obs 276 variables variables #remove Mitochondria
ASV_df4<-ASV_df3[!grepl('Eukaryota', ASV_df3$taxonomy),]##8440 obs 276 variables variables #remove Eukaryotes


#Select only samples from the in vitro experiment
ASV_df5 <- ASV_df4[, !grepl('_L001', names(ASV_df4)), drop = FALSE]
#8440 obs 171 variables
#removing taxonomy column
ASV_df_notaxo <- ASV_df5[,c(1:170)]
tax<-ASV_df5%>%select("taxonomy")
#Remove absent taxa
ASVdf6<-ASV_df_notaxo[!rowSums(ASV_df_notaxo[])==0,] # 93 obs 170 variables

# Merge taxonomy data with ASV_df based on common_id
ASVdf_tax <- merge(ASVdf6, tax, by = "row.names", all.x = TRUE) #93 obs 172 variables
rownames(ASVdf_tax)<-ASVdf_tax$Row.names
ASVdf_tax<-ASVdf_tax[,-1]

mapping_df<-read.table(file=here("Raw_Data","mapping_file.tsv"), row.names=1, header=T, sep="\t", comment.char = "", check.names = F) #170 obs. 5 variables 

taxa<-ASVdf_tax%>%select("taxonomy")
```

#Creating folders
```{r Creating folders}
dir.create("Output")
dir.create(file.path("Output","Permanova"),recursive = T)
```

#Hellinger transformation and subsetting mix miRNAs
Hellinger transformation on the abundance data frame. To transform this data it is important to transpose(rotate) the data frame.
```{r Hellinger and subsetting}
rotate_asv_df <- t(ASV_df_notaxo)
rotate_asv_df <- decostand(rotate_asv_df, method="hellinger")
  
#Subset by dose
#Exposure to all five miRNAs
map_all5<- mapping_df[mapping_df$miRNA == "all5", ] #80 obs 5 variables
all5samples<- row.names(map_all5)
all5_df<-ASV_df_notaxo[ , (names(ASV_df_notaxo) %in% all5samples)]
rotate_all5 <- t(all5_df)
rotate_all5 <- decostand(rotate_all5, method="hellinger")
```

#Hellinger and subsetting single miRNA
```{r Hellinger and subsetting}
#Exposure to a single miRNA
map2uM<-mapping_df[mapping_df$Dose == "2", ] #90 obs 5 variables
samples_2uM<- row.names(map2uM)
df_2uM<-ASV_df_notaxo[ , (names(ASV_df_notaxo) %in% samples_2uM)]
df_2uM<-df_2uM[rowSums(df_2uM[])>0,]#52 obs 5 variables
rotate_2uM <- t(df_2uM)
rotate_2uM <- decostand(rotate_2uM, method="hellinger")

```


#PERMANOVA
```{r PERMANOVA}
set.seed(11) #fixes the permutation round

#All five
#Betadisper was performed and is OK
permanova_all5<- adonis2(rotate_all5~N_Source*Treatment,data=map_all5, permutations = 999, method="euclidean",by="terms")
permanova_all5
#Treatment 0.011**
#N_Source:Treatment 0.013 **



#Single_miRNAs
#Betadisper was performed and is OK for Treatment and miRNA but not N_source
permanova2uM<- adonis2(rotate_2uM~Treatment*miRNA*N_Source,data=map2uM,permutations = 999, method="euclidean",by="terms")
permanova2uM #N_source 0.001 ***

```

#Permanava results to excel
```{r}
#Combining row names to each PERMANOVA result data frame
all5miRNAs<-cbind(" "=rownames(permanova_all5), permanova_all5)
all2uM<-cbind(" "=rownames(permanova2uM), permanova2uM)
sheets <- list("all10uM"= all5miRNAs,"all2uM"= all2uM)
write_xlsx(sheets, file.path("Output","Permanova","16S_miRNAs_PERMANOVA.xlsx"))

```
