---
title: "3_PCA-16SmiRNAs"
author: "Jessica A. Dozois"
date: '2023-10-21'
output: html_document
---

#Loading librairies
```{r librairies}
install.packages("pacman")
pacman::p_load(data.table,ggplot2,dplyr,vegan,ggrepel,here,tidyr,ggpubr,ggh4x,reshape2, stringr)
```

#Creating a folder
```{r}
dir.create(file.path("Output","Ordination"),recursive = T)
```


#Importation
Importing abundance data frame and mapping file.
```{r Importation}
ASV_df<-read.table(file=here("Raw_Data","feature_table_filt_combi.tsv"), header=T, sep="\t", comment.char = "", check.names = F) #8703 obs 277 variables
ASV_df$`#FEATURE_ID` <- paste0("ASV#",ASV_df$`#FEATURE_ID`)
rownames(ASV_df)<-ASV_df$`#FEATURE_ID` # Feature ID as row names
ASV_df<-ASV_df[,-1] #removing the Feature Id column
ASV_df2<-ASV_df[!grepl('Chloroplast', ASV_df$taxonomy),]#8558 obs 276 variables #remove Chloroplasts
ASV_df3<-ASV_df2[!grepl('Mitochondria', ASV_df2$taxonomy),]##8449 obs 276 variables variables #remove Mitochondria
ASV_df4<-ASV_df3[!grepl('Eukaryota', ASV_df3$taxonomy),]##8440 obs 276 variables variables #remove Eukaryotes

#Select only samples from the in vitro experiment
ASV_df5 <- ASV_df4[, !grepl('_L001', names(ASV_df4)), drop = FALSE]
#8440 obs 171 variables
#removing taxonomy column
ASV_df_notaxo <- ASV_df5[,c(1:170)]
tax<-ASV_df5%>%select("taxonomy")
#Remove absent taxa
ASVdf6<-ASV_df_notaxo[!rowSums(ASV_df_notaxo[])==0,] 

# Merge taxonomy data with ASV_df based on common_id
ASVdf_tax <- merge(ASVdf6, tax, by = "row.names", all.x = TRUE)
# Merge taxonomy data with ASV_df based on common_id
rownames(ASVdf_tax)<-ASVdf_tax$Row.names
ASVdf_tax<-ASVdf_tax[,-1]

mapping_df<-read.table(file=here("Raw_Data","mapping_file.tsv"), row.names=1, header=T, sep="\t", comment.char = "", check.names = F) #170 obs. 5 variables 
```

#Hellinger transformation 
on the abundance data frame. 
To transform this data it is important to transpose(rotate) the data frame.
```{r}
#Exposure to all five miRNAs
map_all5<- mapping_df[mapping_df$miRNA == "all5", ] #80 obs 5 variables
all5samples<- row.names(map_all5)
all5_df<-ASV_df_notaxo[ , (names(ASV_df_notaxo) %in% all5samples)]
rotate_all5 <- t(all5_df)
rotate_all5 <- decostand(rotate_all5, method="hellinger")

#Exposure to single miRNAs
map2uM<-mapping_df[mapping_df$Dose == "2", ] #90 obs 5 variables
samples_2uM<- row.names(map2uM)
df_2uM<-ASV_df_notaxo[ , (names(ASV_df_notaxo) %in% samples_2uM)]
df_2uM<-df_2uM[rowSums(df_2uM[])>0,]#52 obs 5 variables
rotate_2uM <- t(df_2uM)
rotate_2uM <- decostand(rotate_2uM, method="hellinger")

```

#Perform PCA
Using the function rda() without precising explanatory variables will calculate the principle components. 
```{r}
#PCA All 5 mirNAs
pca.all5<-rda (rotate_all5)
#verifying if we can interpret Pc1 and PC2
rdaaxe2<-rda(rotate_all5, pca.all5$CA$u[,2],pca.all5$CA$u[,1])
anova(rdaaxe2) # 0.001 ***
#broken stick model
screeplot(pca.all5, bstick = TRUE, type = "lines")

#PCA single mirNAs
pca.single<-rda (rotate_2uM)
#verifying if we can interpret Pc1 and PC2
rdaaxe2<-rda(rotate_2uM, pca.single$CA$u[,2],pca.single$CA$u[,1])
anova(rdaaxe2) # 0.001 ***
#broken stick model
screeplot(pca.single, bstick = TRUE, type = "lines")

```

#Extract Principle components
```{r}
#Components for the exposure to all 5 miRNAs
ii_all5<-summary(pca.all5)
scale1_all5<-scores(pca.all5, choices = 1:2, scaling=1)
#compiling site scores (scaling 1) 
stmat1_all5<-as.data.frame(scale1_all5$sites)
stmat1en_all5<-cbind(Row.Names = rownames(stmat1_all5), stmat1_all5)

#Components for the exposure single miRNAs
ii_single<-summary(pca.single)
scale1_single<-scores(pca.single, choices = 1:2, scaling=1)
#compiling site scores (scaling 1) 
stmat1_single<-as.data.frame(scale1_single$sites)
stmat1en_single<-cbind(Row.Names = rownames(stmat1_single), stmat1_single)

```

#Preparing data frame for ordination
Here we need to join our explanatory variables and our principle components
```{r}
#DF_ordi
df_all5<- merge(stmat1en_all5, map_all5,by = 'row.names')

df_single<- merge(stmat1en_single, map2uM,by = 'row.names')

```

#PCA ordination: exposure to 5 miRNAs
```{r}
 df_all5 <- df_all5 %>%mutate(across(N_Source, str_replace, "mix_17AA", 'Mix 17 AA'))
pca.ordi_all5<-ggplot() +
  geom_point(data = df_all5,aes(PC1,PC2,fill=N_Source, shape=Treatment), color="grey",size=6, stroke=1)+
  scale_fill_manual(values = c("#a50026","#d73027","#f46d43","#fdae61","#fee090","#e0f3f8","#74add1","#457b9d"))+
  scale_shape_manual(values=c(21,22))+
  labs(x=paste("PC1 (", format(100 *ii_all5$cont[[1]][2,1], digits=4), "%)", sep=""),
       y=paste("PC2 (", format(100 *ii_all5$cont[[1]][2,2], digits=4), "%)", sep=""))+
  guides(shape=guide_legend(title="miRNA treatment"))+
  guides(fill = guide_legend(title="Amino acids",override.aes = list(shape = 21)))+
theme_classic()
pca.ordi_all5
pca.ordi_all5.2<-pca.ordi_all5+theme(legend.text = element_text(size=12))+ theme(axis.title = element_text(size = 13))+
theme(legend.title = element_text(size=14)) +theme(plot.title = element_text(hjust = 0.5))
pca.ordi_all5.2
ggsave(pca.ordi_all5.2, file=here("Output","Ordination","PCA_16S_10uM.tiff"),units="cm", width=20, height=15, compression='lzw')
saveRDS(pca.ordi_all5.2, file = here("Output","Ordination","PCA_16S_10uM.rds"))
```

#PCA ordination: exposure to single miRNAs
```{r}
df_single$N_miR<-paste(df_single$N_Source, df_single$miRNA, sep=" ")
pca.ordi_single<-ggplot() +
  geom_point(data = df_single,aes(PC1,PC2,fill=N_miR, shape=Treatment), color="grey",size=6, stroke=1)+
  scale_fill_manual(values = c("#a50026","#e26257","#fb5607","#f58549" ,"#fdae61",
                               "#fffd77","#ffd374","#74add1","#157ecf")) +
  scale_shape_manual(values=c(21,22))+
  labs(x=paste("PC1 (", format(100 *ii_single$cont[[1]][2,1], digits=4), "%)", sep=""),
       y=paste("PC2 (", format(100 *ii_single$cont[[1]][2,2], digits=4), "%)", sep=""))+
  guides(shape=guide_legend(title="miRNA treatment"))+
  guides(fill = guide_legend(title="Amino acids and miRNA",override.aes = list(shape = 21)))+
theme_classic()
pca.ordi_single
pca.ordi_single.2<-pca.ordi_single+theme(legend.text = element_text(size=12))+ theme(axis.title = element_text(size = 13))+
theme(legend.title = element_text(size=14)) +theme(plot.title = element_text(hjust = 0.5))
pca.ordi_single.2
ggsave(pca.ordi_single.2, file=here("Output","Ordination","PCA_16S_2uM.tiff"),units="cm", width=20, height=15, compression='lzw')
saveRDS(pca.ordi_single.2, file = here("Output","Ordination","PCA_16S_2uM.rds"))
```