---
title: "2_mirNA_Reference_Statistics"
author: "Jessica A. Dozois"
date: '2023-01-30'
output: html_document
---
Loading librairies
```{r Librairies}
install.packages("pacman")
pacman::p_load(data.table,ggplot2,dplyr,vegan,ggrepel,writexl, here)
```
#Creating output folder
```{r}
dir.create(file.path("Output"),recursive = T)
```


#Importation
Importing abundance data frame and mapping file.
```{r}
#Arabidopsis
mirdf_RA<- read.table(file.path("Raw_Data","Athaliana_Ref.tsv"), row.names=1, header=T, sep="\t", comment.char = "")# 428 obs. 104

#Importing Mapping file
mapping<- read.table(file.path("Raw_Data","miRNA_map.tsv"),row.names=1, header=T, sep="\t", comment.char = "") # 104 obs.6 variables
mapping$Block <- as.character(mapping$Block) # Blocks need to be considered as chr
```



#Cleaning Data frame
Removing all miRNA clusters found in unplanted controls from the abundance data frame.
```{r Cleaning DF}
Arabidopsis_map<- mapping[mapping$Plant=="Arabidopsis",]

controls <- c("HI.5212.006.RPI12.7","HI.5212.006.RPI13.8","HI.5212.006.RPI14.9","HI.5212.006.RPI21.16", "HI.5212.006.RPI22.17", "HI.5212.006.RPI23.18", "HI.5212.006.RPI30.25", "HI.5212.006.RPI31.26" , "HI.5212.006.RPI32.27", "HI.5212.007.RPI39.34", "HI.5212.007.RPI40.35", "HI.5212.007.RPI41.36", "HI.5212.007.RPI48.43", "HI.5212.007.RPI1.44", "HI.5212.007.RPI2.45")
#selecting all miRNAs found in the unplanted soil samples (experimental controls)

#Arabidopsis
controlsRA<- mirdf_RA[,(names(mirdf_RA) %in% controls)]
mirRAcontrols<- controlsRA[rowSums(controlsRA[])>0,] #10 obs. 15 variables
mirRA_noctlrows<- mirdf_RA[!rownames(mirdf_RA) %in% rownames(mirRAcontrols),]#418obs.  104 variables
mirRA_noctl_clust<-mirRA_noctlrows[,!colnames(mirRA_noctlrows) %in% colnames(mirRAcontrols)]#418 obs. 89 variables
mirRA_noctl_notaxo<- mirRA_noctl_clust[,colnames(mirRA_noctl_clust) %in% rownames(Arabidopsis_map)] #418 obs 44 variables
```

#Hellinger transformation
Hellinger transformation on the abundance data frame. To transform this data it is important to transpose(rotate) the data frame.

```{r Hellinger transformation}
#All data
rotate_RA <- t(mirRA_noctl_notaxo)
rotate_RA <- decostand(rotate_RA, method="hellinger")

#Subset by compartment and plant
#Endosphere of Arabidopsis
map_endoarabi<- Arabidopsis_map[Arabidopsis_map$Compartment == "Endosphere", ]
endoarabi<- row.names(map_endoarabi)
endoarabi<-mirRA_noctl_notaxo[ , (colnames(mirRA_noctl_notaxo) %in% endoarabi)]#418 obs 15 variables
rotate_endoarabi <- t(endoarabi)
rotate_endoarabi <- decostand(rotate_endoarabi, method="hellinger")

```

#PERMANOVAs 
```{r PERMANOVAs}
set.seed(11) #fixes the permutation round
#All data
#Subset by compartment and plant
#Endosphere of Arabidopsis
permanova_endoarabi<- adonis2(rotate_endoarabi~Nitrogen,data=map_endoarabi, groups=Block, permutations = 9999, method="euclidean")

#Add results to an excel workbook
#Combining row names to each PERMANOVA result data frame
resendoa <-cbind(" "=rownames(permanova_endoarabi), permanova_endoarabi)
sheets <- list("permanova_endoarabi"=resendoa)
write_xlsx(sheets, file.path("Output","miRNA_Reference_PERMANOVA.xlsx"))

```


#Analysis of multivariate homogeneity of group dispersions (variances).
Dispersion must be considered when interpreting PERMANOVA results. 
```{r Betadisper}
set.seed(11)
distmatrix_RA<- vegdist(rotate_endoarabi, method="euclidean")
nitro_RA<-betadisper(distmatrix_RA, map_endoarabi$Nitrogen)
permutest(nitro_RA)#0.81
plot(nitro_RA)

```