---
title: "4_miRNA_abundance_Nitrogen"
author: "Marc-Antoine Duchesne & Jessica Dozois"
date: "2024-07-28"
output: html_document
---

#Loading librairies
```{r librairies}
install.packages("pacman")
pacman::p_load(data.table,ggplot2,dplyr,vegan,ggrepel,here,tidyr,ggpubr,ggh4x, rstatix, stringr,car,corrplot, pheatmap, Hmisc, reshape2, cowplot, FSA, scales)
```


#Creating output folder
```{r}
dir.create(file.path("Output","Figures"),recursive = T)
```


#Importation miRNA
Importing abundance data frame and mapping file.
```{r}
#Arabidopsis
mirdf_RA<- read.table(file.path("Raw_Data","Athaliana_Ref.tsv"), row.names=1, header=T, sep="\t", comment.char = "")# 428 obs. 104

#Importing Mapping file
mapping<- read.table(file.path("Raw_Data","miRNA_map.tsv"),row.names=1, header=T, sep="\t", comment.char = "") # 104 obs.6 variables
mapping$Block <- as.character(mapping$Block) # Blocks need to be considered as chr
```


#Cleaning Data frame miRNA
Removing all miRNA clusters found in unplanted controls from the abundance data frame.
```{r}
Arabidopsis_map<- mapping[mapping$Plant=="Arabidopsis",]

controls <- c("HI.5212.006.RPI12.7","HI.5212.006.RPI13.8","HI.5212.006.RPI14.9","HI.5212.006.RPI21.16", "HI.5212.006.RPI22.17", "HI.5212.006.RPI23.18", "HI.5212.006.RPI30.25", "HI.5212.006.RPI31.26" , "HI.5212.006.RPI32.27", "HI.5212.007.RPI39.34", "HI.5212.007.RPI40.35", "HI.5212.007.RPI41.36", "HI.5212.007.RPI48.43", "HI.5212.007.RPI1.44", "HI.5212.007.RPI2.45")
#selecting all miRNAs found in the unplanted soil samples (experimental controls)

#Arabidopsis
controlsRA<- mirdf_RA[,(names(mirdf_RA) %in% controls)]
mirRAcontrols<- controlsRA[rowSums(controlsRA[])>0,] #10 obs. 15 variables
mirRA_noctlrows<- mirdf_RA[!rownames(mirdf_RA) %in% rownames(mirRAcontrols),]#418obs.  104 variables
mirRA_noctl_clust<-mirRA_noctlrows[,!colnames(mirRA_noctlrows) %in% colnames(mirRAcontrols)]#418 obs. 89 variables
mirRA_noctl_notaxo<- mirRA_noctl_clust[,colnames(mirRA_noctl_clust) %in% rownames(Arabidopsis_map)] #418 obs 44 variables
```

#Computing relative abundances of the miRNA
```{r}
#Arabidopsis
miRID_RA<- mirRA_noctl_notaxo # working file for Arabidopsis miRNA
mirRA_noID <- miRID_RA[,1:44] # creating a table without miRNA_IDs 
tmirRA_noID<- t(mirRA_noID) # transposing table, samples as rows, miRNAs as columns to match metadata
mirRA_rel <- (tmirRA_noID/rowSums(tmirRA_noID)) #Normalization by relative abundance
(rowSums(mirRA_rel)) #Sanity check
```

## Subsetting for root miRNA samples
```{r}

mirRA_rel_map<- merge(Arabidopsis_map,mirRA_rel, by = 'row.names', all = TRUE )
mirRA_rel_root<-mirRA_rel_map[mirRA_rel_map$Compartment=='Endosphere',]
```

#Prepping dataframes for stastical test
```{r}
mirRA_rel_rootclean <- mirRA_rel_root[, apply(mirRA_rel_root, 2, function(col) !all(col == 0))]
miRNA_columns_Ara <- mirRA_rel_rootclean[, colnames(mirRA_rel_rootclean)[c(8:152)]]
miRNA_columns_Ara <- setdiff(names(miRNA_columns_Ara), "Nitrogen")
```

```{r}
# Open a connection to the text file for writing results
sink(file = here("Output", "Dunn_Ara_miRNAs.txt"), append = FALSE) # Open file for writing (not appending)

# Loop through each miRNA column and perform the tests
for (miRNA in miRNA_columns_Ara) {
  # Perform the Kruskal-Wallis test
  kruskal_test_result <- kruskal.test(mirRA_rel_rootclean[[miRNA]] ~ Nitrogen, data = mirRA_rel_rootclean)
  
  # Check if Kruskal-Wallis test is significant
  if (kruskal_test_result$p.value < 0.05) {
    # Write the miRNA and Kruskal-Wallis test result to the file
    cat("\nTesting", miRNA, "\n")
    cat("Kruskal-Wallis Test Result:\n")
    print(kruskal_test_result)
    
    # Perform Dunn's test
    dunn_test_result <- dunnTest(mirRA_rel_rootclean[[miRNA]] ~ Nitrogen, data = mirRA_rel_rootclean, method = "bh")
    
    # Extract relevant results
    dunn_results <- dunn_test_result$res
    if (!is.null(dunn_results)) {
      # Print Dunn's test results
      cat("Dunn's Test Result for", miRNA, ":\n")
      cat(sprintf("%-25s %10s %10s %10s\n", "Comparison", "Z", "P.unadj", "P.adj"))
      
      for (i in seq_len(nrow(dunn_results))) {
        comparison <- dunn_results$Comparison[i]
        z_value <- format(dunn_results$Z[i], digits = 6)
        p_unadj <- format(dunn_results$P.unadj[i], digits = 8)
        p_adj <- format(dunn_results$P.adj[i], digits = 8)
        cat(sprintf("%-25s %10s %10s %10s\n", comparison, z_value, p_unadj, p_adj))
      }
    } else {
      cat("Dunn's test did not produce any results.\n")
    }
  }
}

# Close the connection to the text file
sink()
```

#Arabidopsis miRNAs that were significantly affected by N treatment
```{r}
mirRA_interest<- mirRA_rel_rootclean[,c('Nitrogen', 'ath-miR158b_MIMAT0001014','ath-miR399b_MIMAT0000952','ath-miR5642b_MIMAT0022435','ath-miR398a-3p_MIMAT0000948','ath-miR390a-3p_MIMAT0031902','ath-miR160a-3p_MIMAT0031874','ath-miR408-3p_MIMAT0001011','ath-miR827_MIMAT0004243','ath-miR166b-5p_MIMAT0031881', 'ath-miR166d_MIMAT0000192',  'ath-miR164c-5p_MIMAT0001017','ath-miR396b-5p_MIMAT0000945','ath-miR399c-3p_MIMAT0000953','ath-miR399c-5p_MIMAT0031913','ath-miR398b-3p_MIMAT0000949','ath-miR398c-3p_MIMAT0000950' )]


#'ath-miR398b-3p_MIMAT0000949' and 'ath-miR398c-3p_MIMAT0000950' have the same sequence

mirRA_interest$'miR398bc-3p' <-(mirRA_interest$`ath-miR398b-3p_MIMAT0000949` + mirRA_interest$`ath-miR398c-3p_MIMAT0000950`)/2


mirRA_interest <- mirRA_interest %>% select(-contains(c('ath-miR398b','ath-miR398c','ath-miR164c')))#164c removed because dunn test was not significative
RA_abund_melt<-reshape2::melt(mirRA_interest)

RA_abund_melt<-RA_abund_melt %>%
  mutate(across(Nitrogen, str_replace, "No.Added.Nitrogen", 'No added N'))
RA_abund_melt<-RA_abund_melt %>%
  mutate(across(Nitrogen, str_replace, "Amino.Acids", 'AA'))
levels(RA_abund_melt$variable) <- c("ath-miR158b", "ath-miR399b","ath-miR5642b","ath-miR398a-3p","ath-miR390a-3p", "ath-miR160a-3p", "ath-miR408-3p","ath-miR827","ath-miR166b-5p","ath-miR166d","ath-miR396b-5p","ath-miR399c-3p","ath-miR399c-5p","ath-miR398bc-3p" )
names(RA_abund_melt)[2] <- "miRNA"
names(RA_abund_melt)[3] <- "Relative_abundance"

```


#Boxplot Arabidopsis
```{r}
boxall<- ggplot(RA_abund_melt, aes(x=Nitrogen, y=Relative_abundance*100)) +
    geom_boxplot(outlier.shape = NA, alpha=0.4, aes(fill=Nitrogen, color=Nitrogen )) +
  geom_point(aes(fill=Nitrogen, color=Nitrogen),pch = 21, position = position_jitterdodge())+
  theme_light() +
  facet_wrap2(vars(miRNA), scales = "free", nrow=1) +
scale_x_discrete()+
theme(axis.text.x=element_blank() ,axis.ticks.x = element_blank(),strip.background = element_rect(fill="white", linewidth = 0, linetype="solid"))+
theme(strip.text = element_text(colour = 'black', size=10))+
scale_fill_manual(values = c("grey30","#0a2463","#f95d6a"))+
scale_colour_manual(values = c("grey30","#0a2463","#f95d6a"))+
  theme(axis.title.y = element_text(size=14)) +
  labs(x="", y="Relative abundance of miRNAs (%)")+
  theme(legend.title = element_text(size = 14) ,legend.text = element_text(size=12))+
  facet_nested_wrap(~miRNA, scales="free_y", nrow=3, nest_line = TRUE)
    
boxall

#Computing the statistical test
stat.test <- RA_abund_melt %>%
  group_by(miRNA) %>%
  dunn_test(Relative_abundance ~ Nitrogen, p.adjust.method = 'BH') %>%
  add_significance()
stat.test

#adding significative * on boxplot
stat.test.pos<-stat.test %>% add_xy_position(x='Nitrogen', group='miRNA')

# Multiply the y.position values by 100
stat.test.pos$y.position <- c(0.0060, 0, 0, 0, 0, 0.0055, 0, 0.009, 0, 0, 0, 0.0045, 0.0013, 0.0015, 0, 0, 
                              0.003, 0, 0, 0, 0.06, 0, 0.055, 0.05, 0.016, 0.017, 0, 0, 0, 0.03, 0, 
                              0, 0.013, 0, 0, 0.0065, 0.0027, 0, 0.0025, 0, 0.04, 0.035) * 100  # Multiply by 100

boxall2<- boxall+stat_pvalue_manual(
    stat.test.pos, hide.ns = TRUE, 
    label = "p.adj.signif",tip.length = 0, size=6)+scale_y_continuous(labels = scales::number_format(accuracy = 0.01),
    limits = c(0, NA))
boxall2


ggsave(boxall2, file=here("Output","Figures","Arabidopsis_miRNAs_Nsig.tiff"),units="cm", width=24, height=23)
saveRDS(boxall2,file = here("Output","Arabidopsis_miRNAs_Nsig.rds"))


```


