---
title: "5_Correlations_miR_bacteria"
author: "Jessica A. Dozois"
date: "2024-05-24"
output: html_document
---

#Loading librairies
```{r librairies}
install.packages("pacman")
pacman::p_load(data.table,ggplot2,dplyr,vegan,ggrepel,here,tidyr,ggpubr,ggh4x, rstatix, stringr,car,corrplot, pheatmap, Hmisc, reshape2, cowplot)
```


#Creating output folder
```{r}
dir.create(file.path("Output","Correlations"),recursive = T)
```


#Importation miRNA
Importing abundance data frame and mapping file.
```{r}
#Arabidopsis
mirdf_RA<- read.table(file.path("Raw_Data","Athaliana_Ref.tsv"), row.names=1, header=T, sep="\t", comment.char = "")# 428 obs. 104

#Brachypodium
mirdf_RB<- read.table(file.path("Raw_Data","Bdistachyon_Ref.tsv"), row.names=1, header=T, sep="\t", comment.char = "")# 524 obs. 104

#Importing Mapping file
mapping<- read.table(file.path("Raw_Data","miRNA_map.tsv"),row.names=1, header=T, sep="\t", comment.char = "") # 104 obs.6 variables
mapping$Block <- as.character(mapping$Block) # Blocks need to be considered as chr
```


#Cleaning Data frame miRNA
Removing all miRNA clusters found in unplanted controls from the abundance data frame.
```{r}
Arabidopsis_map<- mapping[mapping$Plant=="Arabidopsis",]

controls <- c("HI.5212.006.RPI12.7","HI.5212.006.RPI13.8","HI.5212.006.RPI14.9","HI.5212.006.RPI21.16", "HI.5212.006.RPI22.17", "HI.5212.006.RPI23.18", "HI.5212.006.RPI30.25", "HI.5212.006.RPI31.26" , "HI.5212.006.RPI32.27", "HI.5212.007.RPI39.34", "HI.5212.007.RPI40.35", "HI.5212.007.RPI41.36", "HI.5212.007.RPI48.43", "HI.5212.007.RPI1.44", "HI.5212.007.RPI2.45")
#selecting all miRNAs found in the unplanted soil samples (experimental controls)

#Arabidopsis
controlsRA<- mirdf_RA[,(names(mirdf_RA) %in% controls)]
mirRAcontrols<- controlsRA[rowSums(controlsRA[])>0,] #10 obs. 15 variables
mirRA_noctlrows<- mirdf_RA[!rownames(mirdf_RA) %in% rownames(mirRAcontrols),]#418obs.  104 variables
mirRA_noctl_clust<-mirRA_noctlrows[,!colnames(mirRA_noctlrows) %in% colnames(mirRAcontrols)]#418 obs. 89 variables
mirRA_noctl_notaxo<- mirRA_noctl_clust[,colnames(mirRA_noctl_clust) %in% rownames(Arabidopsis_map)] #418 obs 44 variables
```

#Computing relative abundances of the miRNA
```{r}
#Arabidopsis
miRID_RA<- mirRA_noctl_notaxo # working file for Arabidopsis miRNA
mirRA_noID <- miRID_RA[,1:44] # creating a table without miRNA_IDs 
tmirRA_noID<- t(mirRA_noID) # transposing table, samples as rows, miRNAs as columns to match metadata
mirRA_rel <- (tmirRA_noID/rowSums(tmirRA_noID)) #Normalization by relative abundance
(rowSums(mirRA_rel)) #Sanity check
```

## Subsetting for root miRNA samples
```{r}

mirRA_rel_map<- merge(Arabidopsis_map,mirRA_rel, by = 'row.names', all = TRUE )
mirRA_rel_root<-mirRA_rel_map[mirRA_rel_map$Compartment=='Endosphere',]
```


#Importation 16S data
Importing abundance data frame and mapping file.
```{r Importation}
ASV_df<-read.table(file=here("Raw_Data","feature_table_filt_combi.tsv"), header=T, sep="\t", comment.char = "", check.names = F) #8703 obs 277 variables
ASV_df$`#FEATURE_ID` <- paste0("ASV#",ASV_df$`#FEATURE_ID`)
rownames(ASV_df)<-ASV_df$`#FEATURE_ID` # Feature ID as row names
ASV_df<-ASV_df[,-1] #removing the Feature Id column
colnames(ASV_df)[] <-  sub("_S.*", "", colnames(ASV_df)[]) #simplifying the names of columns
ASV_df2<-ASV_df[!grepl('Chloroplast', ASV_df$taxonomy),]#8558 obs 276 variables #remove Chloroplasts
ASV_df3<-ASV_df2[!grepl('Mitochondria', ASV_df2$taxonomy),]##8449 obs 276 variables variables #remove Mitochondria
ASV_df4<-ASV_df3[!grepl('Eukaryota', ASV_df3$taxonomy),]##8440 obs 276 variables variables #remove Eukaryotes

#Select only samples from the plant experiment
ASV_df5 <- ASV_df4[, !grepl(c('MI.M'), names(ASV_df4)), drop = FALSE]
#8440 obs 106 variables
#removing taxonomy column
ASV_df_notaxo <- ASV_df5[,c(1:105)]
tax<-ASV_df5%>%select("taxonomy")
#Remove absent taxa
ASVdf6<-ASV_df_notaxo[!rowSums(ASV_df_notaxo[])==0,] # 8348 obs 105 variables

# Merge taxonomy data with ASV_df based on common_id
ASVdf_tax <- merge(ASVdf6, tax, by = "row.names", all.x = TRUE) 
rownames(ASVdf_tax)<-ASVdf_tax$Row.names
ASVdf_tax<-ASVdf_tax[,-1] #8348 obs. 105 variables

mapping_df<-read.table(file=here("Raw_Data","mapping_file_16S.tsv"), row.names=1, header=T, sep="\t", comment.char = "", check.names = F) #105 obs. 5 variables

taxa<-ASVdf_tax%>%select("taxonomy") #8369 obs.
```

## Preparing 16S abundance matrix
```{r}
ASV_df_notaxo_t <- t(ASV_df_notaxo) # transposing table, samples as rows, species as columns to match metadata
com16_rel <- (ASV_df_notaxo_t/rowSums(ASV_df_notaxo_t)) #Normalization by relative abundance
(rowSums(com16_rel)) #Sanity check

#Subsetting for root samples
com16_rel_map<- merge(mapping_df,com16_rel, by = 'row.names', all = TRUE )
com16_rel_root<- com16_rel_map[com16_rel_map$Compartment=='Endosphere',]
com16_rel_rootA<-com16_rel_root[com16_rel_root$Plant=='Arabidopsis',]
```

#Combine
```{r}
#Combing miRNA abundance and 16S abundance in a single data frame
Arabi_miR_16S<- merge(com16_rel_rootA, mirRA_rel_root, by='Treatment', all=TRUE)
empty_colA <- colSums(Arabi_miR_16S==0)
non_numeric_colA <- sapply(Arabi_miR_16S, function(x) !is.numeric(x))
Arabi_miR_16S_clean<-Arabi_miR_16S[ ,!(empty_colA) | non_numeric_colA]
non_numeric_colA2 <- sapply(Arabi_miR_16S_clean, function(x) !is.numeric(x))
Arabi_miR_16S_reordered<- Arabi_miR_16S_clean[, c(which(non_numeric_colA2), which(!non_numeric_colA2))]
```

#Spearman heat maps
##Arabidopsis- Spearman correlation
```{r}
#Separating ASV and miRNA and removing the qualitative data
Ara_16S_reo <- Arabi_miR_16S_reordered[, colnames(Arabi_miR_16S_reordered)[c(13:48)]] #Warning : made by hand
Ara_miR_reo <- Arabi_miR_16S_reordered[, colnames(Arabi_miR_16S_reordered)[c(49:90)]]

#Renaming miRNAs
colnames(Ara_miR_reo) <- sapply(strsplit(colnames(Ara_miR_reo), "_"), `[`, 1)

# Combining the two matrices side by side to use rcorr
Acombined_data <- cbind(Ara_miR_reo, Ara_16S_reo)

# Computing correlations and p-values using Hmisc::rcorr
Acor_results <- rcorr(as.matrix(Acombined_data), type="spearman")

# Extracting correlation coefficients and p-values
Acor_matrix <- Acor_results$r
Apval_matrix <- Acor_results$P

# Defining the number of miRNAs and bacteria
Anum_molecules <- ncol(Ara_miR_reo)
Anum_bacteria <- ncol(Ara_16S_reo)

# The correlations between miRNAs and bacteria are in the off-diagonal blocks
Acor_matrix <- Acor_matrix[1:Anum_molecules, (Anum_molecules+1):(Anum_molecules+Anum_bacteria)]
Apval_matrix <- Apval_matrix[1:Anum_molecules, (Anum_molecules+1):(Anum_molecules+Anum_bacteria)]

# Adjusting p-values for multiple comparisons
Apval_adjusted <- p.adjust(as.vector(Apval_matrix), method="none") #warning : to visualize, we removed the adjusment
Apval_adjusted <- matrix(Apval_adjusted, nrow=Anum_molecules, ncol=Anum_bacteria)

# Filter correlations to include only significant ones (p.adjust <= 0.05)
Asignificant_correlations <- Acor_matrix
Asignificant_correlations[Apval_adjusted > 0.05] <- NA

#removing row and colums with no significative correlations
Asignificant_correlations <- Asignificant_correlations[rowSums(is.na(Asignificant_correlations)) != ncol(Asignificant_correlations), ]
Asignificant_correlations <- Asignificant_correlations[, colSums(is.na(Asignificant_correlations)) != nrow(Asignificant_correlations)]

# Note: pheatmap cannot handle NA values, so they are replaced by a small value for visualization. 
#Note MAD : this is not true
#significant_correlations[is.na(significant_correlations)] <- 0  # Replace NA with a very small value
pheatmap(Asignificant_correlations, 
         cluster_rows = F, cluster_cols = F, fontsize = 6,
         main = "Significant Correlations Heatmap",
         na_col = "white")  # Optionally set a color for NA values in pheatmap

```

###adjusting pheatmap + saving
```{r}
# Define a custom color palette
custom_colors <- colorRampPalette(c("#a4133c","#ff758f", "white", "#a3cef1","#003049"))(2000)

# Create the heatmap with custom colors and theme
heat_Ara <- pheatmap(Asignificant_correlations, 
         cluster_rows = F, 
         cluster_cols = F, 
         display_numbers = F,
         color = custom_colors,
         border_color = "lightgrey",  # Remove the border for a cleaner look
         cellwidth = 30, 
         cellheight = 15,
         main = "Significant correlations between bacterial ASVs and Arabidopsis miRNAs",
         na_col = "white")

ggsave(heat_Ara, file = here("Output","Correlations","Heatmap_Aridop.jpg"), width = 50, height = 25, units = "cm" ) 

```

#Correlations between ASVs and miRNAs
```{r}
#ASV#630 and ath-miR827

#ASV630 = k__Bacteria;p__Proteobacteria;c__Gammaproteobacteria;o__Enterobacterales;f__Colwelliaceae;g__Litorilituus;
#Extract the ASV data and miRNA
Asv630v827 <- data.frame(
  Treatment = Arabi_miR_16S_reordered$Treatment,
  Nitrogen.x = Arabi_miR_16S_reordered$Nitrogen.x,
  ASV_630 = Arabi_miR_16S_reordered$"ASV#630",
  ath_miR827 = Arabi_miR_16S_reordered$"ath-miR827_MIMAT0004243")

#Compute correlation
Asv630v827_test <- cor.test(Asv630v827$ASV_630, Asv630v827$ath_miR827, method = "spearman")

# Print the results
print(Asv630v827_test)

Asv630v827_plot <- ggplot(data = Asv630v827, aes(x = ASV_630, y = ath_miR827 )) +
  geom_smooth(method = "lm", se = T, color = "black", fill = "#e9ecef")+
  geom_point(aes(fill =Nitrogen.x), shape = 21, size = 4.5) +
  stat_cor(method = "spearman") + scale_fill_manual(values = c("grey60","#0A2463","#F95D6A"), labels = c("AA", "NH4NO3", "No added N"))  +  
  labs(x = "Litorilituus relative abundance (ASV#630)", y = "", title = "") +theme_bw() + theme(legend.title = element_blank())

```

```{r}
#Correlation between ASV#478 and ath-miR827
#k__Bacteria;p__Proteobacteria;c__Gammaproteobacteria;o__Burkholderiales;f__Oxalobacteraceae;g__Massilia;

#Extract the ASV data and miRNA
Asv478v827 <- data.frame(
  Treatment = Arabi_miR_16S_reordered$Treatment,
  Nitrogen.x = Arabi_miR_16S_reordered$Nitrogen.x,
  ASV_478 = Arabi_miR_16S_reordered$"ASV#478",
  ath_miR827 = Arabi_miR_16S_reordered$"ath-miR827_MIMAT0004243")

#Compute correlation
Asv478v827_test <- cor.test(Asv478v827$ASV_478, Asv478v827$ath_miR827, method = "spearman")

# Print the results
print(Asv478v827_test)

Asv478v827_plot <- ggplot(data = Asv478v827, aes(x = ASV_478, y = ath_miR827 )) +
  geom_smooth(method = "lm", se = T, color = "black", fill = "#e9ecef")+
  geom_point(aes(fill =Nitrogen.x), shape = 21, size = 4.5) +
  stat_cor(method = "spearman", label.y=0.05) + scale_fill_manual(values = c("grey60","#0A2463","#F95D6A"), labels = c("AA", "NH4NO3", "No added N"))  +  
  labs(x = "Massilia relative abundance (ASV#478)", y = "", title = "") +theme_bw() + theme(legend.title = element_blank())
print(Asv478v827_plot)

```


```{r}
#Correlation between ASV#111 and ath-miR827
#k__Bacteria;p__Chloroflexi;c__Ktedonobacteria;o__C0119;f__C0119OR;g__C0119OR;
# Extract the ASV data and miRNA

Asv111v827 <- data.frame(
  Treatment = Arabi_miR_16S_reordered$Treatment,
  Nitrogen.x = Arabi_miR_16S_reordered$Nitrogen.x,
  ASV_111 = Arabi_miR_16S_reordered$"ASV#111",
  ath_miR827 = Arabi_miR_16S_reordered$"ath-miR827_MIMAT0004243")

#Compute correlation
Asv111v827_test <- cor.test(Asv111v827$ASV_111, Asv111v827$ath_miR827, method = "spearman")

# Print the results
print(Asv111v827_test)

Asv111v827_plot <- ggplot(data = Asv111v827, aes(x = ASV_111, y = ath_miR827 )) +
  geom_smooth(method = "lm", se = T, color = "black", fill = "#e9ecef")+
  geom_point(aes(fill =Nitrogen.x), shape = 21, size = 4.5) +
  stat_cor(method = "spearman") + scale_fill_manual(values = c("grey60","#0A2463","#F95D6A"), labels = c("AA", "NH4NO3", "No added N"))  +  
  labs(x = "Ktedonobacteria relative abundance (ASV#111)", y = "", title = "") +theme_bw() + theme(legend.title = element_blank())
print(Asv111v827_plot)

```


```{r}
#Correlation between ASV#41 and ath-miR827
#k__Bacteria;p__Proteobacteria;c__Gammaproteobacteria;o__Xanthomonadales;f__Xanthomonadaceae;g__Luteimonas;

#Extract the ASV data and miRNA
Asv41v827 <- data.frame(
  Treatment = Arabi_miR_16S_reordered$Treatment,
  Nitrogen.x = Arabi_miR_16S_reordered$Nitrogen.x,
  ASV_41 = Arabi_miR_16S_reordered$"ASV#41",
  ath_miR827 = Arabi_miR_16S_reordered$"ath-miR827_MIMAT0004243")

#Compute correlation
Asv41v827_test <- cor.test(Asv41v827$ASV_41, Asv41v827$ath_miR827, method = "spearman")

# Print the results
print(Asv41v827_test)

Asv41v827_plot <- ggplot(data = Asv41v827, aes(x = ASV_41, y = ath_miR827 )) +
  geom_smooth(method = "lm", se = T, color = "black", fill = "#e9ecef")+
  geom_point(aes(fill =Nitrogen.x), shape = 21, size = 4.5) +
  stat_cor(method = "spearman") + scale_fill_manual(values = c("grey60","#0A2463","#F95D6A"), labels = c("AA", "NH4NO3", "No added N"))  +  
  labs(x = "Luteimonas relative abundance (ASV#41)", y = "", title = "") +theme_bw() + theme(legend.title = element_blank())
print(Asv41v827_plot)

```

```{r}
#Correlation between ASV#14 and ath-miR827
#k__Bacteria;p__Proteobacteria;c__Gammaproteobacteria;o__Burkholderiales;f__Oxalobacteraceae;g__Massilia;

#Extract the ASV data and miRNA
Asv14v827 <- data.frame(
  Treatment = Arabi_miR_16S_reordered$Treatment,
  Nitrogen.x = Arabi_miR_16S_reordered$Nitrogen.x,
  ASV_14 = Arabi_miR_16S_reordered$"ASV#14",
  ath_miR827 = Arabi_miR_16S_reordered$"ath-miR827_MIMAT0004243")

#Compute correlation
Asv14v827_test <- cor.test(Asv14v827$ASV_14, Asv14v827$ath_miR827, method = "spearman")

# Print the results
print(Asv14v827_test)

Asv14v827_plot <- ggplot(data = Asv14v827, aes(x = ASV_14, y = ath_miR827 )) +
  geom_smooth(method = "lm", se = T, color = "black", fill = "#e9ecef")+
  geom_point(aes(fill =Nitrogen.x), shape = 21, size = 4.5) +
  stat_cor(method = "spearman") + scale_fill_manual(values = c("grey60","#0A2463","#F95D6A"), labels = c("AA", "NH4NO3", "No added N"))  +  
  labs(x = "Massilia relative abundance (ASV#14)", y = "", title = "") +theme_bw() + theme(legend.title = element_blank())
print(Asv14v827_plot)
```


```{r}
#ath-miR827 combined plot
#make legend bigger beforehand
Asv14v827_plot <- Asv14v827_plot + theme(legend.text = element_text (size = 20))
print(Asv14v827_plot)
                                         
legend <- get_legend(Asv14v827_plot)

# Create an empty plot p3
empty_plot <- ggplot() + theme_void()
# Combine the empty plot with the legend
combined_plot <- plot_grid(empty_plot, legend, ncol = 1, rel_heights = c(1, 0.2))
legend <- get_legend(Asv14v827_plot)

# Create an empty plot with bigger size
empty_plot <- ggplot() + theme_void() + theme(plot.margin = margin(20, 20, 20, 20, "cm"))

# Combine the empty plot with the legend
p3 <- plot_grid(empty_plot, legend, ncol = 1, rel_heights = c(0, 20))
#combined_plot <-combined_plot + theme(legend.position = 0.5,0.5 )

# Print the combined plot
print(p3)

#removing legend 
Asv14v827_plot1 <- Asv14v827_plot + theme(legend.position = "none")
Asv41v827_plot1 <- Asv41v827_plot + theme(legend.position = "none")
Asv111v827_plot1 <-Asv111v827_plot+ theme(legend.position = "none")
Asv478v827_plot1 <-Asv478v827_plot+ theme(legend.position = "none")
Asv630v827_plot1 <- Asv630v827_plot+ theme(legend.position = "none")


all_athmiR827_ara <- ggarrange (Asv14v827_plot1,Asv41v827_plot1,Asv111v827_plot1,Asv478v827_plot1, Asv630v827_plot1, p3)


print (all_athmiR827_ara)
all_athmiR827_ara<-annotate_figure(all_athmiR827_ara, left = text_grob("ath-miR827 relative abondance", size =10, rot = 90))
print(all_athmiR827_ara)

```


```{r}
#Correlation between ASV#67 and ath-miR158a3p
#k__Bacteria;p__Bacteroidota;c__Bacteroidia;o__Chitinophagales;f__Chitinophagaceae;g__Niastella;

#Extract the ASV data and miRNA
Asv67v158a3p <- data.frame(
  Treatment = Arabi_miR_16S_reordered$Treatment,
  Nitrogen.x = Arabi_miR_16S_reordered$Nitrogen.x,
  ASV_67 = Arabi_miR_16S_reordered$"ASV#67",
  ath_miR158a3p = Arabi_miR_16S_reordered$"ath-miR158a-3p_MIMAT0000176")

#Compute correlation
Asv67v158a3p_test <- cor.test(Asv67v158a3p$ASV_67, Asv67v158a3p$ath_miR158a3p, method = "spearman")

# Print the results
print(Asv67v158a3p_test)

Asv67v158a3p_plot <- ggplot(data = Asv67v158a3p, aes(x = ASV_67, y = ath_miR158a3p )) +
  geom_smooth(method = "lm", se = T, color = "black", fill = "#e9ecef")+
  geom_point(aes(fill =Nitrogen.x), shape = 21, size = 4.5) +
  stat_cor(method = "spearman",label.y = 0.12 ) + scale_fill_manual(values = c("grey60","#0A2463","#F95D6A"), labels = c("AA", "NH4NO3", "No added N")) +   labs(x = "Niastella relative abundance (ASV#67)", y = "", title = "") +theme_bw() + theme(legend.title = element_blank())
print(Asv67v158a3p_plot)
 
```


```{r}
#Correlation between ASV#111 and ath-miR158a3p
#k__Bacteria;p__Chloroflexi;c__Ktedonobacteria;o__C0119;f__C0119OR;g__C0119OR;

#Extract the ASV data and miRNA
Asv111v158a3p <- data.frame(
  Treatment = Arabi_miR_16S_reordered$Treatment,
  Nitrogen.x = Arabi_miR_16S_reordered$Nitrogen.x,
  ASV_111 = Arabi_miR_16S_reordered$"ASV#111",
  ath_miR158a3p = Arabi_miR_16S_reordered$"ath-miR158a-3p_MIMAT0000176")

#Compute correlation
Asv111v158a3p_test <- cor.test(Asv111v158a3p$ASV_111, Asv111v158a3p$ath_miR158a3p, method = "spearman")

# Print the results
print(Asv111v158a3p_test)

Asv111v158a3p_plot <- ggplot(data = Asv111v158a3p, aes(x = ASV_111, y = ath_miR158a3p )) +
  geom_smooth(method = "lm", se = T, color = "black", fill = "#e9ecef")+
  geom_point(aes(fill =Nitrogen.x), shape = 21, size = 4.5) +
  stat_cor(method = "spearman",label.y = 0.12 ) + scale_fill_manual(values = c("grey60","#0A2463","#F95D6A"), labels = c("AA", "NH4NO3", "No added N"))  +  
  labs(x = "Ktedonobacteria relative abundance (ASV#111)", y = "", title = "") +theme_bw() + theme(legend.title = element_blank())
print(Asv111v158a3p_plot)
ggsave(Asv111v158a3p_plot, file = here("Output", "Figures","ASV111vsmiR158a3p.jpg"), width = 20, height = 15, units = "cm" ) 
```


```{r}
#Correlation between ASV#630 and ath-miR158a3p
#ASV630 = k__Bacteria;p__Proteobacteria;c__Gammaproteobacteria;o__Enterobacterales;f__Colwelliaceae;g__Litorilituus;

#Extract the ASV data and miRNA
Asv630v158a3p <- data.frame(
  Treatment = Arabi_miR_16S_reordered$Treatment,
  Nitrogen.x = Arabi_miR_16S_reordered$Nitrogen.x,
  ASV_630 = Arabi_miR_16S_reordered$"ASV#630",
  ath_miR158a3p = Arabi_miR_16S_reordered$"ath-miR158a-3p_MIMAT0000176")

#Compute correlation
Asv630v158a3p_test <- cor.test(Asv630v158a3p$ASV_630, Asv630v158a3p$ath_miR158a3p, method = "spearman")

# Print the results
print(Asv630v158a3p_test)

Asv630v158a3p_plot <- ggplot(data = Asv630v158a3p, aes(x = ASV_630, y = ath_miR158a3p )) +
  geom_smooth(method = "lm", se = T, color = "black", fill = "#e9ecef")+
  geom_point(aes(fill =Nitrogen.x), shape = 21, size = 4.5) +
  stat_cor(method = "spearman",label.y = 0.12 ) + scale_fill_manual(values = c("grey60","#0A2463","#F95D6A"), labels = c("AA", "NH4NO3", "No added N"))  +  
  labs(x = "Litorilituus relative abundance (ASV#630)", y = "", title = "") +theme_bw() + theme(legend.title = element_blank())
print(Asv630v158a3p_plot)

```


```{r}
#ath-miR158a3p combined plot
#must run previous chunk to get the empty plot with legend

#removing legend 
Asv67v158a3p_plot1 <- Asv67v158a3p_plot + theme(legend.position = "none")
Asv111v158a3p_plot1 <- Asv111v158a3p_plot + theme(legend.position = "none")
Asv630v158a3p_plot1 <-Asv630v158a3p_plot+ theme(legend.position = "")


all_athmiR158a3p_ara <- ggarrange (Asv67v158a3p_plot1,Asv111v158a3p_plot1,Asv630v158a3p_plot1, ncol = 3, common.legend = T, align = "hv",
  legend = "right")


print (all_athmiR158a3p_ara)

all_athmiR158a3p_ara<-annotate_figure(all_athmiR158a3p_ara, left = text_grob("ath-miR158a-3p relative abondance", size =10, rot = 90))
print(all_athmiR158a3p_ara)

```


```{r}
#Correlation between ASV#53 and ath-miR159a
#k__Bacteria;p__Bacteroidota;c__Bacteroidia;o__Chitinophagales;f__Chitinophagaceae;g__Flavitalea;

#Extract the ASV data and miRNA
Asv53v159a <- data.frame(
  Treatment = Arabi_miR_16S_reordered$Treatment,
  Nitrogen.x = Arabi_miR_16S_reordered$Nitrogen.x,
  ASV_53 = Arabi_miR_16S_reordered$"ASV#53",
  ath_miR159a = Arabi_miR_16S_reordered$"ath-miR159a_MIMAT0000177")

#Compute correlation
Asv53v159a_test <- cor.test(Asv53v159a$ASV_53, Asv53v159a$ath_miR159a, method = "spearman")

# Print the results
print(Asv53v159a_test)

Asv53v159a_plot <- ggplot(data = Asv53v159a, aes(x = ASV_53, y = ath_miR159a )) +
  geom_smooth(method = "lm", se = T, color = "black", fill = "#e9ecef")+
  geom_point(aes(fill =Nitrogen.x), shape = 21, size = 4.5) +
  stat_cor(method = "spearman",label.y = 0.17 ) + scale_fill_manual(values = c("grey60","#0A2463","#F95D6A"), labels = c("AA", "NH4NO3", "No added N"))  +  
  labs(x = "Flavitalea relative abundance (ASV#53)", y = "ath-miR159a relative abondance", title = "") +theme_bw() + theme(legend.title = element_blank())
print(Asv53v159a_plot)
```


```{r}
#Correlation between ASV#14 and ath-miR5642b
#k__Bacteria;p__Proteobacteria;c__Gammaproteobacteria;o__Burkholderiales;f__Oxalobacteraceae;g__Massilia;

#Extract the ASV data and miRNA
Asv14v5642b <- data.frame(
  Treatment = Arabi_miR_16S_reordered$Treatment,
  Nitrogen.x = Arabi_miR_16S_reordered$Nitrogen.x,
  ASV_14 = Arabi_miR_16S_reordered$"ASV#14",
  ath_miR5642b = Arabi_miR_16S_reordered$"ath-miR5642b_MIMAT0022435")

#Compute correlation
Asv14v5642b_test <- cor.test(Asv14v5642b$ASV_14, Asv14v5642b$ath_miR5642b, method = "spearman")

# Print the results
print(Asv14v5642b_test)

Asv14v5642b_plot <- ggplot(data = Asv14v5642b, aes(x = ASV_14, y = ath_miR5642b )) +
  geom_smooth(method = "lm", se = T, color = "black", fill = "#e9ecef")+
  geom_point(aes(fill =Nitrogen.x), shape = 21, size = 4.5) +
  stat_cor(method = "spearman") + scale_fill_manual(values = c("grey60","#0A2463","#F95D6A"), labels = c("AA", "NH4NO3", "No added N"))  +  
  labs(x = "Massilia relative abundance (ASV#14)", y = "", title = "") +theme_bw() + theme(legend.title = element_blank())
print(Asv14v5642b_plot)
```


```{r}
#Correlation between ASV#98 and ath-miR5642b
#k__Bacteria;p__Proteobacteria;c__Alphaproteobacteria;o__Rhizobiales;f__Rhizobiaceae;g__Allorhizobium-Neorhizobium-Pararhizobium-Rhizobium;

#Extract the ASV data and miRNA
Asv98v5642b <- data.frame(
  Treatment = Arabi_miR_16S_reordered$Treatment,
  Nitrogen.x = Arabi_miR_16S_reordered$Nitrogen.x,
  ASV_98 = Arabi_miR_16S_reordered$"ASV#98",
  ath_miR5642b = Arabi_miR_16S_reordered$"ath-miR5642b_MIMAT0022435")

#Compute correlation
Asv98v5642b_test <- cor.test(Asv98v5642b$ASV_98, Asv98v5642b$ath_miR5642b, method = "spearman")

# Print the results
print(Asv98v5642b_test)

Asv98v5642b_plot <- ggplot(data = Asv98v5642b, aes(x = ASV_98, y = ath_miR5642b )) +
  geom_smooth(method = "lm", se = T, color = "black", fill = "#e9ecef")+
  geom_point(aes(fill =Nitrogen.x), shape = 21, size = 4.5) +
  stat_cor(method = "spearman", label.y = 0.010) + scale_fill_manual(values = c("grey60","#0A2463","#F95D6A"), labels = c("AA", "NH4NO3", "No added N"))  +  
  labs(x = "Rhizobiaceae relative abundance (ASV#98)", y = "", title = "") +theme_bw() + theme(legend.title = element_blank())
print(Asv98v5642b_plot)
```


```{r}
#Correlation between ASV#478 and ath-miR5642b
#k__Bacteria;p__Proteobacteria;c__Gammaproteobacteria;o__Burkholderiales;f__Oxalobacteraceae;g__Massilia;
#Extract the ASV data and miRNA

Asv478v5642b <- data.frame(
  Treatment = Arabi_miR_16S_reordered$Treatment,
  Nitrogen.x = Arabi_miR_16S_reordered$Nitrogen.x,
  ASV_478 = Arabi_miR_16S_reordered$"ASV#478",
  ath_miR5642b = Arabi_miR_16S_reordered$"ath-miR5642b_MIMAT0022435")

#Compute correlation
Asv478v5642b_test <- cor.test(Asv478v5642b$ASV_478, Asv478v5642b$ath_miR5642b, method = "spearman")

# Print the results
print(Asv478v5642b_test)

Asv478v5642b_plot <- ggplot(data = Asv478v5642b, aes(x = ASV_478, y = ath_miR5642b )) +
  geom_smooth(method = "lm", se = T, color = "black", fill = "#e9ecef")+
  geom_point(aes(fill =Nitrogen.x), shape = 21, size = 4.5) +
  stat_cor(method = "spearman", label.y=0.009) + scale_fill_manual(values = c("grey60","#0A2463","#F95D6A"), labels = c("AA", "NH4NO3", "No added N"))  +  
  labs(x = "Massilia relative abundance (ASV#478)", y = "", title = "") +theme_bw() + theme(legend.title = element_blank())
print(Asv478v5642b_plot)
```


```{r}
#ath-miR5642b combined plot
#must run previous chunk to get the empty plot with legend
#removing legend 
Asv14v5642b_plot1 <- Asv14v5642b_plot + theme(legend.position = "none")
Asv98v5642b_plot1 <- Asv98v5642b_plot + theme(legend.position = "none")
Asv478v5642b_plot1 <- Asv478v5642b_plot + theme(legend.position = "")

all_athmiR5642b_ara <- ggarrange (Asv14v5642b_plot1,Asv98v5642b_plot1,Asv478v5642b_plot1, ncol = 3, common.legend = T, align = "hv",
  legend = "right")


print (all_athmiR5642b_ara)

all_athmiR5642b_ara<-annotate_figure(all_athmiR5642b_ara, left = text_grob("ath-miR5642b relative abondance", size =10, rot = 90))
print(all_athmiR5642b_ara)

```

#Combining all plots
```{r}
#Adding y label
Asv53v159a_plot <- Asv53v159a_plot + labs(y = "ath-miR159a")
Asv14v827_plot1 <-Asv14v827_plot + labs(y = "ath-miR827")
Asv41v827_plot1 <-Asv41v827_plot1+ labs(y = "ath-miR827")
Asv111v827_plot1 <-Asv111v827_plot1+ labs(y = "ath-miR827")
Asv478v827_plot1 <-Asv478v827_plot1+ labs(y = "ath-miR827")
Asv630v827_plot1 <-Asv630v827_plot1+ labs(y = "ath-miR827")
Asv67v158a3p_plot1<-Asv67v158a3p_plot1+ labs(y = "ath-miR158a-3p")
Asv111v158a3p_plot1<-Asv111v158a3p_plot1+ labs(y = "ath-miR158a-3p")
Asv630v158a3p_plot1<-Asv630v158a3p_plot1+ labs(y = "ath-miR158a-3p")
Asv14v5642b_plot1 <-Asv14v5642b_plot1+ labs(y = "ath-miR5642b")
Asv98v5642b_plot1<-Asv98v5642b_plot1+ labs(y = "ath-miR5642b")
Asv478v5642b_plot1<-Asv478v5642b_plot1+ labs(y = "ath-miR5642b")


#combining miR827 with miR159 for aesthetic
Asv14v827_plot2 <- Asv14v827_plot1 +theme(legend.text = element_text(size = 12))
Asv53v159a_plot2 <- Asv53v159a_plot + theme(legend.position = "none")

miR827_159 <- ggarrange (Asv14v827_plot2,Asv41v827_plot1,Asv111v827_plot1,Asv478v827_plot1, Asv630v827_plot1,Asv53v159a_plot2, common.legend = T )
miR827_159 <- annotate_figure(miR827_159, left = text_grob("", size =12, rot = 90))
miR827_159 

#removing legends
miR158 <-ggarrange(Asv67v158a3p_plot1,Asv111v158a3p_plot1,Asv630v158a3p_plot1, common.legend = F, ncol = 3)
miR158 <- annotate_figure(miR158, left = text_grob("", size =12, rot = 90))
miR158

miR5642b <- ggarrange(Asv14v5642b_plot1,Asv98v5642b_plot1,Asv478v5642b_plot1, ncol = 3, common.legend = F)
miR5642b<-annotate_figure(miR5642b, left = text_grob("", size =12, rot = 90))
miR5642b

  
all1 <- ggarrange(miR827_159,miR158,miR5642b , common.legend = T, ncol =1, align = "hv",heights = c(2,1,1))
all1

all <- annotate_figure(all1, left = text_grob("Relative abundance of root miRNAs", size =14, rot = 90))
ggsave(all, file = here("Output", "Correlations","All_asv_vs_miRAra.tiff"), width = 30, height = 35, units = "cm")
saveRDS(all,file = here("Output","Correlations","All_asv_vs_miRAra.rds"))
```


#Linear regression models with N
```{r}
#For more information about assumptions reqquired to perform and interpret linear regression models, please consult
#http://www.sthda.com/english/articles/39-regression-model-diagnostics/161-linear-regression-assumptions-and-diagnostics-in-r-essentials/

#158a_3p
model158a_67<-lm(`ASV#67` ~ `ath-miR158a-3p_MIMAT0000176`+Nitrogen.x, data = Arabi_miR_16S_clean)
summary(model158a_67)#*
Anova(model158a_67) # to extract ANOVA table from the model
#Assumptions
par(mfrow = c(2, 2))
plot(model158a_67)
ncvTest(model158a_67)# NOT OK, but the scale-location plot is ok
#normality assumption
shapiro.test(residuals(model158a_67)) #OK

model158a_111<-lm(`ASV#111` ~ `ath-miR158a-3p_MIMAT0000176`+Nitrogen.x, data = Arabi_miR_16S_clean)
summary(model158a_111) #ns

model158a_630<-lm(`ASV#630` ~ `ath-miR158a-3p_MIMAT0000176`+ Nitrogen.x, data = Arabi_miR_16S_clean)
summary(model158a_630) #ns

#159
model159_53 <- lm(`ASV#53` ~ `ath-miR159a_MIMAT0000177`+ Nitrogen.x, data = Arabi_miR_16S_clean)
summary(model159_53) #ns

#827
model827_14 <- lm(`ASV#14` ~ `ath-miR827_MIMAT0004243`+ Nitrogen.x, data = Arabi_miR_16S_clean)
summary(model827_14) #*
Anova(model827_14) # to extract ANOVA table from the model
#Assumptions
par(mfrow = c(2, 2))
plot(model827_14)
ncvTest(model827_14)#OK
#normality assumption
shapiro.test(residuals(model827_14)) #OK

model827_41 <- lm(`ASV#41` ~ `ath-miR827_MIMAT0004243`+ Nitrogen.x, data = Arabi_miR_16S_clean)
summary(model827_41) #ns

model827_111 <- lm(`ASV#111` ~ `ath-miR827_MIMAT0004243` + Nitrogen.x, data = Arabi_miR_16S_clean)
summary(model827_111) #ns

model827_478 <- lm(`ASV#478` ~ `ath-miR827_MIMAT0004243` + Nitrogen.x, data = Arabi_miR_16S_clean)
summary(model827_478) #ns

model827_630 <- lm(`ASV#630` ~ `ath-miR827_MIMAT0004243` +Nitrogen.x, data = Arabi_miR_16S_clean)
summary(model827_630) #ns

#5642b
model5642b_14 <- lm(`ASV#14` ~ `ath-miR5642b_MIMAT0022435`+Nitrogen.x, data = Arabi_miR_16S_clean)
summary(model5642b_14) #*
Anova(model5642b_14)# to extract ANOVA table from the model
#Assumptions
ncvTest(model5642b_14) #OK
#normality assumption
shapiro.test(residuals(model5642b_14)) #OK

model5642b_98 <- lm(`ASV#98` ~ `ath-miR5642b_MIMAT0022435`+Nitrogen.x, data = Arabi_miR_16S_clean)
summary(model5642b_98)#ns

model5642b_478 <- lm(`ASV#478` ~ `ath-miR5642b_MIMAT0022435` +Nitrogen.x, data = Arabi_miR_16S_clean)
summary(model5642b_478)#ns

```
#Linear regression models without N
```{r}
#For more information about assumptions reqquired to perform and interpret linear regression models, please consult
#http://www.sthda.com/english/articles/39-regression-model-diagnostics/161-linear-regression-assumptions-and-diagnostics-in-r-essentials/

#158a_3p
model158a_67<-lm(`ASV#67` ~ `ath-miR158a-3p_MIMAT0000176`, data = Arabi_miR_16S_clean)
summary(model158a_67)#ns

model158a_111<-lm(`ASV#111` ~ `ath-miR158a-3p_MIMAT0000176`, data = Arabi_miR_16S_clean)
summary(model158a_111) #*
#Assumptions
ncvTest(model158a_111) #OK
#normality assumption
shapiro.test(residuals(model158a_111)) #OK

model158a_630<-lm(`ASV#630` ~ `ath-miR158a-3p_MIMAT0000176`, data = Arabi_miR_16S_clean)
summary(model158a_630) #*
#Assumptions
ncvTest(model158a_630) #OK
#normality assumption
shapiro.test(residuals(model158a_630)) #OK

#159
model159_53 <- lm(`ASV#53` ~ `ath-miR159a_MIMAT0000177`, data = Arabi_miR_16S_clean)
summary(model159_53) #ns

#827
model827_14 <- lm(`ASV#14` ~ `ath-miR827_MIMAT0004243`, data = Arabi_miR_16S_clean)
summary(model827_14) #*
#Assumptions
par(mfrow = c(2, 2))
plot(model827_14)
ncvTest(model827_14)#OK
#normality assumption
shapiro.test(residuals(model827_14)) #OK

model827_41 <- lm(`ASV#41` ~ `ath-miR827_MIMAT0004243`, data = Arabi_miR_16S_clean)
summary(model827_41) #*
#Assumptions
ncvTest(model827_41) #OK
#normality assumption
shapiro.test(residuals(model827_41)) #OK

model827_111 <- lm(`ASV#111` ~ `ath-miR827_MIMAT0004243`, data = Arabi_miR_16S_clean)
summary(model827_111) #*
#Assumptions
ncvTest(model827_111) #OK
#normality assumption
shapiro.test(residuals(model827_111)) #OK

model827_478 <- lm(`ASV#478` ~ `ath-miR827_MIMAT0004243`, data = Arabi_miR_16S_clean)
summary(model827_478) #*
#Assumptions
ncvTest(model827_478) #problematic
#normality assumption
shapiro.test(residuals(model827_478)) # problematic

model827_630 <- lm(`ASV#630` ~ `ath-miR827_MIMAT0004243`, data = Arabi_miR_16S_clean)
summary(model827_630) #*
#Assumptions
ncvTest(model827_630) #OK
#normality assumption
shapiro.test(residuals(model827_630)) #OK

#5642b
model5642b_14 <- lm(`ASV#14` ~ `ath-miR5642b_MIMAT0022435`, data = Arabi_miR_16S_clean)
summary(model5642b_14) #*
#Assumptions
ncvTest(model5642b_14) #OK
#normality assumption
shapiro.test(residuals(model5642b_14)) #OK

model5642b_98 <- lm(`ASV#98` ~ `ath-miR5642b_MIMAT0022435`, data = Arabi_miR_16S_clean)
summary(model5642b_98)#ns

model5642b_478 <- lm(`ASV#478` ~ `ath-miR5642b_MIMAT0022435`, data = Arabi_miR_16S_clean)
summary(model5642b_478)#ns

```

