---
title: "2_PCA-16SmiRNAs"
author: "Jessica A. Dozois"
date: '2023-10-21'
output: html_document
---

#Loading librairies
```{r librairies}
install.packages("pacman")
pacman::p_load(data.table,ggplot2,dplyr,vegan,ggrepel,here,tidyr,ggpubr,ggh4x, stringr)
```

#Creating a folder
```{r}
dir.create(file.path("Output","Ordination"),recursive = T)
```

#Importation
Importing abundance data frame and mapping file.
```{r Importation}
ASV_df<-read.table(file=here("Raw_Data","feature_table_filt_combi.tsv"), header=T, sep="\t", comment.char = "", check.names = F) #8703 obs 277 variables
ASV_df$`#FEATURE_ID` <- paste0("ASV#",ASV_df$`#FEATURE_ID`)
rownames(ASV_df)<-ASV_df$`#FEATURE_ID` # Feature ID as row names
ASV_df<-ASV_df[,-1] #removing the Feature Id column
colnames(ASV_df)[] <-  sub("_S.*", "", colnames(ASV_df)[]) #simplifying the names of columns
ASV_df2<-ASV_df[!grepl('Chloroplast', ASV_df$taxonomy),]#8558 obs 276 variables #remove Chloroplasts
ASV_df3<-ASV_df2[!grepl('Mitochondria', ASV_df2$taxonomy),]##8449 obs 276 variables variables #remove Mitochondria
ASV_df4<-ASV_df3[!grepl('Eukaryota', ASV_df3$taxonomy),]##8440 obs 276 variables variables #remove Eukaryotes

#Select only samples from the plant experiment
ASV_df5 <- ASV_df4[, !grepl(c('MI.M'), names(ASV_df4)), drop = FALSE]
#8440 obs 106 variables
#removing taxonomy column
ASV_df_notaxo <- ASV_df5[,c(1:105)]
tax<-ASV_df5%>%select("taxonomy")
#Remove absent taxa
ASVdf6<-ASV_df_notaxo[!rowSums(ASV_df_notaxo[])==0,] # 8348 obs 105 variables

# Merge taxonomy data with ASV_df based on common_id
ASVdf_tax <- merge(ASVdf6, tax, by = "row.names", all.x = TRUE) 
rownames(ASVdf_tax)<-ASVdf_tax$Row.names
ASVdf_tax<-ASVdf_tax[,-1] #8348 obs. 105 variables

mapping_df<-read.table(file=here("Raw_Data","mapping_file.tsv"), row.names=1, header=T, sep="\t", comment.char = "", check.names = F) #105 obs. 5 variables

taxa<-ASVdf_tax%>%select("taxonomy") #8369 obs.
```

```{r}
Arabi_map<-mapping_df[mapping_df$Plant=='Arabidopsis',]
Roots_map<-Arabi_map[Arabi_map$Compartment=='Endosphere',]
root_samples<-row.names(Roots_map)

Root_ASVs<-ASVdf6 %>% select(names(.)[names(.) %in% root_samples])
```

#Hellinger transformation and subsetting mix miRNAs
Hellinger transformation on the abundance data frame. To transform this data it is important to transpose(rotate) the data frame.
```{r}
rotate_asv_df_16S <- t(Root_ASVs)
rotate_asv_df_16S <- decostand(rotate_asv_df_16S, method="hellinger")
```

#Perform PCA
Using the function rda() without precising explanatory variables will calculate the principle components. 
```{r}
#PCA All 5 mirNAs
pca.16S_plantexp<-rda (rotate_asv_df_16S )
#verifying if we can interpret Pc1 and PC2
rdaaxe2<-rda(rotate_asv_df_16S, pca.16S_plantexp$CA$u[,2],pca.16S_plantexp$CA$u[,1])
anova(rdaaxe2) # 0.002 ***
#broken stick model
screeplot(pca.16S_plantexp, bstick = TRUE, type = "lines")

```

#Extract Principle components
```{r}
#Selecting the appropriate scaling
ii_16S_plantexp<-summary(pca.16S_plantexp)
scale1_16S_plantexp<-scores(pca.16S_plantexp, choices = 1:2, scaling=1)
#compiling site scores (scaling 1) 
stmat1_16S_plantexp<-as.data.frame(scale1_16S_plantexp$sites)
stmat1en_16S_plantexp<-cbind(Row.Names = rownames(stmat1_16S_plantexp), stmat1_16S_plantexp)

```

#Preparing data frame for ordination
Here we need to join our explanatory variables and our principle components
```{r}
#DF_ordi
df_16S_plantexp<- merge(stmat1en_16S_plantexp, Roots_map,by = 'row.names')

df_16S_plantexp<-  df_16S_plantexp %>%
  mutate(across(Nitrogen, str_replace, "No.Added.Nitrogen", 'Low N'))

df_16S_plantexp <- df_16S_plantexp %>%
  mutate(across(Nitrogen, str_replace, "Amino.Acids", 'AA'))


```

#PCA ordination
```{r}

pca.ordi_16S_plantexp<-ggplot() +
   geom_point(data = df_16S_plantexp, aes(PC1, PC2), color = "grey70", size = 6.5, stroke = 1) +
  geom_point(data = df_16S_plantexp,aes(PC1,PC2, color=Nitrogen),size=6, alpha=0.8)+
  scale_color_manual(values = c("grey30","#f95d6a","#0a2463"))+
  labs(x=paste("PC1 (", format(100 *ii_16S_plantexp$cont[[1]][2,1], digits=4), "%)", sep=""),
       y=paste("PC2 (", format(100 *ii_16S_plantexp$cont[[1]][2,2], digits=4), "%)", sep=""))+
theme_classic()
pca.ordi_16S_plantexp
pca.ordi_16S_plantexp.2<-pca.ordi_16S_plantexp+theme(legend.text = element_text(size=12))+ theme(axis.title = element_text(size = 13))+
theme(legend.title = element_text(size=14)) +theme(plot.title = element_text(hjust = 0.5))
pca.ordi_16S_plantexp.2
ggsave(pca.ordi_16S_plantexp.2, file=here("Output","Ordination","PCA_root_16S_plantexp.tiff"),units="cm", width=20, height=15, compression='lzw')
saveRDS(pca.ordi_16S_plantexp.2,file=here("Output","Ordination","PCA_root_16S_plantexp.rds"))
```








# To run the PCA on all samples
#Hellinger transformation and subsetting mix miRNAs
Hellinger transformation on the abundance data frame. To transform this data it is important to transpose(rotate) the data frame.
```{r Hellinger and subsetting}
rotate_asv_df_16S <- t(ASVdf6)
rotate_asv_df_16S <- decostand(rotate_asv_df_16S, method="hellinger")
```


#Perform PCA
Using the function rda() without precising explanatory variables will calculate the principle components. 
```{r}
#PCA All 5 mirNAs
pca.16S_plantexp<-rda (rotate_asv_df_16S )
#verifying if we can interpret Pc1 and PC2
rdaaxe2<-rda(rotate_asv_df_16S, pca.16S_plantexp$CA$u[,2],pca.16S_plantexp$CA$u[,1])
anova(rdaaxe2) # 0.001 ***
#broken stick model
screeplot(pca.16S_plantexp, bstick = TRUE, type = "lines")

```

#Extract Principle components
```{r}
#Components for the exposure to all 5 miRNAs
ii_16S_plantexp<-summary(pca.16S_plantexp)
scale1_16S_plantexp<-scores(pca.16S_plantexp, choices = 1:2, scaling=1)
#compiling site scores (scaling 1) 
stmat1_16S_plantexp<-as.data.frame(scale1_16S_plantexp$sites)
stmat1en_16S_plantexp<-cbind(Row.Names = rownames(stmat1_16S_plantexp), stmat1_16S_plantexp)

```

#Preparing data frame for ordination
Here we need to join our explanatory variables and our principle components
```{r}
#DF_ordi
df_16S_plantexp<- merge(stmat1en_16S_plantexp, mapping_df,by = 'row.names')
df_16S_plantexp$'Compartments and plant species' <- paste(df_16S_plantexp$Compartment,df_16S_plantexp$Plant ) # 105 obs. 10 variables
```

#PCA ordination: exposure to 5 miRNAs
```{r}

pca.ordi_16S_plantexp<-ggplot() +
  geom_point(data = df_16S_plantexp,aes(PC1,PC2,shape=Nitrogen,fill=`Compartments and plant species`), color="grey",size=6, stroke=1)+
  scale_fill_manual(values = c("#FB9A99", "#E31A1C", "#FDBF6F", "#A6CEE3","#1F78B4", "#B2DF8A", "#33A02C"))+
  scale_shape_manual(values=c(21,22,23))+
  labs(x=paste("PC1 (", format(100 *ii_16S_plantexp$cont[[1]][2,1], digits=4), "%)", sep=""),
       y=paste("PC2 (", format(100 *ii_16S_plantexp$cont[[1]][2,2], digits=4), "%)", sep=""))+
  guides(shape=guide_legend(title="miRNA treatment"))+
  guides(fill = guide_legend(title="Amino acids",override.aes = list(shape = 21)))+
theme_classic()
pca.ordi_16S_plantexp
pca.ordi_16S_plantexp.2<-pca.ordi_16S_plantexp+theme(legend.text = element_text(size=12))+ theme(axis.title = element_text(size = 13))+
theme(legend.title = element_text(size=14)) +theme(plot.title = element_text(hjust = 0.5))
pca.ordi_16S_plantexp.2
ggsave(pca.ordi_16S_plantexp.2, file=here("Output","Ordination","PCA_16S_plantexp.tiff"),units="cm", width=20, height=15, compression='lzw')
```

