---
title: "2_Acinetobacter_AA"
author: "Jessica A. Dozois"
date: "2025-01-20"
output: html_document
---

#Loading librairies
```{r Librairies}
install.packages("pacman")
pacman::p_load(data.table,ggplot2,dplyr,forcats,here,ggpubr,car,rstatix,gridExtra,,pracma)
```

#Creating folders
```{r}
dir.create(file.path("Output", "Figures"), recursive=TRUE)
dir.create(file.path("Output", "t.test_results", "Growth_curves"), recursive=TRUE)
```

#Importation
```{r setup, include=FALSE}
ReplicaAB<- read.table(file.path("Raw_Data", "Acinetobacter","Acineto_AB.txt"), header = TRUE, sep="\t") #142 obs. 8 var.
ReplicaCDE<- read.table(file.path("Raw_Data", "Acinetobacter","Acineto_CDE.txt"), header = TRUE, sep="\t") #234 obs. 8 var.


```

#Standard curves for each Assay (540nm) 

```{r}
##ASSAY AB
samplesAB<-ReplicaAB[!ReplicaAB$Treatment=="std",]
samplesAB1<-samplesAB[samplesAB$Plate=="1",]
samplesAB2<-samplesAB[samplesAB$Plate=="2",]

#Standard curves plates AB
standardsAB<- ReplicaAB[ReplicaAB$Treatment=="std",]

standardsAB1<-standardsAB[standardsAB$Plate=="1",]
standardsAB1$N_Source<-as.numeric((standardsAB1$N_Source))
standardsAB1<-standardsAB1[!standardsAB1$N_Source=="500",]

nm540AB1<- ggplot(standardsAB1, aes(x=N_Source, y=OD540))+
  labs( y="Optical Density (540nm)", x="Concentration of L-AAs (uM)")+
  geom_point()+stat_cor(label.y=0.75, r.accuracy = 0.0001)+
  stat_regline_equation(label.y= 0.7)+
 geom_smooth(method = "lm", alpha=.15, colour='purple') +
  theme_bw()+
  ggtitle('Acinetobacter AB1')
nm540AB1 


standardsAB2<-standardsAB[standardsAB$Plate=="2",]
standardsAB2$N_Source<-as.numeric((standardsAB2$N_Source))
standardsAB2<-standardsAB2[!standardsAB2$N_Source=="500",]

nm540AB2<- ggplot(standardsAB2, aes(x=N_Source, y=OD540))+
  labs( y="Optical Density (540nm)", x="Concentration of L-AAs (uM)")+
  geom_point()+stat_cor(label.y=0.75, r.accuracy = 0.0001)+
  stat_regline_equation(label.y= 0.7)+
 geom_smooth(method = "lm", alpha=.15, colour='purple') +
  theme_bw()+
  ggtitle('Acinetobacter AB2')
nm540AB2 


##ASSAY CDE
samplesCDE<-ReplicaCDE[!ReplicaCDE$Treatment=="std",]
samplesCDE1<-samplesCDE[samplesCDE$Plate=="1",]
samplesCDE2<-samplesCDE[samplesCDE$Plate=="2",]
samplesCDE3<-samplesCDE[samplesCDE$Plate=="3",]

#Standard curves plates CDE
standardsCDE<- ReplicaCDE[ReplicaCDE$Treatment=="std",]

standardsCDE1<-standardsCDE[standardsCDE$Plate=="1",]
standardsCDE1$N_Source<-as.numeric((standardsCDE1$N_Source))
standardsCDE1<-standardsCDE1[!standardsCDE1$N_Source=="500",]

nm540CDE1<- ggplot(standardsCDE1, aes(x=N_Source, y=OD540))+
  labs( y="Optical Density (540nm)", x="Concentration of L-AAs (uM)")+
  geom_point()+stat_cor(label.y=0.75, r.accuracy = 0.0001)+
  stat_regline_equation(label.y= 0.7)+
 geom_smooth(method = "lm", alpha=.15, colour='purple') +
  theme_bw()+
  ggtitle('Acinetobacter CDE1')
nm540CDE1 


standardsCDE2<-standardsCDE[standardsCDE$Plate=="2",]
standardsCDE2$N_Source<-as.numeric((standardsCDE2$N_Source))
standardsCDE2<-standardsCDE2[!standardsCDE2$N_Source=="500",]

nm540CDE2<- ggplot(standardsCDE2, aes(x=N_Source, y=OD540))+
  labs( y="Optical Density (540nm)", x="Concentration of L-AAs (uM)")+
  geom_point()+stat_cor(label.y=0.75, r.accuracy = 0.0001)+
  stat_regline_equation(label.y= 0.7)+
 geom_smooth(method = "lm", alpha=.15, colour='purple') +
  theme_bw()+
  ggtitle('Acinetobacter CDE2')
nm540CDE2 


standardsCDE3<-standardsCDE[standardsCDE$Plate=="3",]
standardsCDE3$N_Source<-as.numeric((standardsCDE3$N_Source))
standardsCDE3<-standardsCDE3[!standardsCDE3$N_Source=="500",]

nm540CDE3<- ggplot(standardsCDE3, aes(x=N_Source, y=OD540))+
  labs( y="Optical Density (540nm)", x="Concentration of L-AAs (uM)")+
  geom_point()+stat_cor(label.y=0.75, r.accuracy = 0.0001)+
  stat_regline_equation(label.y= 0.7)+
 geom_smooth(method = "lm", alpha=.15, colour='purple') +
  theme_bw()+
  ggtitle('Acinetobacter CDE3')
nm540CDE3 

```

#Predicted L-AA
##Assay AB
Predicted L-Amino Acids concentrations of samples based on the standard curve.
```{r}
#Plates AB1 & AB2
standardsAB1$Time <- as.factor(standardsAB1$Time)
modelAB1<-lm(OD540~N_Source,data = standardsAB1)
  modelAB1$coefficients   
 summary(modelAB1)
 
 standardsAB2$Time <- as.factor(standardsAB2$Time)
modelAB2<-lm(OD540~N_Source,data = standardsAB2)
  modelAB2$coefficients   
 summary(modelAB2)
 
#Calculating the concentration of L-AA (uM) that corresponds to measured optical densities
predictedAA_AB1<- ((samplesAB1$OD540-modelAB1$coefficients[1])/modelAB1$coefficients[2])*70
samplesAB1$'Predicted_AA_Concentration'<-predictedAA_AB1

predictedAA_AB2<- ((samplesAB2$OD540-modelAB2$coefficients[1])/modelAB2$coefficients[2])*70
samplesAB2$'Predicted_AA_Concentration'<-predictedAA_AB2

#Plates CDE1, CDE2, CDE3
standardsCDE1$Time <- as.factor(standardsCDE1$Time)
modelCDE1<-lm(OD540~N_Source,data = standardsCDE1)
  modelCDE1$coefficients   
 summary(modelCDE1)
 
 standardsCDE2$Time <- as.factor(standardsCDE2$Time)
modelCDE2<-lm(OD540~N_Source,data = standardsCDE2)
  modelCDE2$coefficients   
 summary(modelCDE2)
 
 standardsCDE3$Time <- as.factor(standardsCDE3$Time)
modelCDE3<-lm(OD540~N_Source,data = standardsCDE3)
  modelCDE3$coefficients   
 summary(modelCDE3)
 
 #Calculating the concentration of L-AA (uM) that corresponds to measured optical densities
predictedAA_CDE1<- ((samplesCDE1$OD540-modelCDE1$coefficients[1])/modelCDE1$coefficients[2])*70
samplesCDE1$'Predicted_AA_Concentration'<-predictedAA_CDE1

predictedAA_CDE2<- ((samplesCDE2$OD540-modelCDE2$coefficients[1])/modelCDE2$coefficients[2])*70
samplesCDE2$'Predicted_AA_Concentration'<-predictedAA_CDE2

predictedAA_CDE3<- ((samplesCDE3$OD540-modelCDE3$coefficients[1])/modelCDE3$coefficients[2])*70
samplesCDE3$'Predicted_AA_Concentration'<-predictedAA_CDE3
```

#Combining technical replicates
```{r}
#AB
combined_data_AB <- merge(samplesAB1[, c("Time", "Pair","Treatment", "miRNA", "Predicted_AA_Concentration")], 
                       samplesAB2[, c("Time", "Pair","Treatment", "miRNA", "Predicted_AA_Concentration")], 
                       by = c("Time", "Pair","Treatment", "miRNA"), 
                       suffixes = c("_AB1", "_AB2"))

#Changing negative values to zero
combined_data_AB$Predicted_AA_Concentration_AB2[combined_data_AB$Predicted_AA_Concentration_AB2 < 0] <- 0

#Calculate the mean predicted AA concentration for each qualitative variable
combined_data_AB$Mean_Predicted_AA <- rowMeans(combined_data_AB[, c("Predicted_AA_Concentration_AB1", "Predicted_AA_Concentration_AB2")], na.rm = TRUE)

#CDE
# Merge the dataframes
combined_data_CDE <- merge(
  merge(
    samplesCDE1[, c("Time", "Pair", "Treatment", "miRNA", "Predicted_AA_Concentration")],
    samplesCDE2[, c("Time", "Pair", "Treatment", "miRNA", "Predicted_AA_Concentration")],
    by = c("Time", "Pair", "Treatment", "miRNA"),
    suffixes = c("_CDE1", "_CDE2"),
    all = TRUE
  ),
  samplesCDE3[, c("Time", "Pair", "Treatment", "miRNA", "Predicted_AA_Concentration")],
  by = c("Time", "Pair", "Treatment", "miRNA"),
  suffixes = c("_CDE12", "_CDE3"),
  all = TRUE
)



#Calculate the mean predicted AA concentration for each qualitative variablele
combined_data_CDE <- combined_data_CDE %>%
  mutate( Mean_Predicted_AA = rowMeans(
    data.frame(Predicted_AA_Concentration_CDE1, 
               Predicted_AA_Concentration_CDE2, 
               Predicted_AA_Concentration),
    na.rm = TRUE
  ))


```

#Merging all replicas
```{r}
AAAcineto<- rbind(combined_data_AB[, c("Treatment", "Time", "miRNA", "Pair", "Mean_Predicted_AA")], 
                   combined_data_CDE[, c("Treatment", "Time", "miRNA", "Pair", "Mean_Predicted_AA")])
```


##Paired Ttests for each timepoint
```{r}
AAAcineto_noctl<-AAAcineto[!AAAcineto$Treatment=='control',]

AAAcineto_noctl$Treatment<-recode_factor(AAAcineto_noctl$Treatment, scramble= "Scramble miRNAs",plant="Plant miRNAs" )

AAAcineto_noctl$Time<-as.factor(AAAcineto_noctl$Time)
loop<-levels(AAAcineto_noctl$Time)

AAAcineto_158b<-AAAcineto_noctl[AAAcineto_noctl$miRNA=='ath-mir158b',]
AAAcineto_mixmiR5<-AAAcineto_noctl[AAAcineto_noctl$miRNA=='mix5miR',]
AAAcineto_5642<-AAAcineto_noctl[AAAcineto_noctl$miRNA=='ath-miR5642b',]



#mir158b
for(i in 1:4) 
{
Timepoint<-AAAcineto_158b[AAAcineto_158b$Time==loop[i],]
plant<- Timepoint[Timepoint$Treatment=="Plant miRNAs",]
planto<-plant[order(plant$Pair),]
mirplant<-planto$Mean_Predicted_AA
scram<- Timepoint[Timepoint$Treatment=="Scramble miRNAs",]
scramo<-scram[order(scram$Pair),]
mirscram<-scramo$Mean_Predicted_AA
differences<- as.data.frame(mirscram - mirplant)
outliers<-identify_outliers(differences) 
test<-shapiro_test(differences$`mirscram - mirplant`)
{
  if(nrow(outliers)>=1|test$p.value < 0.05)
    cat("Time:",loop[i]," ","p.value :", test$p.value, " ","Statistic:", test$statistic,"Outliers:",outliers$is.outlier,"\n", file=here("Output","t.test_results","Assump_AA_Acineto_158b.txt"), append=T) 
  } 
 i=i+1}

for(i in 1:4) 
{
Timepoint<-AAAcineto_158b[AAAcineto_158b$Time==loop[i],]
plant<- Timepoint[Timepoint$Treatment=="Plant miRNAs",]
planto<-plant[order(plant$Pair),]
mirplant<-planto$Mean_Predicted_AA
scram<- Timepoint[Timepoint$Treatment=="Scramble miRNAs",]
scramo<-scram[order(scram$Pair),]
mirscram<-scramo$Mean_Predicted_AA
test<-t.test(mirplant, mirscram, paired = TRUE, alternative = "two.sided")
{
  if(test$p.value < 0.05)
    cat("Time:",loop[i]," ","p.value :", test$p.value, " ","statistic:", test$statistic, "\n", file=here("Output","t.test_results","Acineto_T_158b.txt"), append=T) 
  } 
 i=i+1} #


#mixmir5
for(i in 1:4) 
{
Timepoint<-AAAcineto_mixmiR5[AAAcineto_mixmiR5$Time==loop[i],]
plant<- Timepoint[Timepoint$Treatment=="Plant miRNAs",]
planto<-plant[order(plant$Pair),]
mirplant<-planto$Mean_Predicted_AA
scram<- Timepoint[Timepoint$Treatment=="Scramble miRNAs",]
scramo<-scram[order(scram$Pair),]
mirscram<-scramo$Mean_Predicted_AA
differences<- as.data.frame(mirscram - mirplant)
outliers<-identify_outliers(differences) 
test<-shapiro_test(differences$`mirscram - mirplant`)
{
  if(nrow(outliers)>=1|test$p.value < 0.05)
    cat("Time:",loop[i]," ","p.value :", test$p.value, " ","Statistic:", test$statistic,"Outliers:",outliers$is.outlier,"\n", file=here("Output","t.test_results","Assump_AA_Acineto_mixmiR5.txt"), append=T) 
  } 
 i=i+1}

i=0 
for(i in 1:4) 
{
Timepoint<-AAAcineto_mixmiR5[AAAcineto_mixmiR5$Time==loop[i],]
plant<- Timepoint[Timepoint$Treatment=="Plant miRNAs",]
planto<-plant[order(plant$Pair),]
mirplant<-planto$Mean_Predicted_AA
scram<- Timepoint[Timepoint$Treatment=="Scramble miRNAs",]
scramo<-scram[order(scram$Pair),]
mirscram<-scramo$Mean_Predicted_AA
test<-t.test(mirplant, mirscram, paired = TRUE, alternative = "less")
{
  if(test$p.value < 0.05)
    cat("Time:",loop[i]," ","p.value :", test$p.value, " ","statistic:", test$statistic, "\n", file=here("Output","t.test_results","Acineto_T_mixmiR5_less.txt"), append=T) 
  }
 i=i+1}

#mir5642
for(i in 1:4) 
{
Timepoint<-AAAcineto_5642[AAAcineto_5642$Time==loop[i],]
plant<- Timepoint[Timepoint$Treatment=="Plant miRNAs",]
planto<-plant[order(plant$Pair),]
mirplant<-planto$Mean_Predicted_AA
scram<- Timepoint[Timepoint$Treatment=="Scramble miRNAs",]
scramo<-scram[order(scram$Pair),]
mirscram<-scramo$Mean_Predicted_AA
differences<- as.data.frame(mirscram - mirplant)
outliers<-identify_outliers(differences) 
test<-shapiro_test(differences$`mirscram - mirplant`)
{
  if(nrow(outliers)>=1|test$p.value < 0.05)
    cat("Time:",loop[i]," ","p.value :", test$p.value, " ","Statistic:", test$statistic,"Outliers:",outliers$is.outlier,"\n", file=here("Output","t.test_results","Assump_AA_Acineto_5642.txt"), append=T) 
  } 
 i=i+1}

i=0 
for(i in 1:4) 
{
Timepoint<-AAAcineto_5642[AAAcineto_5642$Time==loop[i],]
plant<- Timepoint[Timepoint$Treatment=="Plant miRNAs",]
planto<-plant[order(plant$Pair),]
mirplant<-planto$Mean_Predicted_AA
scram<- Timepoint[Timepoint$Treatment=="Scramble miRNAs",]
scramo<-scram[order(scram$Pair),]
mirscram<-scramo$Mean_Predicted_AA
test<-t.test(mirplant, mirscram, paired = TRUE, alternative = "less")
{
  if(test$p.value < 0.05)
    cat("Time:",loop[i]," ","p.value :", test$p.value, " ","statistic:", test$statistic, "\n", file=here("Output","t.test_results","Acineto_T_5642_less.txt"), append=T) 
  }
 i=i+1}

```

##AA Consumption AUC
```{r}
# Calculate AUC using the trapz function
# Define a custom AUC calculation function
calculate_auc <- function(data, x_col, y_col) {
  x <- data[[x_col]]  # Date column
  y <- data[[y_col]]  # Data column
  trapz(x, y)  # Calculate AUC using trapezoidal rule
}

#ath-miR158b
AAAcineto_158b$Time <- as.numeric(AAAcineto_158b$Time) 
# Select columns with data for AUC calculation
data_cols <- names(AAAcineto_158b)[5]  # Adjust to match your data column range
# Group by isolate and block
AUC_AAAcineto_158b<- AAAcineto_158b %>%
  group_by(Pair, Treatment) %>%
  summarise(
    across(all_of(data_cols), ~ calculate_auc(cur_data(), "Time", cur_column()), .names = "AUC_{.col}")
  )

#ath-miR5642b
AAAcineto_5642$Time <- as.numeric(AAAcineto_5642$Time) 
# Select columns with data for AUC calculation
data_cols <- names(AAAcineto_5642)[5]  # Adjust to match your data column range
# Group by isolate and block
AUC_AAAcineto_5642<- AAAcineto_5642 %>%
  group_by(Pair, Treatment) %>%
  summarise(
    across(all_of(data_cols), ~ calculate_auc(cur_data(), "Time", cur_column()), .names = "AUC_{.col}")
  )

#ath-miRMix5
AAAcineto_mixmiR5$Time <- as.numeric(AAAcineto_mixmiR5$Time) 
# Select columns with data for AUC calculation
data_cols <- names(AAAcineto_mixmiR5)[5]  # Adjust to match your data column range
# Group by isolate and block
AUC_AAAcineto_Mix5<- AAAcineto_mixmiR5 %>%
  group_by(Pair, Treatment) %>%
  summarise(
    across(all_of(data_cols), ~ calculate_auc(cur_data(), "Time", cur_column()), .names = "AUC_{.col}")
  )

```


#Growth of Acinetobacter
##Importation
```{r}
GrowthData<- read.table(file.path("Raw_Data", "Acinetobacter","Acineto_Growth.txt"), header = TRUE, sep="\t") #160 obs. 6 var.
GrowthData$Time<-as.factor(GrowthData$Time)
GrowthData$Pair<-as.factor(GrowthData$Pair)
```

#Subsetting by miRNA
```{r}
Growth158b<-GrowthData[GrowthData$miRNA=="158b",]
Growth5642b<-GrowthData[GrowthData$miRNA=="5642b",]
GrowthMix5<-GrowthData[GrowthData$miRNA=="Mix5",]
```


#Statistical Tests
```{r}
loop<-levels(GrowthData$Time)
#ath-miR158b
i=0 
for(i in 1:4) 
{
Timepoint<-Growth158b[Growth158b$Time==loop[i],]
plant<- Timepoint[Timepoint$Treatment=="Plant",]
planto<-plant[order(plant$Pair),]
mirplant<-planto$OD600
scram<- Timepoint[Timepoint$Treatment=="Scramble",]
scramo<-scram[order(scram$Pair),]
mirscram<-scramo$OD600
differences<- as.data.frame(mirscram - mirplant)
outliers<-identify_outliers(differences) 
test<-shapiro_test(differences$`mirscram - mirplant`)
{
  if(nrow(outliers)>=1|test$p.value < 0.05)
    cat("Time:",loop[i]," ","p.value :", test$p.value, " ","Statistic:", test$statistic,"Outliers:",outliers$is.outlier,"\n", file=here("Output","t.test_results","Growth_curves","Acineto_Assump_158b.txt"), append=T) 
  } 
 i=i+1}

i=0 
for(i in 1:4) 
{
Timepoint<-Growth158b[Growth158b$Time==loop[i],]
plant<- Timepoint[Timepoint$Treatment=="Plant",]
planto<-plant[order(plant$Pair),]
mirplant<-planto$OD600
scram<- Timepoint[Timepoint$Treatment=="Scramble",]
scramo<-scram[order(scram$Pair),]
mirscram<-scramo$OD600
test<-t.test(mirplant, mirscram, paired = TRUE, alternative = "two.sided")
{
  if(test$p.value < 0.05)
    cat("Time:",loop[i]," ","p.value :", test$p.value, " ","statistic:", test$statistic, "\n", file=here("Output","t.test_results","Growth_curves","Acineto_158b_t.test.txt"), append=T) 
  } 
 i=i+1} #nothing significant

#ath-miR5642b
i=0 
for(i in 1:4) 
{
Timepoint<-Growth5642b[Growth5642b$Time==loop[i],]
plant<- Timepoint[Timepoint$Treatment=="Plant",]
planto<-plant[order(plant$Pair),]
mirplant<-planto$OD600
scram<- Timepoint[Timepoint$Treatment=="Scramble",]
scramo<-scram[order(scram$Pair),]
mirscram<-scramo$OD600
differences<- as.data.frame(mirscram - mirplant)
outliers<-identify_outliers(differences) 
test<-shapiro_test(differences$`mirscram - mirplant`)
{
  if(nrow(outliers)>=1|test$p.value < 0.05)
    cat("Time:",loop[i]," ","p.value :", test$p.value, " ","Statistic:", test$statistic,"Outliers:",outliers$is.outlier,"\n", file=here("Output","t.test_results","Growth_curves","Acineto_Assump_5642b.txt"), append=T) 
  } 
 i=i+1}

i=0 
for(i in 1:4) 
{
Timepoint<-Growth5642b[Growth5642b$Time==loop[i],]
plant<- Timepoint[Timepoint$Treatment=="Plant",]
planto<-plant[order(plant$Pair),]
mirplant<-planto$OD600
scram<- Timepoint[Timepoint$Treatment=="Scramble",]
scramo<-scram[order(scram$Pair),]
mirscram<-scramo$OD600
test<-t.test(mirplant, mirscram, paired = TRUE, alternative = "two.sided")
{
  if(test$p.value < 0.05)
    cat("Time:",loop[i]," ","p.value :", test$p.value, " ","statistic:", test$statistic, "\n", file=here("Output","t.test_results","Growth_curves","Acineto_5642b_t.test.txt"), append=T) 
  } 
 i=i+1} #nothing significant


#Mix 5
i=0 
for(i in 1:4) 
{
Timepoint<-GrowthMix5[GrowthMix5$Time==loop[i],]
plant<- Timepoint[Timepoint$Treatment=="Plant",]
planto<-plant[order(plant$Pair),]
mirplant<-planto$OD600
scram<- Timepoint[Timepoint$Treatment=="Scramble",]
scramo<-scram[order(scram$Pair),]
mirscram<-scramo$OD600
differences<- as.data.frame(mirscram - mirplant)
outliers<-identify_outliers(differences) 
test<-shapiro_test(differences$`mirscram - mirplant`)
{
  if(nrow(outliers)>=1|test$p.value < 0.05)
    cat("Time:",loop[i]," ","p.value :", test$p.value, " ","Statistic:", test$statistic,"Outliers:",outliers$is.outlier,"\n", file=here("Output","t.test_results","Growth_curves","Acineto_Assump_Mix5.txt"), append=T) 
  } 
 i=i+1}

i=0 
for(i in 1:4) 
{
Timepoint<-GrowthMix5[GrowthMix5$Time==loop[i],]
plant<- Timepoint[Timepoint$Treatment=="Plant",]
planto<-plant[order(plant$Pair),]
mirplant<-planto$OD600
scram<- Timepoint[Timepoint$Treatment=="Scramble",]
scramo<-scram[order(scram$Pair),]
mirscram<-scramo$OD600
test<-t.test(mirplant, mirscram, paired = TRUE, alternative = "two.sided")
{
  if(test$p.value < 0.05)
    cat("Time:",loop[i]," ","p.value :", test$p.value, " ","statistic:", test$statistic, "\n", file=here("Output","t.test_results","Growth_curves","Acineto_Mix5_t.test.txt"), append=T) 
  } 
 i=i+1} #nothing significant

```

##Growth AUC
```{r}
# Calculate AUC using the trapz function
# Define a custom AUC calculation function
calculate_auc <- function(data, x_col, y_col) {
  x <- data[[x_col]]  # Date column
  y <- data[[y_col]]  # Data column
  trapz(x, y)  # Calculate AUC using trapezoidal rule
}

#ath-miR158b
Growth158b$Time <- as.numeric(Growth158b$Time) 
# Select columns with data for AUC calculation
data_cols <- names(Growth158b)[6]  # Adjust to match your data column range
# Group by isolate and block
AUC_Growth_158b<- Growth158b %>%
  group_by(Pair, Treatment) %>%
  summarise(
    across(all_of(data_cols), ~ calculate_auc(cur_data(), "Time", cur_column()), .names = "AUC_{.col}")
  )


#ath-miR5642b
Growth5642b$Time <- as.numeric(Growth5642b$Time) 
# Select columns with data for AUC calculation
data_cols <- names(Growth5642b)[6]  # Adjust to match your data column range
# Group by isolate and block
AUC_Growth_5642b<- Growth5642b %>%
  group_by(Pair, Treatment) %>%
  summarise(
    across(all_of(data_cols), ~ calculate_auc(cur_data(), "Time", cur_column()), .names = "AUC_{.col}")
  )

#Mix5
GrowthMix5$Time <- as.numeric(GrowthMix5$Time) 
# Select columns with data for AUC calculation
data_cols <- names(GrowthMix5)[6]  # Adjust to match your data column range
# Group by isolate and block
AUC_Growth_Mix5<- GrowthMix5 %>%
  group_by(Pair, Treatment) %>%
  summarise(
    across(all_of(data_cols), ~ calculate_auc(cur_data(), "Time", cur_column()), .names = "AUC_{.col}")
  )

```


#Merging Growth data and consumption data
```{r}
AAAcineto_158b$miRNA<-recode_factor(AAAcineto_158b$miRNA, 'ath-mir158b'="ath-miR158b")
AAAcineto_mixmiR5$miRNA<-recode_factor(AAAcineto_mixmiR5$miRNA, mix5miR="Mix of 5")

Growth158b$miRNA<-recode_factor(Growth158b$miRNA, '158b'="ath-miR158b")
Growth158b$Treatment<-recode_factor(Growth158b$Treatment, Plant="Plant miRNAs", Scramble= "Scramble miRNAs")

Growth5642b$miRNA<-recode_factor(Growth5642b$miRNA, '5642b'="ath-miR5642b")
Growth5642b$Treatment<-recode_factor(Growth5642b$Treatment, Plant="Plant miRNAs", Scramble= "Scramble miRNAs")

GrowthMix5$Treatment<-recode_factor(GrowthMix5$Treatment, Plant="Plant miRNAs", Scramble= "Scramble miRNAs")
GrowthMix5$miRNA <- recode_factor(GrowthMix5$miRNA, Mix5="Mix of 5")

# Define the desired column order
columns <- c("Time", "miRNA", "Treatment", "Pair")

#ath-miR158b
# Reorder columns in both dataframes
Growth158b <- Growth158b[, c(columns, setdiff(names(Growth158b), columns))]
AAAcineto_158b <- AAAcineto_158b[, c(columns, setdiff(names(AAAcineto_158b),columns))]
# Merge the dataframes
All158b <- merge(Growth158b, AAAcineto_158b, by = c("Time", "miRNA", "Pair", "Treatment"), all = TRUE) 


#ath-miR5642b
# Reorder columns in both dataframes
Growth5642b <- Growth5642b[, c(columns, setdiff(names(Growth5642b), columns))]
AAAcineto_5642 <- AAAcineto_5642[, c(columns, setdiff(names(AAAcineto_5642),columns))]
# Merge the dataframes
All5642b <- merge(Growth5642b, AAAcineto_5642, by = c("Time", "miRNA", "Pair", "Treatment"), all = TRUE)

# Mix of 5 
# Reorder columns in both dataframes
GrowthMix5 <- GrowthMix5[, c(columns, setdiff(names(GrowthMix5), columns))]
AAAcineto_mixmiR5 <- AAAcineto_mixmiR5[, c(columns, setdiff(names(AAAcineto_mixmiR5),columns))]
# Merge the dataframes
AllMix5 <- merge(GrowthMix5, AAAcineto_mixmiR5, by = c("Time", "miRNA", "Pair", "Treatment"), all = TRUE)

```


#Dual Y axis ath-miR158b
```{r}
coeff<- 40000
boxAcineto158b<- ggplot(All158b) +
    stat_summary(mapping=aes(x=Time, y=OD600,color=Treatment,group=Treatment, linetype =Treatment),fun = mean,geom='line',position = position_dodge(0.2)) +
    stat_summary(mapping=aes(x=Time, y=OD600,color=Treatment,group=Treatment), fun=mean,geom='point',position = position_dodge(0.2))+
  stat_summary(mapping=aes(x=Time, y=OD600,color=Treatment,group=Treatment),fun.data=mean_cl_boot,
        geom='errorbar',
        width=0.1,position = position_dodge(0.2))+
  #Adding data of AA consumption
  stat_summary(mapping=aes(x=Time, y=Mean_Predicted_AA/coeff,group=Treatment,linetype=Treatment),fun = mean,geom='line',position = position_dodge(0.2)) +
    stat_summary(mapping=aes(x=Time, y=Mean_Predicted_AA/coeff,group=Treatment),fun=mean,geom='point',position = position_dodge(0.2))+
  stat_summary(mapping=aes(x=Time, y=Mean_Predicted_AA/coeff,group=Treatment),fun.data=mean_cl_boot,geom='errorbar',width=0.1,position = position_dodge(0.2))+
  scale_linetype_manual(name = "Treatement",values=c("solid", "twodash"))+
  scale_y_continuous(name="", sec.axis = sec_axis(~.*coeff,name="")) +
  scale_color_manual(name="",values = c("darkslategray4","lightcyan3"))+
  labs(x = "", color="",fill="", group="",linetype="Treatement", shape="")+
 theme_pubr()+theme( axis.text.y = element_text(color = "darkslategray4"),
    axis.text.y.right = element_text(color = "black"),
  legend.title = element_text(size=12),
   legend.text = element_text(size=12)
  )+ggtitle("Acinetobacter ath-miR158b")+theme(plot.title = element_text(hjust = 0.005, size=20))+ theme(legend.position = "none")   
  grow_consume158b<-ggpar( boxAcineto158b,ylim = c(0.0, 0.5))
  
  grow_consume158b<-annotate_figure( grow_consume158b,
           bottom = text_grob("Time (hours)", size = 12),
            left = text_grob("Optical density (600 nm)",size = 12, rot=90, color = "darkslategray4"),
          right= text_grob("L-amino acid concentration (μM)",size = 12, rot=270))
    grow_consume158b
```

#Dual Y axis ath-miR5642b
```{r}
coeff<- 40000
boxAcineto5642b<- ggplot(All5642b) +
    stat_summary(mapping=aes(x=Time, y=OD600,color=Treatment,group=Treatment, linetype =Treatment),fun = mean,geom='line',position = position_dodge(0.2)) +
    stat_summary(mapping=aes(x=Time, y=OD600,color=Treatment,group=Treatment), fun=mean,geom='point',position = position_dodge(0.2))+
  stat_summary(mapping=aes(x=Time, y=OD600,color=Treatment,group=Treatment),fun.data=mean_cl_boot,
        geom='errorbar',
        width=0.1,position = position_dodge(0.2))+
  #Adding data of AA consumption
  stat_summary(mapping=aes(x=Time, y=Mean_Predicted_AA/coeff,group=Treatment,linetype=Treatment),fun = mean,geom='line',position = position_dodge(0.2)) +
    stat_summary(mapping=aes(x=Time, y=Mean_Predicted_AA/coeff,group=Treatment),fun=mean,geom='point',position = position_dodge(0.2))+
  stat_summary(mapping=aes(x=Time, y=Mean_Predicted_AA/coeff,group=Treatment),fun.data=mean_cl_boot,geom='errorbar',width=0.1,position = position_dodge(0.2))+
  scale_linetype_manual(name = "Treatement",values=c("solid", "twodash"))+
  scale_y_continuous(name="", sec.axis = sec_axis(~.*coeff,name="")) +
  scale_color_manual(name="",values = c("darkslategray4","lightcyan3"))+
  labs(x = "", color="",fill="", group="",linetype="Treatement", shape="")+
 theme_pubr()+theme( axis.text.y = element_text(color = "darkslategray4"),
    axis.text.y.right = element_text(color = "black"),
  legend.title = element_text(size=18),
   legend.text = element_text(size=18)
  )+ggtitle("Acinetobacter ath-miR5642b")+theme(plot.title = element_text(hjust = 0.005, size=20))+ theme(legend.position = "none")   
  grow_consume5642b<-ggpar( boxAcineto5642b,ylim = c(0.0, 0.45))
    
    grow_consume5642b<-annotate_figure( grow_consume5642b,
           bottom = text_grob("Time (hours)", size = 12),
            left = text_grob("Optical density (600 nm)",size = 12, rot=90, color = "darkslategray4"),
          right= text_grob("L-amino acid concentration (μM)",size = 12, rot=270))
  grow_consume5642b
```


#Dual Y axis Mix of 5
```{r}
coeff3<- 42000

# Create a new variable to group color and linetype together
AllMix5$Treatment2 <- factor(AllMix5$Treatment, levels = c("Plant miRNAs", "Scramble miRNAs"))

boxAcinetoMix5<- ggplot(AllMix5) +
    # First plot for OD600: Line, Points, and Error bars with color and linetype based on Treatment2
    stat_summary(mapping=aes(x=Time, y=OD600,color=Treatment2,group=Treatment2,linetype =Treatment2),fun = mean,geom='line',position = position_dodge(0.2)) +
    stat_summary(mapping=aes(x=Time, y=OD600,color=Treatment2,group=Treatment2), fun=mean,geom='point',position = position_dodge(0.2))+
  stat_summary(mapping=aes(x=Time, y=OD600,color=Treatment2,group=Treatment2),fun.data=mean_cl_boot,
        geom='errorbar',
        width=0.1,position = position_dodge(0.2))+
  #Adding data of AA consumption
  stat_summary(mapping=aes(x=Time, y=Mean_Predicted_AA/coeff3,group=Treatment2,linetype=Treatment2),fun = mean,geom='line',position = position_dodge(0.2)) +
    stat_summary(mapping=aes(x=Time, y=Mean_Predicted_AA/coeff3,group=Treatment2),fun=mean,geom='point',position = position_dodge(0.2))+
  stat_summary(mapping=aes(x=Time, y=Mean_Predicted_AA/coeff3,group=Treatment2),fun.data=mean_cl_boot,geom='errorbar',width=0.1,position = position_dodge(0.2))+
  
  # Customize linetypes and colors for Treatment2
  scale_linetype_manual(name = "Treatment", values = c("solid", "twodash")) +  # Solid for Plant miRNAs, dashed for Scramble miRNAs
  scale_color_manual(name = "Treatment", values = c("darkslategray4", "lightcyan3")) +  # darkslategray4 for Plant miRNAs, lightcyan3 for Scramble miRNAs
  
  # Adjust y-axis and add a secondary axis
  scale_y_continuous(name = "", sec.axis = sec_axis(~ . * coeff3, name = "")) +
  
  # Add labels and adjust legend
  labs(x = "Time (hours)", color = "", fill = "", group = "", linetype = "Treatment", shape = "") +
  
  # Apply clean theme
  theme_pubr() + 
  theme(axis.text.y = element_text(color = "darkslategray4"),
        axis.text.y.right = element_text(color = "black"),
        legend.title = element_text(size = 12),
        legend.text = element_text(size = 12)) +
  ggtitle(expression(italic("Acinetobacter") ~ "mix of 5 miRNAs")) +
  theme(plot.title = element_text(hjust = 0.005, size = 14)) + 
  theme(legend.position = "bottom") + 
  annotate("text", x = 4, y = 0.1, label = "*", size = 10) + 
  
  # Merge the color and linetype legends together
  guides(color = guide_legend(order = 1), 
         linetype = guide_legend(order = 1))

# Adjust the plot appearance further
grow_consumeMix5 <- ggpar(boxAcinetoMix5, ylim = c(0.0, 0.5))

# Add annotations for axes
    grow_consumeMix5_2<-annotate_figure(grow_consumeMix5,
           bottom = text_grob("", size = 12),
            left = text_grob("Optical density (600 nm)",size = 12, rot=90, color = "darkslategray4"),
          right= text_grob("L-amino acid concentration (μM)",size = 12, rot=270))
    grow_consumeMix5_2

    ggsave(grow_consumeMix5_2, file=here("Output","Figures","Acineto_grow_consumeMix5.tiff"),width = 15, height = 15, units = "cm", compression='lzw')
    
    grow_consumeMix5_3<-grow_consumeMix5+theme(legend.position = "none")
    saveRDS(grow_consumeMix5_3, file = here("Output","Figures","Acineto_grow_consumeMix5.rds"))
``` 

#Boxplot Mix of 5 miRs and Time 28
```{r}
AAAcineto_mixmiR5_28<-AAAcineto_mixmiR5[AAAcineto_mixmiR5$Time=='28',]
AAAcineto_mixmiR5_28$Pair<-as.factor(AAAcineto_mixmiR5_28$Pair)
boxMix5Acineto<-ggplot(AAAcineto_mixmiR5_28, aes(x=Treatment, y=Mean_Predicted_AA ,fill=Treatment, colour=Treatment)) +geom_boxplot(outlier.shape = NA, alpha=0.4) +
  geom_point(pch = 21, position = position_jitterdodge(0.1))+
 theme_light() + theme(legend.position = "none")+
  scale_fill_manual(values = c("#003049","#2a7f62"))+
scale_colour_manual(values = c("#003049","#2a7f62"))+geom_line(aes(group = Pair), color = "grey50", linetype = "solid", alpha = 0.5)+labs(y="L-amino acid concentration (μM)") 
boxMix5Acineto
```



