---
title: "4_Raoultella_AA"
author: "Jessica A. Dozois"
date: "2025-02-24"
output: html_document
---
#Loading librairies
```{r Librairies}
install.packages("pacman")
pacman::p_load(data.table,ggplot2,dplyr,forcats,here,ggpubr,car,rstatix,gridExtra,pracma)
```

#Creating folders
```{r}
dir.create(file.path("Output", "Figures"), recursive=TRUE)
dir.create(file.path("Output", "t.test_results", "Growth_curves"), recursive=TRUE)
```

#AA Consumption
##Importation
```{r}
All_Raoul_AA<- read.table(file.path("Raw_Data", "Raoultella","Raoul_AA.txt"), header = TRUE, sep="\t") #700 obs. 8 var.
```

##Standard curves for each Assay (540nm) 

```{r}
##ASSAY A
Assay_A<-All_Raoul_AA[All_Raoul_AA$Pair=="A",]
samples_A<-Assay_A[!Assay_A$Treatment=="std",]
samples_A1<-samples_A[! is.na(samples_A$Plate) & samples_A$Plate=="1",]
samples_A2<-samples_A[! is.na(samples_A$Plate) & samples_A$Plate=="2",]


#Standard curves plates A
standards_A <- Assay_A[!is.na(Assay_A$Treatment) & Assay_A$Treatment == "std", ]

standards_A1<-standards_A[standards_A$Plate=="1",]
standards_A1$N_Source<-as.numeric((standards_A1$N_Source))
nm540_A1<- ggplot(standards_A1, aes(x=N_Source, y=OD540))+
  labs( y="Optical Density (540nm)", x="Concentration of L-AAs (uM)")+
  geom_point()+stat_cor(label.y=0.75, r.accuracy = 0.0001)+
  stat_regline_equation(label.y= 0.7)+
 geom_smooth(method = "lm", alpha=.15, colour='purple') +
  theme_bw()+
  ggtitle('Raoultella_A1')
nm540_A1 


standards_A2<-standards_A[standards_A$Plate=="2",]
standards_A2$N_Source<-as.numeric((standards_A2$N_Source))
nm540_A2<- ggplot(standards_A2, aes(x=N_Source, y=OD540))+
  labs( y="Optical Density (540nm)", x="Concentration of L-AAs (uM)")+
  geom_point()+stat_cor(label.y=0.75, r.accuracy = 0.0001)+
  stat_regline_equation(label.y= 0.7)+
 geom_smooth(method = "lm", alpha=.15, colour='purple') +
  theme_bw()+
  ggtitle('Raoultella_A2')
nm540_A2

##Predicted L-AA
#Predicted L-Amino Acids concentrations of samples based on the standard curve.
standards_A1$Time <- as.factor(standards_A1$Time)
model_A1<-lm(OD540~N_Source,data = standards_A1)
  model_A1$coefficients   
 summary(model_A1)
 
 standards_A2$Time <- as.factor(standards_A2$Time)
model_A2<-lm(OD540~N_Source,data = standards_A2)
  model_A2$coefficients   
 summary(model_A2)
 
#Calculating the concentration of L-AA (uM) that corresponds to measured optical densities
predictedAA_A1<- ((samples_A1$OD540-model_A1$coefficients[1])/model_A1$coefficients[2])*70
samples_A1$'Predicted_AA_Concentration'<-predictedAA_A1

predictedAA_A2<- ((samples_A2$OD540-model_A2$coefficients[1])/model_A2$coefficients[2])*70
samples_A2$'Predicted_AA_Concentration'<-predictedAA_A2

#Combining technical replicates
combined_data_A <- merge(samples_A1[, c("Time", "Pair","Treatment", "miRNA", "Predicted_AA_Concentration")], 
                       samples_A2[, c("Time", "Pair","Treatment", "miRNA", "Predicted_AA_Concentration")], 
                       by = c("Time", "Pair","Treatment", "miRNA"), 
                       suffixes = c("_A1", "_A2"))

 # This an outlier that has been replaced by its technical replicate value
tolerance <- 1e-3
combined_data_A$Predicted_AA_Concentration_A2[abs(combined_data_A$Predicted_AA_Concentration_A2 - 32051.809) < tolerance] <- 8986.012

#Calculate the mean predicted AA concentration for each qualitative variable
combined_data_A$Mean_Predicted_AA <- rowMeans(combined_data_A[, c("Predicted_AA_Concentration_A1", "Predicted_AA_Concentration_A2")], na.rm = TRUE)

```




```{r}
##ASSAY B
Assay_B<-All_Raoul_AA[All_Raoul_AA$Pair=="B",]
samples_B<-Assay_B[!Assay_B$Treatment=="std",]
samples_B1<-samples_B[! is.na(samples_B$Plate) & samples_B$Plate=="1",]
samples_B2<-samples_B[! is.na(samples_B$Plate) & samples_B$Plate=="2",]


#Standard curves plates B
standards_B <- Assay_B[!is.na(Assay_B$Treatment) & Assay_B$Treatment == "std", ]

standards_B1<-standards_B[standards_B$Plate=="1",]
standards_B1$N_Source<-as.numeric((standards_B1$N_Source))
nm540_B1<- ggplot(standards_B1, aes(x=N_Source, y=OD540))+
  labs( y="Optical Density (540nm)", x="Concentration of L-AAs (uM)")+
  geom_point()+stat_cor(label.y=0.75, r.accuracy = 0.0001)+
  stat_regline_equation(label.y= 0.7)+
 geom_smooth(method = "lm", alpha=.15, colour='purple') +
  theme_bw()+
  ggtitle('Raoultella_B1')
nm540_B1 


standards_B2<-standards_B[standards_B$Plate=="2",]
standards_B2$N_Source<-as.numeric((standards_B2$N_Source))
nm540_B2<- ggplot(standards_B2, aes(x=N_Source, y=OD540))+
  labs( y="Optical Density (540nm)", x="Concentration of L-AAs (uM)")+
  geom_point()+stat_cor(label.y=0.75, r.accuracy = 0.0001)+
  stat_regline_equation(label.y= 0.7)+
 geom_smooth(method = "lm", alpha=.15, colour='purple') +
  theme_bw()+
  ggtitle('Raoultella_B2')
nm540_B2

##Predicted L-AA
#Predicted L-Amino Acids concentrations of samples based on the standard curve.
standards_B1$Time <- as.factor(standards_B1$Time)
model_B1<-lm(OD540~N_Source,data = standards_B1)
  model_B1$coefficients   
 summary(model_B1)
 
 standards_B2$Time <- as.factor(standards_B2$Time)
model_B2<-lm(OD540~N_Source,data = standards_B2)
  model_B2$coefficients   
 summary(model_B2)
 
#Calculating the concentration of L-AA (uM) that corresponds to measured optical densities
predictedAA_B1<- ((samples_B1$OD540-model_B1$coefficients[1])/model_B1$coefficients[2])*70
samples_B1$'Predicted_AA_Concentration'<-predictedAA_B1

predictedAA_B2<- ((samples_B2$OD540-model_B2$coefficients[1])/model_B2$coefficients[2])*70
samples_B2$'Predicted_AA_Concentration'<-predictedAA_B2

#Combining technical replicates
combined_data_B <- merge(samples_B1[, c("Time", "Pair","Treatment", "miRNA", "Predicted_AA_Concentration")], 
                       samples_B2[, c("Time", "Pair","Treatment", "miRNA", "Predicted_AA_Concentration")], 
                       by = c("Time", "Pair","Treatment", "miRNA"), 
                       suffixes = c("_B1", "_B2"))


#Calculate the mean predicted AA concentration for each qualitative variable
combined_data_B$Mean_Predicted_AA <- rowMeans(combined_data_B[, c("Predicted_AA_Concentration_B1", "Predicted_AA_Concentration_B2")], na.rm = TRUE)

```

```{r}
##ASSAY C
Assay_C<-All_Raoul_AA[All_Raoul_AA$Pair=="C",]
samples_C<-Assay_C[!Assay_C$Treatment=="std",]
samples_C1<-samples_C[! is.na(samples_C$Plate) & samples_C$Plate=="1",]
samples_C2<-samples_C[! is.na(samples_C$Plate) & samples_C$Plate=="2",]


#Standard curves plates C
standards_C <- Assay_C[!is.na(Assay_C$Treatment) & Assay_C$Treatment == "std", ]

standards_C1<-standards_C[standards_C$Plate=="1",]
standards_C1$N_Source<-as.numeric((standards_C1$N_Source))
nm540_C1<- ggplot(standards_C1, aes(x=N_Source, y=OD540))+
  labs( y="Optical Density (540nm)", x="Concentration of L-AAs (uM)")+
  geom_point()+stat_cor(label.y=0.75, r.accuracy = 0.0001)+
  stat_regline_equation(label.y= 0.7)+
 geom_smooth(method = "lm", alpha=.15, colour='purple') +
  theme_bw()+
  ggtitle('Raoultella_C1')
nm540_C1 


standards_C2<-standards_C[standards_C$Plate=="2",]
standards_C2$N_Source<-as.numeric((standards_C2$N_Source))
nm540_C2<- ggplot(standards_C2, aes(x=N_Source, y=OD540))+
  labs( y="Optical Density (540nm)", x="Concentration of L-AAs (uM)")+
  geom_point()+stat_cor(label.y=0.75, r.accuracy = 0.0001)+
  stat_regline_equation(label.y= 0.7)+
 geom_smooth(method = "lm", alpha=.15, colour='purple') +
  theme_bw()+
  ggtitle('Raoultella_C2')
nm540_C2

##Predicted L-AA
#Predicted L-Amino Acids concentrations of samples based on the standard curve.
standards_C1$Time <- as.factor(standards_C1$Time)
model_C1<-lm(OD540~N_Source,data = standards_C1)
  model_C1$coefficients   
 summary(model_C1)
 
 standards_C2$Time <- as.factor(standards_C2$Time)
model_C2<-lm(OD540~N_Source,data = standards_C2)
  model_C2$coefficients   
 summary(model_C2)
 
#Calculating the concentration of L-AA (uM) that corresponds to measured optical densities
predictedAA_C1<- ((samples_C1$OD540-model_C1$coefficients[1])/model_C1$coefficients[2])*70
samples_C1$'Predicted_AA_Concentration'<-predictedAA_C1

predictedAA_C2<- ((samples_C2$OD540-model_C2$coefficients[1])/model_C2$coefficients[2])*70
samples_C2$'Predicted_AA_Concentration'<-predictedAA_C2

#Combining technical replicates
combined_data_C <- merge(samples_C1[, c("Time", "Pair","Treatment", "miRNA", "Predicted_AA_Concentration")], 
                       samples_C2[, c("Time", "Pair","Treatment", "miRNA", "Predicted_AA_Concentration")], 
                       by = c("Time", "Pair","Treatment", "miRNA"), 
                       suffixes = c("_C1", "_C2"))


#Calculate the mean predicted AA concentration for each qualitative variable
combined_data_C$Mean_Predicted_AA <- rowMeans(combined_data_C[, c("Predicted_AA_Concentration_C1", "Predicted_AA_Concentration_C2")], na.rm = TRUE)

```

```{r}
##ASSAY D
Assay_D<-All_Raoul_AA[All_Raoul_AA$Pair=="D",]
samples_D<-Assay_D[!Assay_D$Treatment=="std",]
samples_D1<-samples_D[! is.na(samples_D$Plate) & samples_D$Plate=="1",]
samples_D2<-samples_D[! is.na(samples_D$Plate) & samples_D$Plate=="2",]


#Standard curves plates D
standards_D <- Assay_D[!is.na(Assay_D$Treatment) & Assay_D$Treatment == "std", ]

standards_D1<-standards_D[standards_D$Plate=="1",]
standards_D1$N_Source<-as.numeric((standards_D1$N_Source))
nm540_D1<- ggplot(standards_D1, aes(x=N_Source, y=OD540))+
  labs( y="Optical Density (540nm)", x="Concentration of L-AAs (uM)")+
  geom_point()+stat_cor(label.y=0.75, r.accuracy = 0.0001)+
  stat_regline_equation(label.y= 0.7)+
 geom_smooth(method = "lm", alpha=.15, colour='purple') +
  theme_bw()+
  ggtitle('Raoultella_D1')
nm540_D1 


standards_D2<-standards_D[standards_D$Plate=="2",]
standards_D2$N_Source<-as.numeric((standards_D2$N_Source))
nm540_D2<- ggplot(standards_D2, aes(x=N_Source, y=OD540))+
  labs( y="Optical Density (540nm)", x="Concentration of L-AAs (uM)")+
  geom_point()+stat_cor(label.y=0.75, r.accuracy = 0.0001)+
  stat_regline_equation(label.y= 0.7)+
 geom_smooth(method = "lm", alpha=.15, colour='purple') +
  theme_bw()+
  ggtitle('Raoultella_D2')
nm540_D2

##Predicted L-AA
#Predicted L-Amino Acids concentrations of samples based on the standard curve.
standards_D1$Time <- as.factor(standards_D1$Time)
model_D1<-lm(OD540~N_Source,data = standards_D1)
  model_D1$coefficients   
 summary(model_D1)
 
 standards_D2$Time <- as.factor(standards_D2$Time)
model_D2<-lm(OD540~N_Source,data = standards_D2)
  model_D2$coefficients   
 summary(model_D2)
 
#Calculating the concentration of L-AA (uM) that corresponds to measured optical densities
predictedAA_D1<- ((samples_D1$OD540-model_D1$coefficients[1])/model_D1$coefficients[2])*70
samples_D1$'Predicted_AA_Doncentration'<-predictedAA_D1

predictedAA_D2<- ((samples_D2$OD540-model_D2$coefficients[1])/model_D2$coefficients[2])*70
samples_D2$'Predicted_AA_Doncentration'<-predictedAA_D2

#Combining technical replicates
combined_data_D <- merge(samples_D1[, c("Time", "Pair","Treatment", "miRNA", "Predicted_AA_Doncentration")], 
                       samples_D2[, c("Time", "Pair","Treatment", "miRNA", "Predicted_AA_Doncentration")], 
                       by = c("Time", "Pair","Treatment", "miRNA"), 
                       suffixes = c("_D1", "_D2"))


#Calculate the mean predicted AA concentration for each qualitative variable
combined_data_D$Mean_Predicted_AA <- rowMeans(combined_data_D[, c("Predicted_AA_Doncentration_D1", "Predicted_AA_Doncentration_D2")], na.rm = TRUE)
```

```{r}
##ASSAY E
Assay_E<-All_Raoul_AA[All_Raoul_AA$Pair=="E",]
samples_E<-Assay_E[!Assay_E$Treatment=="std",]
samples_E1<-samples_E[! is.na(samples_E$Plate) & samples_E$Plate=="1",]
samples_E2<-samples_E[! is.na(samples_E$Plate) & samples_E$Plate=="2",]


#Standard curves plates E
standards_E <- Assay_E[!is.na(Assay_E$Treatment) & Assay_E$Treatment == "std", ]

standards_E1<-standards_E[standards_E$Plate=="1",]
standards_E1$N_Source<-as.numeric((standards_E1$N_Source))
nm540_E1<- ggplot(standards_E1, aes(x=N_Source, y=OD540))+
  labs( y="Optical Density (540nm)", x="Concentration of L-AAs (uM)")+
  geom_point()+stat_cor(label.y=0.75, r.accuracy = 0.0001)+
  stat_regline_equation(label.y= 0.7)+
 geom_smooth(method = "lm", alpha=.15, colour='purple') +
  theme_bw()+
  ggtitle('Raoultella_E1')
nm540_E1 


standards_E2<-standards_E[standards_E$Plate=="2",]
standards_E2$N_Source<-as.numeric((standards_E2$N_Source))
nm540_E2<- ggplot(standards_E2, aes(x=N_Source, y=OD540))+
  labs( y="Optical Density (540nm)", x="Concentration of L-AAs (uM)")+
  geom_point()+stat_cor(label.y=0.75, r.accuracy = 0.0001)+
  stat_regline_equation(label.y= 0.7)+
 geom_smooth(method = "lm", alpha=.15, colour='purple') +
  theme_bw()+
  ggtitle('Raoultella_E2')
nm540_E2

##Predicted L-AA
#Predicted L-Amino Acids concentrations of samples based on the standard curve.
standards_E1$Time <- as.factor(standards_E1$Time)
model_E1<-lm(OD540~N_Source,data = standards_E1)
  model_E1$coefficients   
 summary(model_E1)
 
 standards_E2$Time <- as.factor(standards_E2$Time)
model_E2<-lm(OD540~N_Source,data = standards_E2)
  model_E2$coefficients   
 summary(model_E2)
 
#Calculating the concentration of L-AA (uM) that corresponds to measured optical densities
predictedAA_E1<- ((samples_E1$OD540-model_E1$coefficients[1])/model_E1$coefficients[2])*70
samples_E1$'Predicted_AA_Eoncentration'<-predictedAA_E1

predictedAA_E2<- ((samples_E2$OD540-model_E2$coefficients[1])/model_E2$coefficients[2])*70
samples_E2$'Predicted_AA_Eoncentration'<-predictedAA_E2

#Combining technical replicates
combined_data_E <- merge(samples_E1[, c("Time", "Pair","Treatment", "miRNA", "Predicted_AA_Eoncentration")], 
                       samples_E2[, c("Time", "Pair","Treatment", "miRNA", "Predicted_AA_Eoncentration")], 
                       by = c("Time", "Pair","Treatment", "miRNA"), 
                       suffixes = c("_E1", "_E2"))


#Calculate the mean predicted AA concentration for each qualitative variable
combined_data_E$Mean_Predicted_AA <- rowMeans(combined_data_E[, c("Predicted_AA_Eoncentration_E1", "Predicted_AA_Eoncentration_E2")], na.rm = TRUE)
```

##Merging all replicas
```{r}
AARaoul<- rbind(combined_data_A[, c("Treatment", "Time", "miRNA", "Pair", "Mean_Predicted_AA")], 
                   combined_data_B[, c("Treatment", "Time", "miRNA", "Pair", "Mean_Predicted_AA")],
                  combined_data_C[, c("Treatment", "Time", "miRNA", "Pair", "Mean_Predicted_AA")],
                  combined_data_D[, c("Treatment", "Time", "miRNA", "Pair", "Mean_Predicted_AA")],
                 combined_data_E[, c("Treatment", "Time", "miRNA", "Pair", "Mean_Predicted_AA")])
```

##Statistical Tests
```{r}
AARaoul_noctl<-AARaoul

AARaoul_noctl$Treatment<-recode_factor(AARaoul_noctl$Treatment, Scramble= "Scramble miRNAs",Plant="Plant miRNAs" )

AARaoul_noctl$Time<-as.factor(AARaoul_noctl$Time)
loop<-levels(AARaoul_noctl$Time)

AARaoul_158a3p<-AARaoul_noctl[AARaoul_noctl$miRNA=='ath-miR158a3p',]
AARaoul_158b<-AARaoul_noctl[AARaoul_noctl$miRNA=='ath-miR158b',]
AARaoul_159<-AARaoul_noctl[AARaoul_noctl$miRNA=='ath-miR159',]
AARaoul_827<-AARaoul_noctl[AARaoul_noctl$miRNA=='ath-miR827',]
AARaoul_5642b<-AARaoul_noctl[AARaoul_noctl$miRNA=='ath-miR5642b',]
AARaoul_mixmiR5<-AARaoul_noctl[AARaoul_noctl$miRNA=='Mix5',]

#mir158a3p
for(i in 1:4) 
{
Timepoint<-AARaoul_158a3p[AARaoul_158a3p$Time==loop[i],]
plant<- Timepoint[Timepoint$Treatment=="Plant miRNAs",]
planto<-plant[order(plant$Pair),]
mirplant<-planto$Mean_Predicted_AA
scram<- Timepoint[Timepoint$Treatment=="Scramble miRNAs",]
scramo<-scram[order(scram$Pair),]
mirscram<-scramo$Mean_Predicted_AA
differences<- as.data.frame(mirscram - mirplant)
outliers<-identify_outliers(differences) 
test<-shapiro_test(differences$`mirscram - mirplant`)
{
  if(nrow(outliers)>=1|test$p.value < 0.05)
    cat("Time:",loop[i]," ","p.value :", test$p.value, " ","Statistic:", test$statistic,"Outliers:",outliers$is.outlier,"\n", file=here("Output","t.test_results","Assump_AA_Raoul_158a3p.txt"), append=T) 
  } 
 i=i+1}

i=0 
for(i in 1:4) 
{
Timepoint<-AARaoul_158a3p[AARaoul_158a3p$Time==loop[i],]
plant<- Timepoint[Timepoint$Treatment=="Plant miRNAs",]
planto<-plant[order(plant$Pair),]
mirplant<-planto$Mean_Predicted_AA
scram<- Timepoint[Timepoint$Treatment=="Scramble miRNAs",]
scramo<-scram[order(scram$Pair),]
mirscram<-scramo$Mean_Predicted_AA
test<-t.test(mirplant, mirscram, paired = TRUE, alternative = "less")
{
  if(test$p.value < 0.05)
    cat("Time:",loop[i]," ","p.value :", test$p.value, " ","statistic:", test$statistic, "\n", file=here("Output","t.test_results","Raoul_T_158a3p_less.txt"), append=T) 
  }
 i=i+1} # Time 24, Time 6 = 0.06916512 


#mir158b
for(i in 1:4) 
{
Timepoint<-AARaoul_158b[AARaoul_158b$Time==loop[i],]
plant<- Timepoint[Timepoint$Treatment=="Plant miRNAs",]
planto<-plant[order(plant$Pair),]
mirplant<-planto$Mean_Predicted_AA
scram<- Timepoint[Timepoint$Treatment=="Scramble miRNAs",]
scramo<-scram[order(scram$Pair),]
mirscram<-scramo$Mean_Predicted_AA
differences<- as.data.frame(mirscram - mirplant)
outliers<-identify_outliers(differences) 
test<-shapiro_test(differences$`mirscram - mirplant`)
{
  if(nrow(outliers)>=1|test$p.value < 0.05)
    cat("Time:",loop[i]," ","p.value :", test$p.value, " ","Statistic:", test$statistic,"Outliers:",outliers$is.outlier,"\n", file=here("Output","t.test_results","Assump_AA_Raoul_158b.txt"), append=T) 
  } 
 i=i+1}

for(i in 1:4) 
{
Timepoint<-AARaoul_158b[AARaoul_158b$Time==loop[i],]
plant<- Timepoint[Timepoint$Treatment=="Plant miRNAs",]
planto<-plant[order(plant$Pair),]
mirplant<-planto$Mean_Predicted_AA
scram<- Timepoint[Timepoint$Treatment=="Scramble miRNAs",]
scramo<-scram[order(scram$Pair),]
mirscram<-scramo$Mean_Predicted_AA
test<-t.test(mirplant, mirscram, paired = TRUE, alternative = "greater")
{
  if(test$p.value < 0.05)
    cat("Time:",loop[i]," ","p.value :", test$p.value, " ","statistic:", test$statistic, "\n", file=here("Output","t.test_results","Raoul_T_158b_greater.txt"), append=T) 
  } 
 i=i+1} # Time 0, Time 3 = 0.08338839  


#mir159
for(i in 1:4) 
{
Timepoint<-AARaoul_159[AARaoul_159$Time==loop[i],]
plant<- Timepoint[Timepoint$Treatment=="Plant miRNAs",]
planto<-plant[order(plant$Pair),]
mirplant<-planto$Mean_Predicted_AA
scram<- Timepoint[Timepoint$Treatment=="Scramble miRNAs",]
scramo<-scram[order(scram$Pair),]
mirscram<-scramo$Mean_Predicted_AA
differences<- as.data.frame(mirscram - mirplant)
outliers<-identify_outliers(differences) 
test<-shapiro_test(differences$`mirscram - mirplant`)
{
  if(nrow(outliers)>=1|test$p.value < 0.05)
    cat("Time:",loop[i]," ","p.value :", test$p.value, " ","Statistic:", test$statistic,"Outliers:",outliers$is.outlier,"\n", file=here("Output","t.test_results","Assump_AA_Raoul_159.txt"), append=T) 
  } 
 i=i+1}

for(i in 1:4) 
{
Timepoint<-AARaoul_159[AARaoul_159$Time==loop[i],]
plant<- Timepoint[Timepoint$Treatment=="Plant miRNAs",]
planto<-plant[order(plant$Pair),]
mirplant<-planto$Mean_Predicted_AA
scram<- Timepoint[Timepoint$Treatment=="Scramble miRNAs",]
scramo<-scram[order(scram$Pair),]
mirscram<-scramo$Mean_Predicted_AA
test<-t.test(mirplant, mirscram, paired = TRUE, alternative = "two.sided")
{
  if(test$p.value < 0.05)
    cat("Time:",loop[i]," ","p.value :", test$p.value, " ","statistic:", test$statistic, "\n", file=here("Output","t.test_results","Raoul_T_159r.txt"), append=T) 
  } 
 i=i+1} #ns

#mir827
for(i in 1:4) 
{
Timepoint<-AARaoul_827[AARaoul_827$Time==loop[i],]
plant<- Timepoint[Timepoint$Treatment=="Plant miRNAs",]
planto<-plant[order(plant$Pair),]
mirplant<-planto$Mean_Predicted_AA
scram<- Timepoint[Timepoint$Treatment=="Scramble miRNAs",]
scramo<-scram[order(scram$Pair),]
mirscram<-scramo$Mean_Predicted_AA
differences<- as.data.frame(mirscram - mirplant)
outliers<-identify_outliers(differences) 
test<-shapiro_test(differences$`mirscram - mirplant`)
{
  if(nrow(outliers)>=1|test$p.value < 0.05)
    cat("Time:",loop[i]," ","p.value :", test$p.value, " ","Statistic:", test$statistic,"Outliers:",outliers$is.outlier,"\n", file=here("Output","t.test_results","Assump_AA_Raoul_827.txt"), append=T) 
  } 
 i=i+1}

for(i in 1:4) 
{
Timepoint<-AARaoul_827[AARaoul_827$Time==loop[i],]
plant<- Timepoint[Timepoint$Treatment=="Plant miRNAs",]
planto<-plant[order(plant$Pair),]
mirplant<-planto$Mean_Predicted_AA
scram<- Timepoint[Timepoint$Treatment=="Scramble miRNAs",]
scramo<-scram[order(scram$Pair),]
mirscram<-scramo$Mean_Predicted_AA
test<-t.test(mirplant, mirscram, paired = TRUE, alternative = "two.sided")
{
  if(test$p.value < 0.05)
    cat("Time:",loop[i]," ","p.value :", test$p.value, " ","statistic:", test$statistic, "\n", file=here("Output","t.test_results","Raoul_T_827.txt"), append=T) 
  } 
 i=i+1} # ns



#mir5642b
for(i in 1:4) 
{
Timepoint<-AARaoul_5642b[AARaoul_5642b$Time==loop[i],]
plant<- Timepoint[Timepoint$Treatment=="Plant miRNAs",]
planto<-plant[order(plant$Pair),]
mirplant<-planto$Mean_Predicted_AA
scram<- Timepoint[Timepoint$Treatment=="Scramble miRNAs",]
scramo<-scram[order(scram$Pair),]
mirscram<-scramo$Mean_Predicted_AA
differences<- as.data.frame(mirscram - mirplant)
outliers<-identify_outliers(differences) 
test<-shapiro_test(differences$`mirscram - mirplant`)
{
  if(nrow(outliers)>=1|test$p.value < 0.05)
    cat("Time:",loop[i]," ","p.value :", test$p.value, " ","Statistic:", test$statistic,"Outliers:",outliers$is.outlier,"\n", file=here("Output","t.test_results","Assump_AA_Raoul_5642b.txt"), append=T) 
  } 
 i=i+1}

for(i in 1:4) 
{
Timepoint<-AARaoul_5642b[AARaoul_5642b$Time==loop[i],]
plant<- Timepoint[Timepoint$Treatment=="Plant miRNAs",]
planto<-plant[order(plant$Pair),]
mirplant<-planto$Mean_Predicted_AA
scram<- Timepoint[Timepoint$Treatment=="Scramble miRNAs",]
scramo<-scram[order(scram$Pair),]
mirscram<-scramo$Mean_Predicted_AA
test<-t.test(mirplant, mirscram, paired = TRUE, alternative = "greater")
{
  if(test$p.value < 0.05)
    cat("Time:",loop[i]," ","p.value :", test$p.value, " ","statistic:", test$statistic, "\n", file=here("Output","t.test_results","Raoul_T_5642b_greater.txt"), append=T) 
  } 
 i=i+1} #Time 3

i=0 
for(i in 1:4) 
{
Timepoint<-AARaoul_5642b[AARaoul_5642b$Time==loop[i],]
plant<- Timepoint[Timepoint$Treatment=="Plant miRNAs",]
planto<-plant[order(plant$Pair),]
mirplant<-planto$Mean_Predicted_AA
scram<- Timepoint[Timepoint$Treatment=="Scramble miRNAs",]
scramo<-scram[order(scram$Pair),]
mirscram<-scramo$Mean_Predicted_AA
test<-t.test(mirplant, mirscram, paired = TRUE, alternative = "less")
{
  if(test$p.value < 0.05)
    cat("Time:",loop[i]," ","p.value :", test$p.value, " ","statistic:", test$statistic, "\n", file=here("Output","t.test_results","Raoul_T_5642b_less.txt"), append=T) 
  }
 i=i+1} #Time 0 



#mixmir5
for(i in 1:4) 
{
Timepoint<-AARaoul_mixmiR5[AARaoul_mixmiR5$Time==loop[i],]
plant<- Timepoint[Timepoint$Treatment=="Plant miRNAs",]
planto<-plant[order(plant$Pair),]
mirplant<-planto$Mean_Predicted_AA
scram<- Timepoint[Timepoint$Treatment=="Scramble miRNAs",]
scramo<-scram[order(scram$Pair),]
mirscram<-scramo$Mean_Predicted_AA
differences<- as.data.frame(mirscram - mirplant)
outliers<-identify_outliers(differences) 
test<-shapiro_test(differences$`mirscram - mirplant`)
{
  if(nrow(outliers)>=1|test$p.value < 0.05)
    cat("Time:",loop[i]," ","p.value :", test$p.value, " ","Statistic:", test$statistic,"Outliers:",outliers$is.outlier,"\n", file=here("Output","t.test_results","Assump_AA_Raoul_mixmiR5.txt"), append=T) 
  } 
 i=i+1}

for(i in 1:4) 
{
Timepoint<-AARaoul_mixmiR5[AARaoul_mixmiR5$Time==loop[i],]
plant<- Timepoint[Timepoint$Treatment=="Plant miRNAs",]
planto<-plant[order(plant$Pair),]
mirplant<-planto$Mean_Predicted_AA
scram<- Timepoint[Timepoint$Treatment=="Scramble miRNAs",]
scramo<-scram[order(scram$Pair),]
mirscram<-scramo$Mean_Predicted_AA
test<-t.test(mirplant, mirscram, paired = TRUE, alternative = "greater")
{
  if(test$p.value < 0.05)
    cat("Time:",loop[i]," ","p.value :", test$p.value, " ","statistic:", test$statistic, "\n", file=here("Output","t.test_results","Raoul_T_mixmiR5_greater.txt"), append=T) 
  } 
 i=i+1} #Time 24


```

##AA Consumption AUC
```{r}
# Calculate AUC using the trapz function
# Define a custom AUC calculation function
calculate_auc <- function(data, x_col, y_col) {
  x <- data[[x_col]]  # Date column
  y <- data[[y_col]]  # Data column
  trapz(x, y)  # Calculate AUC using trapezoidal rule
}

#ath-miR158a3p
AARaoul_158a3p$Time <- as.numeric(AARaoul_158a3p$Time) 
# Select columns with data for AUC calculation
data_cols <- names(AARaoul_158a3p)[5]  # Adjust to match your data column range
# Group by isolate and block
AUC_AARaoul_158a3p<- AARaoul_158a3p %>%
  group_by(Pair, Treatment) %>%
  summarise(
    across(all_of(data_cols), ~ calculate_auc(cur_data(), "Time", cur_column()), .names = "AUC_{.col}")
  )
plant<- AUC_AARaoul_158a3p[AUC_AARaoul_158a3p$Treatment=="Plant miRNAs",]
planto<-plant[order(plant$Pair),]
mirplant<-planto$AUC_Mean_Predicted_AA
scram<- AUC_AARaoul_158a3p[AUC_AARaoul_158a3p$Treatment=="Scramble miRNAs",]
scramo<-scram[order(scram$Pair),]
mirscram<-scramo$AUC_Mean_Predicted_AA
differences<- as.data.frame(mirscram - mirplant)
identify_outliers(differences) #none
shapiro_test(differences$`mirscram - mirplant`) #p-value= 0.7144164	
t.test(AUC_Mean_Predicted_AA ~ Treatment, paired=TRUE, data= AUC_AARaoul_158a3p, alternative='greater') #p-value = 0.01693

boxAUC_AA_158a3p<-ggplot(AUC_AARaoul_158a3p, aes(y=AUC_Mean_Predicted_AA, x=Treatment, fill=Treatment))+
   geom_boxplot(outlier.shape = NA, alpha=0.4, aes(fill=Treatment, color=Treatment )) +
  geom_point(aes(fill=Treatment, color=Treatment),pch = 21, position = position_jitterdodge(0.2))+
  geom_line(aes(group = Pair), color = "grey50", linetype = "solid", alpha = 0.5) +
  theme_classic() + theme(legend.position="none", axis.ticks.x=element_blank(), axis.text.x = element_text(size = 12, angle = 45, hjust = 1),axis.text.y = element_text(size = 10)) +labs(x="", y="")+
scale_fill_manual(values = c("#003049","#2a7f62"))+
scale_colour_manual(values = c("#003049","#2a7f62"))+
  ggtitle(expression(italic("Raoultella") ~ "ath-miR158a3p"))+
  annotate('text', x = 1.5, y = 32000, label='*', size=8)+
  annotate('text', x = 1.5, y = 35000, label='Amino acids', size=4.5)
boxAUC_AA_158a3p_2<-ggpar(boxAUC_AA_158a3p,ylim = c(15000, 35000))
boxAUC_AA_158a3p_2

#ath-miR158b
AARaoul_158b$Time <- as.numeric(AARaoul_158b$Time) 
# Select columns with data for AUC calculation
data_cols <- names(AARaoul_158b)[5]  # Adjust to match your data column range
# Group by isolate and block
AUC_AARaoul_158b<- AARaoul_158b %>%
  group_by(Pair, Treatment) %>%
  summarise(
    across(all_of(data_cols), ~ calculate_auc(cur_data(), "Time", cur_column()), .names = "AUC_{.col}")
  )
plant<- AUC_AARaoul_158b[AUC_AARaoul_158b$Treatment=="Plant miRNAs",]
planto<-plant[order(plant$Pair),]
mirplant<-planto$AUC_Mean_Predicted_AA
scram<- AUC_AARaoul_158b[AUC_AARaoul_158b$Treatment=="Scramble miRNAs",]
scramo<-scram[order(scram$Pair),]
mirscram<-scramo$AUC_Mean_Predicted_AA
differences<- as.data.frame(mirscram - mirplant)
identify_outliers(differences) #none
shapiro_test(differences$`mirscram - mirplant`) #p-value= 0.01586739	
wilcox.test(AUC_Mean_Predicted_AA ~ Treatment, paired=TRUE, data= AUC_AARaoul_158b, alternative='less')
#p-value = 0.03125

boxAUC_AA_158b<-ggplot(AUC_AARaoul_158b, aes(y=AUC_Mean_Predicted_AA, x=Treatment, fill=Treatment))+
   geom_boxplot(outlier.shape = NA, alpha=0.4, aes(fill=Treatment, color=Treatment )) +
  geom_point(aes(fill=Treatment, color=Treatment),pch = 21, position = position_jitterdodge(0.2))+
  geom_line(aes(group = Pair), color = "grey50", linetype = "solid", alpha = 0.5) +
  theme_classic() + theme(legend.position="none", axis.ticks.x=element_blank(), axis.text.x = element_text(size = 12, angle = 45, hjust = 1),axis.text.y = element_text(size = 10))+labs(x="", y="")+
scale_fill_manual(values = c("#003049","#2a7f62"))+
scale_colour_manual(values = c("#003049","#2a7f62"))+
  ggtitle(expression(italic("Raoultella") ~ "ath-miR158b"))+
  annotate('text', x = 1.5, y = 32000, label='*', size=8)+
  annotate('text', x = 1.5, y = 35000, label='Amino acids', size=4.5)
boxAUC_AA_158b
boxAUC_AA_158b_2<-ggpar(boxAUC_AA_158b,ylim = c(15000, 35000))
boxAUC_AA_158b_2

#ath-miR159
AARaoul_159$Time <- as.numeric(AARaoul_159$Time) 
# Select columns with data for AUC calculation
data_cols <- names(AARaoul_159)[5]  # Adjust to match your data column range
# Group by isolate and block
AUC_AARaoul_159<- AARaoul_159 %>%
  group_by(Pair, Treatment) %>%
  summarise(
    across(all_of(data_cols), ~ calculate_auc(cur_data(), "Time", cur_column()), .names = "AUC_{.col}")
  )

#ath-miR827
AARaoul_827$Time <- as.numeric(AARaoul_827$Time) 
# Select columns with data for AUC calculation
data_cols <- names(AARaoul_827)[5]  # Adjust to match your data column range
# Group by isolate and block
AUC_AARaoul_827<- AARaoul_827 %>%
  group_by(Pair, Treatment) %>%
  summarise(
    across(all_of(data_cols), ~ calculate_auc(cur_data(), "Time", cur_column()), .names = "AUC_{.col}")
  )
#ath-miR5642b
AARaoul_5642b$Time <- as.numeric(AARaoul_5642b$Time) 
# Select columns with data for AUC calculation
data_cols <- names(AARaoul_5642b)[5]  # Adjust to match your data column range
# Group by isolate and block
AUC_AARaoul_5642b<- AARaoul_5642b %>%
  group_by(Pair, Treatment) %>%
  summarise(
    across(all_of(data_cols), ~ calculate_auc(cur_data(), "Time", cur_column()), .names = "AUC_{.col}")
  )
t.test(AUC_Mean_Predicted_AA ~ Treatment, paired=TRUE, data= AUC_AARaoul_5642b, alternative='greater') #p-value = 0.02862

boxAUC_AA_5642b<-ggplot(AUC_AARaoul_5642b, aes(y=AUC_Mean_Predicted_AA, x=Treatment,fill=Treatment))+
   geom_boxplot(outlier.shape = NA, alpha=0.4, aes(fill=Treatment, color=Treatment )) +
  geom_point(aes(fill=Treatment, color=Treatment),pch = 21, position = position_jitterdodge(0.2))+
  geom_line(aes(group = Pair), color = "grey50", linetype = "solid", alpha = 0.5) +
  theme_classic()+
  theme(legend.position="none", axis.ticks.x=element_blank(), axis.text.x = element_text(size = 12, angle = 45, hjust = 1),axis.text.y = element_text(size = 10))+
  labs(x="", y="")+
scale_fill_manual(values = c("#003049","#2a7f62"))+
scale_colour_manual(values = c("#003049","#2a7f62"))+
 ggtitle(expression(italic("Raoultella") ~ "ath-miR5642b"))+
  annotate('text', x = 1.5, y = 32000, label='*', size=8)+
  annotate('text', x = 1.5, y = 35000, label='Amino acids', size=4.5)
boxAUC_AA_5642b
boxAUC_AA_5642b_2<-ggpar(boxAUC_AA_5642b,ylim = c(15000, 35000))
boxAUC_AA_5642b_2


#ath-miRMix5
AARaoul_mixmiR5$Time <- as.numeric(AARaoul_mixmiR5$Time) 
# Select columns with data for AUC calculation
data_cols <- names(AARaoul_mixmiR5)[5]  # Adjust to match your data column range
# Group by isolate and block
AUC_AARaoul_Mix5<- AARaoul_mixmiR5 %>%
  group_by(Pair, Treatment) %>%
  summarise(
    across(all_of(data_cols), ~ calculate_auc(cur_data(), "Time", cur_column()), .names = "AUC_{.col}")
  )
plant<- AUC_AARaoul_Mix5[AUC_AARaoul_Mix5$Treatment=="Plant miRNAs",]
planto<-plant[order(plant$Pair),]
mirplant<-planto$AUC_Mean_Predicted_AA
scram<- AUC_AARaoul_Mix5[AUC_AARaoul_Mix5$Treatment=="Scramble miRNAs",]
scramo<-scram[order(scram$Pair),]
mirscram<-scramo$AUC_Mean_Predicted_AA
differences<- as.data.frame(mirscram - mirplant)
identify_outliers(differences) #none
shapiro_test(differences$`mirscram - mirplant`) #p-value= 0.4177331	
t.test(AUC_Mean_Predicted_AA ~ Treatment, paired=TRUE, data= AUC_AARaoul_Mix5, alternative='less')
#p-value = 0.07461

Raoul_combiAA<-ggarrange(boxAUC_AA_158a3p_2,boxAUC_AA_158b_2,boxAUC_AA_5642b_2, nrow=1, ncol=3)
saveRDS(Raoul_combiAA, file = here("Output","Figures","Raoul_AUC_AA.rds"))

```


#Growth Raoultella
##Importation
```{r}
GrowthData<- read.table(file.path("Raw_Data", "Raoultella","Raoul_Growth.txt"), header = TRUE, sep="\t") #280 obs. 6 var.
GrowthData$Time<-as.factor(GrowthData$Time)
GrowthData$Pair<-as.factor(GrowthData$Pair)
```

##Subsetting by miRNA
```{r}
Growth158a3p<-GrowthData[GrowthData$miRNA=="ath-miR158a3p",]
Growth158b<-GrowthData[GrowthData$miRNA=="ath-miR158b",]
Growth159<-GrowthData[GrowthData$miRNA=="ath-miR159",]
Growth827<-GrowthData[GrowthData$miRNA=="ath-miR827",]
Growth5642b<-GrowthData[GrowthData$miRNA=="ath-miR5642b",]
GrowthMix5<-GrowthData[GrowthData$miRNA=="Mix5",]
```

##Statistical Tests
```{r}
loop<-levels(GrowthData$Time)
#ath-miR158a3p
i=0 
for(i in 1:4) 
{
Timepoint<-Growth158a3p[Growth158a3p$Time==loop[i],]
plant<- Timepoint[Timepoint$Treatment=="Plant",]
planto<-plant[order(plant$Pair),]
mirplant<-planto$OD600
scram<- Timepoint[Timepoint$Treatment=="Scramble",]
scramo<-scram[order(scram$Pair),]
mirscram<-scramo$OD600
differences<- as.data.frame(mirscram - mirplant)
outliers<-identify_outliers(differences) 
test<-shapiro_test(differences$`mirscram - mirplant`)
{
  if(nrow(outliers)>=1|test$p.value < 0.05)
    cat("Time:",loop[i]," ","p.value :", test$p.value, " ","Statistic:", test$statistic,"Outliers:",outliers$is.outlier,"\n", file=here("Output","t.test_results","Growth_curves","Raoul_Assump_158a3p.txt"), append=T) 
  } 
 i=i+1}

i=0 
for(i in 1:4) 
{
Timepoint<-Growth158a3p[Growth158a3p$Time==loop[i],]
plant<- Timepoint[Timepoint$Treatment=="Plant",]
planto<-plant[order(plant$Pair),]
mirplant<-planto$OD600
scram<- Timepoint[Timepoint$Treatment=="Scramble",]
scramo<-scram[order(scram$Pair),]
mirscram<-scramo$OD600
test<-t.test(mirplant, mirscram, paired = TRUE, alternative = "two.sided")
{
  if(test$p.value < 0.05)
    cat("Time:",loop[i]," ","p.value :", test$p.value, " ","statistic:", test$statistic, "\n", file=here("Output","t.test_results","Growth_curves","Raoul_158a3p_t.test.txt"), append=T) 
  } 
 i=i+1} #nothing significant

#ath-miR158b
i=0 
for(i in 1:4) 
{
Timepoint<-Growth158b[Growth158b$Time==loop[i],]
plant<- Timepoint[Timepoint$Treatment=="Plant",]
planto<-plant[order(plant$Pair),]
mirplant<-planto$OD600
scram<- Timepoint[Timepoint$Treatment=="Scramble",]
scramo<-scram[order(scram$Pair),]
mirscram<-scramo$OD600
differences<- as.data.frame(mirscram - mirplant)
outliers<-identify_outliers(differences) 
test<-shapiro_test(differences$`mirscram - mirplant`)
{
  if(nrow(outliers)>=1|test$p.value < 0.05)
    cat("Time:",loop[i]," ","p.value :", test$p.value, " ","Statistic:", test$statistic,"Outliers:",outliers$is.outlier,"\n", file=here("Output","t.test_results","Growth_curves","Raoul_Assump_158b.txt"), append=T) 
  } 
 i=i+1}

i=0 
for(i in 1:4) 
{
Timepoint<-Growth158b[Growth158b$Time==loop[i],]
plant<- Timepoint[Timepoint$Treatment=="Plant",]
planto<-plant[order(plant$Pair),]
mirplant<-planto$OD600
scram<- Timepoint[Timepoint$Treatment=="Scramble",]
scramo<-scram[order(scram$Pair),]
mirscram<-scramo$OD600
test<-t.test(mirplant, mirscram, paired = TRUE, alternative = "two.sided")
{
  if(test$p.value < 0.05)
    cat("Time:",loop[i]," ","p.value :", test$p.value, " ","statistic:", test$statistic, "\n", file=here("Output","t.test_results","Growth_curves","Raoul_158b_t.test.txt"), append=T) 
  } 
 i=i+1} #nothing significant

#ath-miR159
i=0 
for(i in 1:4) 
{
Timepoint<-Growth159[Growth159$Time==loop[i],]
plant<- Timepoint[Timepoint$Treatment=="Plant",]
planto<-plant[order(plant$Pair),]
mirplant<-planto$OD600
scram<- Timepoint[Timepoint$Treatment=="Scramble",]
scramo<-scram[order(scram$Pair),]
mirscram<-scramo$OD600
differences<- as.data.frame(mirscram - mirplant)
outliers<-identify_outliers(differences) 
test<-shapiro_test(differences$`mirscram - mirplant`)
{
  if(nrow(outliers)>=1|test$p.value < 0.05)
    cat("Time:",loop[i]," ","p.value :", test$p.value, " ","Statistic:", test$statistic,"Outliers:",outliers$is.outlier,"\n", file=here("Output","t.test_results","Growth_curves","Raoul_Assump_159.txt"), append=T) 
  } 
 i=i+1}

i=0 
for(i in 1:4) 
{
Timepoint<-Growth159[Growth159$Time==loop[i],]
plant<- Timepoint[Timepoint$Treatment=="Plant",]
planto<-plant[order(plant$Pair),]
mirplant<-planto$OD600
scram<- Timepoint[Timepoint$Treatment=="Scramble",]
scramo<-scram[order(scram$Pair),]
mirscram<-scramo$OD600
test<-t.test(mirplant, mirscram, paired = TRUE, alternative = "two.sided")
{
  if(test$p.value < 0.05)
    cat("Time:",loop[i]," ","p.value :", test$p.value, " ","statistic:", test$statistic, "\n", file=here("Output","t.test_results","Growth_curves","Raoul_159_t.test.txt"), append=T) 
  } 
 i=i+1} #nothing significant

#ath-miR827
i=0 
for(i in 1:4) 
{
Timepoint<-Growth827[Growth827$Time==loop[i],]
plant<- Timepoint[Timepoint$Treatment=="Plant",]
planto<-plant[order(plant$Pair),]
mirplant<-planto$OD600
scram<- Timepoint[Timepoint$Treatment=="Scramble",]
scramo<-scram[order(scram$Pair),]
mirscram<-scramo$OD600
differences<- as.data.frame(mirscram - mirplant)
outliers<-identify_outliers(differences) 
test<-shapiro_test(differences$`mirscram - mirplant`)
{
  if(nrow(outliers)>=1|test$p.value < 0.05)
    cat("Time:",loop[i]," ","p.value :", test$p.value, " ","Statistic:", test$statistic,"Outliers:",outliers$is.outlier,"\n", file=here("Output","t.test_results","Growth_curves","Raoul_Assump_827.txt"), append=T) 
  } 
 i=i+1}

i=0 
for(i in 1:4) 
{
Timepoint<-Growth827[Growth827$Time==loop[i],]
plant<- Timepoint[Timepoint$Treatment=="Plant",]
planto<-plant[order(plant$Pair),]
mirplant<-planto$OD600
scram<- Timepoint[Timepoint$Treatment=="Scramble",]
scramo<-scram[order(scram$Pair),]
mirscram<-scramo$OD600
test<-t.test(mirplant, mirscram, paired = TRUE, alternative = "two.sided")
{
  if(test$p.value < 0.05)
    cat("Time:",loop[i]," ","p.value :", test$p.value, " ","statistic:", test$statistic, "\n", file=here("Output","t.test_results","Growth_curves","Raoul_827_t.test.txt"), append=T) 
  } 
 i=i+1} #nothing significant

#ath-miR5642b
i=0 
for(i in 1:4) 
{
Timepoint<-Growth5642b[Growth5642b$Time==loop[i],]
plant<- Timepoint[Timepoint$Treatment=="Plant",]
planto<-plant[order(plant$Pair),]
mirplant<-planto$OD600
scram<- Timepoint[Timepoint$Treatment=="Scramble",]
scramo<-scram[order(scram$Pair),]
mirscram<-scramo$OD600
differences<- as.data.frame(mirscram - mirplant)
outliers<-identify_outliers(differences) 
test<-shapiro_test(differences$`mirscram - mirplant`)
{
  if(nrow(outliers)>=1|test$p.value < 0.05)
    cat("Time:",loop[i]," ","p.value :", test$p.value, " ","Statistic:", test$statistic,"Outliers:",outliers$is.outlier,"\n", file=here("Output","t.test_results","Growth_curves","Raoul_Assump_5642b.txt"), append=T) 
  } 
 i=i+1}

i=0 
for(i in 1:4) 
{
Timepoint<-Growth5642b[Growth5642b$Time==loop[i],]
plant<- Timepoint[Timepoint$Treatment=="Plant",]
planto<-plant[order(plant$Pair),]
mirplant<-planto$OD600
scram<- Timepoint[Timepoint$Treatment=="Scramble",]
scramo<-scram[order(scram$Pair),]
mirscram<-scramo$OD600
test<-t.test(mirplant, mirscram, paired = TRUE, alternative = "less")
{
  if(test$p.value < 0.05)
    cat("Time:",loop[i]," ","p.value :", test$p.value, " ","statistic:", test$statistic, "\n", file=here("Output","t.test_results","Growth_curves","Raoul_5642b_t.test_less.txt"), append=T) 
  } 
 i=i+1} #Time 3

#ath-miRMix5
i=0 
for(i in 1:4) 
{
Timepoint<-GrowthMix5[GrowthMix5$Time==loop[i],]
plant<- Timepoint[Timepoint$Treatment=="Plant",]
planto<-plant[order(plant$Pair),]
mirplant<-planto$OD600
scram<- Timepoint[Timepoint$Treatment=="Scramble",]
scramo<-scram[order(scram$Pair),]
mirscram<-scramo$OD600
differences<- as.data.frame(mirscram - mirplant)
outliers<-identify_outliers(differences) 
test<-shapiro_test(differences$`mirscram - mirplant`)
{
  if(nrow(outliers)>=1|test$p.value < 0.05)
    cat("Time:",loop[i]," ","p.value :", test$p.value, " ","Statistic:", test$statistic,"Outliers:",outliers$is.outlier,"\n", file=here("Output","t.test_results","Growth_curves","Raoul_Assump_Mix5.txt"), append=T) 
  } 
 i=i+1}

i=0 
for(i in 1:4) 
{
Timepoint<-GrowthMix5[GrowthMix5$Time==loop[i],]
plant<- Timepoint[Timepoint$Treatment=="Plant",]
planto<-plant[order(plant$Pair),]
mirplant<-planto$OD600
scram<- Timepoint[Timepoint$Treatment=="Scramble",]
scramo<-scram[order(scram$Pair),]
mirscram<-scramo$OD600
test<-t.test(mirplant, mirscram, paired = TRUE, alternative = "two.sided")
{
  if(test$p.value < 0.05)
    cat("Time:",loop[i]," ","p.value :", test$p.value, " ","statistic:", test$statistic, "\n", file=here("Output","t.test_results","Growth_curves","Raoul_Mix5_t.test.txt"), append=T) 
  } 
 i=i+1} #nothing significant
```


#Growth AUC
```{r}
#ath-miR158a3p
Growth158a3p$Time <- as.numeric(Growth158a3p$Time) 
# Select columns with data for AUC calculation
data_cols <- names(Growth158a3p)[6]  # Adjust to match your data column range
# Group by isolate and block
AUC_Growth_158a3p<- Growth158a3p %>%
  group_by(Pair, Treatment) %>%
  summarise(
    across(all_of(data_cols), ~ calculate_auc(cur_data(), "Time", cur_column()), .names = "AUC_{.col}")
  )

#ath-miR158b
Growth158b$Time <- as.numeric(Growth158b$Time) 
# Select columns with data for AUC calculation
data_cols <- names(Growth158b)[6]  # Adjust to match your data column range
# Group by isolate and block
AUC_Growth_158b<- Growth158b %>%
  group_by(Pair, Treatment) %>%
  summarise(
    across(all_of(data_cols), ~ calculate_auc(cur_data(), "Time", cur_column()), .names = "AUC_{.col}")
  )


#ath-miR159
Growth159$Time <- as.numeric(Growth159$Time) 
# Select columns with data for AUC calculation
data_cols <- names(Growth159)[6]  # Adjust to match your data column range
# Group by isolate and block
AUC_Growth_159<- Growth159 %>%
  group_by(Pair, Treatment) %>%
  summarise(
    across(all_of(data_cols), ~ calculate_auc(cur_data(), "Time", cur_column()), .names = "AUC_{.col}")
  )


#ath-miR827
Growth827$Time <- as.numeric(Growth827$Time) 
# Select columns with data for AUC calculation
data_cols <- names(Growth827)[6]  # Adjust to match your data column range
# Group by isolate and block
AUC_Growth_827<- Growth827 %>%
  group_by(Pair, Treatment) %>%
  summarise(
    across(all_of(data_cols), ~ calculate_auc(cur_data(), "Time", cur_column()), .names = "AUC_{.col}")
  )
t.test(AUC_OD600 ~ Treatment, paired=TRUE, data= AUC_Growth_827, alternative='greater')#p-value = 0.05027

boxAUC_AA_827<-ggplot(AUC_Growth_827, aes(y=AUC_OD600, x=Treatment, fill=Treatment))+
   geom_boxplot(outlier.shape = NA, alpha=0.4, aes(fill=Treatment, color=Treatment )) +
  geom_point(aes(fill=Treatment, color=Treatment),pch = 21, position = position_jitterdodge(0.05))+
  geom_line(aes(group = Pair), color = "grey50", linetype = "solid", alpha = 0.5) +
  theme_classic() +theme(axis.text.x=element_blank())+labs(x="", y="Area under the curve for \n optical density (600 nm)")+
scale_fill_manual(values = c("#003049","#2a7f62"))+
scale_colour_manual(values = c("#003049","#2a7f62"))+
  ggtitle(expression(italic("Raoultella") ~ "ath-miR827"))+
  annotate('text', x = 1.5, y = 1.1, label='p = 0.05027', size=4)
boxAUC_AA_827
boxAUC_AA_827_2<-ggpar(boxAUC_AA_827,ylim = c(0.6, 1.2))
boxAUC_AA_827_2



#ath-miR5642b
Growth5642b$Time <- as.numeric(Growth5642b$Time) 
# Select columns with data for AUC calculation
data_cols <- names(Growth5642b)[6]  # Adjust to match your data column range
# Group by isolate and block
AUC_Growth_5642b<- Growth5642b %>%
  group_by(Pair, Treatment) %>%
  summarise(
    across(all_of(data_cols), ~ calculate_auc(cur_data(), "Time", cur_column()), .names = "AUC_{.col}")
  )

#Mix5
GrowthMix5$Time <- as.numeric(GrowthMix5$Time) 
# Select columns with data for AUC calculation
data_cols <- names(GrowthMix5)[6]  # Adjust to match your data column range
# Group by isolate and block
AUC_Growth_Mix5<- GrowthMix5 %>%
  group_by(Pair, Treatment) %>%
  summarise(
    across(all_of(data_cols), ~ calculate_auc(cur_data(), "Time", cur_column()), .names = "AUC_{.col}")
  )
```


#Merging Growth data and consumption data
```{r}

Growth158a3p$Treatment<-recode_factor(Growth158a3p$Treatment, Plant="Plant miRNAs", Scramble= "Scramble miRNAs")

Growth158b$Treatment<-recode_factor(Growth158b$Treatment, Plant="Plant miRNAs", Scramble= "Scramble miRNAs")

Growth159$Treatment<-recode_factor(Growth159$Treatment, Plant="Plant miRNAs", Scramble= "Scramble miRNAs")

Growth827$Treatment<-recode_factor(Growth827$Treatment, Plant="Plant miRNAs", Scramble= "Scramble miRNAs")

Growth5642b$Treatment<-recode_factor(Growth5642b$Treatment, Plant="Plant miRNAs", Scramble= "Scramble miRNAs")

GrowthMix5$Treatment<-recode_factor(GrowthMix5$Treatment, Plant="Plant miRNAs", Scramble= "Scramble miRNAs")
GrowthMix5$miRNA <- recode_factor(GrowthMix5$miRNA, Mix5="Mix of 5")
AARaoul_mixmiR5$miRNA<- recode_factor(AARaoul_mixmiR5$miRNA, Mix5="Mix of 5")

# Define the desired column order
columns <- c("Time", "miRNA", "Treatment", "Pair")

#ath-miR158a-3p
# Reorder columns in both dataframes
Growth158a3p <- Growth158a3p[, c(columns, setdiff(names(Growth158a3p), columns))]
AARaoul_158a3p <- AARaoul_158a3p[, c(columns, setdiff(names(AARaoul_158a3p),columns))]
# Merge the dataframes
All158a3p <- merge(Growth158a3p, AARaoul_158a3p, by = c("Time", "miRNA", "Pair", "Treatment"), all = TRUE) 

#ath-miR158b
# Reorder columns in both dataframes
Growth158b <- Growth158b[, c(columns, setdiff(names(Growth158b), columns))]
AARaoul_158b <- AARaoul_158b[, c(columns, setdiff(names(AARaoul_158b),columns))]
# Merge the dataframes
All158b <- merge(Growth158b, AARaoul_158b, by = c("Time", "miRNA", "Pair", "Treatment"), all = TRUE) 

# Reorder columns in both dataframes
Growth159 <- Growth159[, c(columns, setdiff(names(Growth159), columns))]
AARaoul_159 <- AARaoul_159[, c(columns, setdiff(names(AARaoul_159),columns))]
# Merge the dataframes
All159 <- merge(Growth159, AARaoul_159, by = c("Time", "miRNA", "Pair", "Treatment"), all = TRUE) 

# Reorder columns in both dataframes
Growth827 <- Growth827[, c(columns, setdiff(names(Growth827), columns))]
AARaoul_827 <- AARaoul_827[, c(columns, setdiff(names(AARaoul_827),columns))]
# Merge the dataframes
All827 <- merge(Growth827, AARaoul_827, by = c("Time", "miRNA", "Pair", "Treatment"), all = TRUE) 

#ath-miR5642b
# Reorder columns in both dataframes
Growth5642b <- Growth5642b[, c(columns, setdiff(names(Growth5642b), columns))]
AARaoul_5642b <- AARaoul_5642b[, c(columns, setdiff(names(AARaoul_5642b),columns))]
# Merge the dataframes
All5642b <- merge(Growth5642b, AARaoul_5642b, by = c("Time", "miRNA", "Pair", "Treatment"), all = TRUE)

# Mix of 5 
# Reorder columns in both dataframes
GrowthMix5 <- GrowthMix5[, c(columns, setdiff(names(GrowthMix5), columns))]
AARaoul_mixmiR5 <- AARaoul_mixmiR5[, c(columns, setdiff(names(AARaoul_mixmiR5),columns))]
# Merge the dataframes
AllMix5 <- merge(GrowthMix5, AARaoul_mixmiR5, by = c("Time", "miRNA", "Pair", "Treatment"), all = TRUE)

```


#Dual Y axis ath-miR158a3p
```{r}
coeff<- 40000

# Create a new variable to group color and linetype together
All158a3p$Treatment2 <- factor(All158a3p$Treatment, levels = c("Plant miRNAs", "Scramble miRNAs"))

boxRaoul158a3p<- ggplot(All158a3p) +
  # First plot for OD600: Line, Points, and Error bars with color and linetype based on Treatment2
  stat_summary(mapping = aes(x = Time, y = OD600, color = Treatment2, group = Treatment2, linetype = Treatment2), 
               fun = mean, geom = 'line', position = position_dodge(0.2)) +
  stat_summary(mapping = aes(x = Time, y = OD600, color = Treatment2, group = Treatment2), 
               fun = mean, geom = 'point', position = position_dodge(0.2)) +
  stat_summary(mapping = aes(x = Time, y = OD600, color = Treatment2, group = Treatment2), 
               fun.data = mean_cl_boot, geom = 'errorbar', width = 0.1, position = position_dodge(0.2)) +
  
  # Adding data of AA consumption
  stat_summary(mapping = aes(x = Time, y = Mean_Predicted_AA / coeff, group = Treatment2, linetype = Treatment2), 
               fun = mean, geom = 'line', position = position_dodge(0.2)) +
  stat_summary(mapping = aes(x = Time, y = Mean_Predicted_AA / coeff, group = Treatment2), 
               fun = mean, geom = 'point', position = position_dodge(0.2)) +
  stat_summary(mapping = aes(x = Time, y = Mean_Predicted_AA / coeff, group = Treatment2), 
               fun.data = mean_cl_boot, geom = 'errorbar', width = 0.1, position = position_dodge(0.2)) +
  
  # Customize linetypes and colors for Treatment2
  scale_linetype_manual(name = "Treatment", values = c("solid", "twodash")) +  # Solid for Plant miRNAs, dashed for Scramble miRNAs
  scale_color_manual(name = "Treatment", values = c("darkslategray4", "lightcyan3")) +  # darkslategray4 for Plant miRNAs, lightcyan3 for Scramble miRNAs
  
  # Adjust y-axis and add a secondary axis
  scale_y_continuous(name = "", sec.axis = sec_axis(~ . * coeff, name = "")) +
  
  # Add labels and adjust legend
  labs(x = "Time (hours)", color = "", fill = "", group = "", linetype = "Treatment", shape = "") +
  
  # Apply clean theme
  theme_pubr() + 
  theme(axis.text.y = element_text(color = "darkslategray4"),
        axis.text.y.right = element_text(color = "black"),
        legend.title = element_text(size = 12),
        legend.text = element_text(size = 12)) +
  ggtitle(expression(italic("Raoultella") ~ "ath-miR158a3p")) +
  theme(plot.title = element_text(hjust = 0.005, size = 14)) + 
  theme(legend.position = "bottom") + 
  annotate("text", x = 4, y = 0.22, label = "*", size = 10) + 
  
  # Merge the color and linetype legends together
  guides(color = guide_legend(order = 1), 
         linetype = guide_legend(order = 1))

  # Adjust the plot appearance further
  grow_consume158a3p<-ggpar( boxRaoul158a3p,ylim = c(0.0, 0.5))
    
  # Add annotations for axes
  grow_consume158a3p_2<-annotate_figure( grow_consume158a3p,
           bottom = text_grob("", size = 12),
            left = text_grob("Optical density (600 nm)",size = 12, rot=90, color = "darkslategray4"),
          right= text_grob("L-amino acid concentration (M)",size = 12, rot=270))
    grow_consume158a3p_2
    
     ggsave(grow_consume158a3p_2, file=here("Output","Figures","Raoul_grow_consume158a3p.tiff"),width = 15, height = 15, units = "cm", compression='lzw')
     
     grow_consume158a3p_3<-grow_consume158a3p+theme(legend.position = "none")
saveRDS(grow_consume158a3p_3, file = here("Output","Figures","Raoul_grow_consume158a3p.rds"))   
```
  



#Dual Y axis ath-miR158b
```{r}
coeff<- 40000
# Create a new variable to group color and linetype together
All158b$Treatment2 <- factor(All158b$Treatment, levels = c("Plant miRNAs", "Scramble miRNAs"))

boxRaoul158b<- ggplot(All158b) +
  # First plot for OD600: Line, Points, and Error bars with color and linetype based on Treatment2
  stat_summary(mapping = aes(x = Time, y = OD600, color = Treatment2, group = Treatment2, linetype = Treatment2), 
               fun = mean, geom = 'line', position = position_dodge(0.2)) +
  stat_summary(mapping = aes(x = Time, y = OD600, color = Treatment2, group = Treatment2), 
               fun = mean, geom = 'point', position = position_dodge(0.2)) +
  stat_summary(mapping = aes(x = Time, y = OD600, color = Treatment2, group = Treatment2), 
               fun.data = mean_cl_boot, geom = 'errorbar', width = 0.1, position = position_dodge(0.2)) +
  
  # Adding data of AA consumption
  stat_summary(mapping = aes(x = Time, y = Mean_Predicted_AA / coeff, group = Treatment2, linetype = Treatment2), 
               fun = mean, geom = 'line', position = position_dodge(0.2)) +
  stat_summary(mapping = aes(x = Time, y = Mean_Predicted_AA / coeff, group = Treatment2), 
               fun = mean, geom = 'point', position = position_dodge(0.2)) +
  stat_summary(mapping = aes(x = Time, y = Mean_Predicted_AA / coeff, group = Treatment2), 
               fun.data = mean_cl_boot, geom = 'errorbar', width = 0.1, position = position_dodge(0.2)) +
  
  # Customize linetypes and colors for Treatment2
  scale_linetype_manual(name = "Treatment", values = c("solid", "twodash")) +  # Solid for Plant miRNAs, dashed for Scramble miRNAs
  scale_color_manual(name = "Treatment", values = c("darkslategray4", "lightcyan3")) +  # darkslategray4 for Plant miRNAs, lightcyan3 for Scramble miRNAs
  
  # Adjust y-axis and add a secondary axis
  scale_y_continuous(name = "", sec.axis = sec_axis(~ . * coeff, name = "")) +
  
  # Add labels and adjust legend
  labs(x = "Time (hours)", color = "", fill = "", group = "", linetype = "Treatment", shape = "") +
  
  # Apply clean theme
  theme_pubr() + 
  theme(axis.text.y = element_text(color = "darkslategray4"),
        axis.text.y.right = element_text(color = "black"),
        legend.title = element_text(size = 12),
        legend.text = element_text(size = 12)) +
  ggtitle(expression(italic("Raoultella") ~ "ath-miR158b")) +
  theme(plot.title = element_text(hjust = 0.005, size = 14)) + 
  theme(legend.position = "bottom") + 
  annotate("text",x=1.05,y=0.48,label="*", size = 10)  + 
  
  # Merge the color and linetype legends together
  guides(color = guide_legend(order = 1), 
         linetype = guide_legend(order = 1))

  # Adjust the plot appearance further
  grow_consume158b<-ggpar( boxRaoul158b,ylim = c(0.0, 0.5))
    
  # Add annotations for axes
  grow_consume158b_2<-annotate_figure( grow_consume158b,
           bottom = text_grob("", size = 12),
            left = text_grob("Optical density (600 nm)",size = 12, rot=90, color = "darkslategray4"),
          right= text_grob("L-amino acid concentration (M)",size = 12, rot=270))
    grow_consume158b_2

    ggsave(grow_consume158b_2, file=here("Output","Figures","Raoul_grow_consume158b.tiff"),width = 15, height = 15, units = "cm", compression='lzw')
    
 grow_consume158b_3<-grow_consume158b+theme(legend.position = "none")
 saveRDS(grow_consume158b_3, file = here("Output","Figures","Raoul_grow_consume158b.rds"))   

```

#Dual Y axis ath-miR159
```{r}
coeff<- 40000
boxRaoul159<- ggplot(All159) +
    stat_summary(mapping=aes(x=Time, y=OD600,color=Treatment,group=Treatment, linetype =Treatment),fun = mean,geom='line',position = position_dodge(0.2)) +
    stat_summary(mapping=aes(x=Time, y=OD600,color=Treatment,group=Treatment), fun=mean,geom='point',position = position_dodge(0.2))+
  stat_summary(mapping=aes(x=Time, y=OD600,color=Treatment,group=Treatment),fun.data=mean_cl_boot,
        geom='errorbar',
        width=0.1,position = position_dodge(0.2))+
  #Adding data of AA consumption
  stat_summary(mapping=aes(x=Time, y=Mean_Predicted_AA/coeff,group=Treatment,linetype=Treatment),fun = mean,geom='line',position = position_dodge(0.2)) +
    stat_summary(mapping=aes(x=Time, y=Mean_Predicted_AA/coeff,group=Treatment),fun=mean,geom='point',position = position_dodge(0.2))+
  stat_summary(mapping=aes(x=Time, y=Mean_Predicted_AA/coeff,group=Treatment),fun.data=mean_cl_boot,geom='errorbar',width=0.1,position = position_dodge(0.2))+
  scale_linetype_manual(name = "Treatement",values=c("solid", "twodash"))+
  scale_y_continuous(name="", sec.axis = sec_axis(~.*coeff,name="")) +
  scale_color_manual(name="",values = c("darkslategray4","lightcyan3"))+
  labs(x = "", color="",fill="", group="",linetype="Treatement", shape="")+
 theme_pubr()+theme( axis.text.y = element_text(color = "darkslategray4"),
    axis.text.y.right = element_text(color = "black"),
  legend.title = element_text(size=18),
   legend.text = element_text(size=18)
  )+ggtitle("Raoultella ath-miR159")+theme(plot.title = element_text(hjust = 0.005, size=20))+ theme(legend.position = "none")   
  grow_consume159<-ggpar( boxRaoul159,ylim = c(0.0, 0.5))
  
  grow_consume159<-annotate_figure( grow_consume159,
           bottom = text_grob("Time (hours)", size = 12),
            left = text_grob("Optical density (600 nm)",size = 12, rot=90, color = "darkslategray4"),
          right= text_grob("L-amino acid concentration (M)",size = 12, rot=270))
    grow_consume159
```

#Dual Y axis ath-miR827
```{r}
coeff<- 40000
boxRaoul827<- ggplot(All827) +
    stat_summary(mapping=aes(x=Time, y=OD600,color=Treatment,group=Treatment, linetype =Treatment),fun = mean,geom='line',position = position_dodge(0.2)) +
    stat_summary(mapping=aes(x=Time, y=OD600,color=Treatment,group=Treatment), fun=mean,geom='point',position = position_dodge(0.2))+
  stat_summary(mapping=aes(x=Time, y=OD600,color=Treatment,group=Treatment),fun.data=mean_cl_boot,
        geom='errorbar',
        width=0.1,position = position_dodge(0.2))+
  #Adding data of AA consumption
  stat_summary(mapping=aes(x=Time, y=Mean_Predicted_AA/coeff,group=Treatment,linetype=Treatment),fun = mean,geom='line',position = position_dodge(0.2)) +
    stat_summary(mapping=aes(x=Time, y=Mean_Predicted_AA/coeff,group=Treatment),fun=mean,geom='point',position = position_dodge(0.2))+
  stat_summary(mapping=aes(x=Time, y=Mean_Predicted_AA/coeff,group=Treatment),fun.data=mean_cl_boot,geom='errorbar',width=0.1,position = position_dodge(0.2))+
  scale_linetype_manual(name = "Treatement",values=c("solid", "twodash"))+
  scale_y_continuous(name="", sec.axis = sec_axis(~.*coeff,name="")) +
  scale_color_manual(name="",values = c("darkslategray4","lightcyan3"))+
  labs(x = "", color="",fill="", group="",linetype="Treatement", shape="")+
 theme_pubr()+theme( axis.text.y = element_text(color = "darkslategray4"),
    axis.text.y.right = element_text(color = "black"),
  legend.title = element_text(size=18),
   legend.text = element_text(size=18)
  )+ggtitle("Raoultella ath-miR827")+theme(plot.title = element_text(hjust = 0.005, size=20))+ theme(legend.position = "none")   
  grow_consume827<-ggpar( boxRaoul827,ylim = c(0.0, 0.6))
  
  grow_consume827<-annotate_figure( grow_consume827,
           bottom = text_grob("Time (hours)", size = 12),
            left = text_grob("Optical density (600 nm)",size = 12, rot=90, color = "darkslategray4"),
          right= text_grob("L-amino acid concentration (M)",size = 12, rot=270))
    grow_consume827

```


#Dual Y axis ath-miR5642b
```{r}
coeff2<- 33000

# Create a new variable to group color and linetype together
All5642b$Treatment2 <- factor(All5642b$Treatment, levels = c("Plant miRNAs", "Scramble miRNAs"))

boxRaoul5642b<- ggplot(All5642b) +
  # First plot for OD600: Line, Points, and Error bars with color and linetype based on Treatment2
  stat_summary(mapping = aes(x = Time, y = OD600, color = Treatment2, group = Treatment2, linetype = Treatment2), 
               fun = mean, geom = 'line', position = position_dodge(0.2)) +
  stat_summary(mapping = aes(x = Time, y = OD600, color = Treatment2, group = Treatment2), 
               fun = mean, geom = 'point', position = position_dodge(0.2)) +
  stat_summary(mapping = aes(x = Time, y = OD600, color = Treatment2, group = Treatment2), 
               fun.data = mean_cl_boot, geom = 'errorbar', width = 0.1, position = position_dodge(0.2)) +
  
  # Adding data of AA consumption
  stat_summary(mapping = aes(x = Time, y = Mean_Predicted_AA / coeff2, group = Treatment2, linetype = Treatment2), 
               fun = mean, geom = 'line', position = position_dodge(0.2)) +
  stat_summary(mapping = aes(x = Time, y = Mean_Predicted_AA / coeff2, group = Treatment2), 
               fun = mean, geom = 'point', position = position_dodge(0.2)) +
  stat_summary(mapping = aes(x = Time, y = Mean_Predicted_AA / coeff2, group = Treatment2), 
               fun.data = mean_cl_boot, geom = 'errorbar', width = 0.1, position = position_dodge(0.2)) +
  
  # Customize linetypes and colors for Treatment2
  scale_linetype_manual(name = "Treatment", values = c("solid", "twodash")) +  # Solid for Plant miRNAs, dashed for Scramble miRNAs
  scale_color_manual(name = "Treatment", values = c("darkslategray4", "lightcyan3")) +  # darkslategray4 for Plant miRNAs, lightcyan3 for Scramble miRNAs
  
  # Adjust y-axis and add a secondary axis
  scale_y_continuous(name = "", sec.axis = sec_axis(~ . * coeff2, name = "")) +
  
  # Add labels and adjust legend
  labs(x = "Time (hours)", color = "", fill = "", group = "", linetype = "Treatment", shape = "") +
  
  # Apply clean theme
  theme_pubr() + 
  theme(axis.text.y = element_text(color = "darkslategray4"),
        axis.text.y.right = element_text(color = "black"),
        legend.title = element_text(size = 12),
        legend.text = element_text(size = 12)) +
  ggtitle(expression(italic("Raoultella") ~ "ath-miR5642b")) +
  theme(plot.title = element_text(hjust = 0.005, size = 14)) + 
  theme(legend.position = "bottom") + 
  annotate("text",x=0.95,y=0.49,label="*", size = 10)+
  annotate("text",x=2,y=0.45,label="*", size = 10)+
  annotate("text",x=2,y=0.28,label="*", size = 10, color="darkslategray4") + 
  
  # Merge the color and linetype legends together
  guides(color = guide_legend(order = 1), 
         linetype = guide_legend(order = 1))

  # Adjust the plot appearance further
  grow_consume5642b<-ggpar( boxRaoul5642b,ylim = c(0.0, 0.5))
    
  # Add annotations for axes
  grow_consume5642b_2<-annotate_figure( grow_consume5642b,
           bottom = text_grob("", size = 12),
            left = text_grob("Optical density (600 nm)",size = 12, rot=90, color = "darkslategray4"),
          right= text_grob("L-amino acid concentration (M)",size = 12, rot=270))
    grow_consume5642b_2

    ggsave(grow_consume5642b_2, file=here("Output","Figures","Raoul_grow_consume5642b.tiff"),width = 15, height = 15, units = "cm", compression='lzw')
   
    grow_consume5642b_3<-grow_consume5642b+theme(legend.position = "none")
     saveRDS(grow_consume5642b_3, file = here("Output","Figures","Raoul_grow_consume5642b.rds"))
  
```

#Dual Y axis Mix of 5
```{r}
coeff4<- 37500

# Create a new variable to group color and linetype together
AllMix5$Treatment2 <- factor(AllMix5$Treatment, levels = c("Plant miRNAs", "Scramble miRNAs"))

boxRaoulMix5<- ggplot(AllMix5) +
  # First plot for OD600: Line, Points, and Error bars with color and linetype based on Treatment2
  stat_summary(mapping = aes(x = Time, y = OD600, color = Treatment2, group = Treatment2, linetype = Treatment2), 
               fun = mean, geom = 'line', position = position_dodge(0.2)) +
  stat_summary(mapping = aes(x = Time, y = OD600, color = Treatment2, group = Treatment2), 
               fun = mean, geom = 'point', position = position_dodge(0.2)) +
  stat_summary(mapping = aes(x = Time, y = OD600, color = Treatment2, group = Treatment2), 
               fun.data = mean_cl_boot, geom = 'errorbar', width = 0.1, position = position_dodge(0.2)) +
  
  # Adding data of AA consumption
  stat_summary(mapping = aes(x = Time, y = Mean_Predicted_AA / coeff4, group = Treatment2, linetype = Treatment2), 
               fun = mean, geom = 'line', position = position_dodge(0.2)) +
  stat_summary(mapping = aes(x = Time, y = Mean_Predicted_AA / coeff4, group = Treatment2), 
               fun = mean, geom = 'point', position = position_dodge(0.2)) +
  stat_summary(mapping = aes(x = Time, y = Mean_Predicted_AA / coeff4, group = Treatment2), 
               fun.data = mean_cl_boot, geom = 'errorbar', width = 0.1, position = position_dodge(0.2)) +
  
  # Customize linetypes and colors for Treatment2
  scale_linetype_manual(name = "Treatment", values = c("solid", "twodash")) +  # Solid for Plant miRNAs, dashed for Scramble miRNAs
  scale_color_manual(name = "Treatment", values = c("darkslategray4", "lightcyan3")) +  # darkslategray4 for Plant miRNAs, lightcyan3 for Scramble miRNAs
  
  # Adjust y-axis and add a secondary axis
  scale_y_continuous(name = "", sec.axis = sec_axis(~ . * coeff4, name = "")) +
  
  # Add labels and adjust legend
  labs(x = "Time (hours)", color = "", fill = "", group = "", linetype = "Treatment", shape = "") +
  
  # Apply clean theme
  theme_pubr() + 
  theme(axis.text.y = element_text(color = "darkslategray4"),
        axis.text.y.right = element_text(color = "black"),
        legend.title = element_text(size = 12),
        legend.text = element_text(size = 12)) +
  ggtitle(expression(italic("Raoultella") ~ "mix of 5 miRNAs")) +
  theme(plot.title = element_text(hjust = 0.005, size = 14)) + 
  theme(legend.position = "bottom") + 
  annotate("text",x=4,y=0.22,label="*", size = 10) + 
  
  # Merge the color and linetype legends together
  guides(color = guide_legend(order = 1), 
         linetype = guide_legend(order = 1))

  # Adjust the plot appearance further
  grow_consumeMix5<-ggpar( boxRaoulMix5,ylim = c(0.0, 0.5))
    
  # Add annotations for axes
  grow_consumeMix5_2<-annotate_figure( grow_consumeMix5,
           bottom = text_grob("", size = 12),
            left = text_grob("Optical density (600 nm)",size = 12, rot=90, color = "darkslategray4"),
          right= text_grob("L-amino acid concentration (M)",size = 12, rot=270))
    grow_consumeMix5_2

    ggsave(grow_consumeMix5_2, file=here("Output","Figures","Raoul_grow_consumeMix5.tiff"),width = 15, height = 15, units = "cm", compression='lzw')
    
    grow_consumeMix5_3<-grow_consumeMix5+theme(legend.position = "none")
    saveRDS(grow_consumeMix5_3, file = here("Output","Figures","Raoul_grow_consumeMix5.rds"))

```

