---
title: "Final_Figures"
author: "Jessica A. Dozois"
date: "2024-07-06"
output: html_document
---

------------------------------------------------------------------------

#Loading librairies

```{r Librairies}
install.packages("pacman")
pacman::p_load(data.table,ggplot2,dplyr,here,ggpubr)
```

#Creating folders

```{r}
dir.create(file.path("Output"))

```

#Figure 1 - Relative abundance of the five candidate miRNAs in the roots of A. thaliana

```{r}
miRNAs_5<-readRDS(file=here('Main','Arabidopsis__miRNAs_sig.rds'))

fig1<- ggarrange(miRNAs_5, common.legend = T, font.label=list(color="black",size=14), legend='right')
fig1
ggsave(fig1, filename = here("Output" ,"Fig1.tiff"), compression = "lzw", dpi = 600, device = "tiff", height = 4, width = 10, units = "in")
```



#Figure 2 - miRNA modifies bacterial community growth

```{r}
AUC_sig<-readRDS(file=here('Main', 'AUC_sig.rds'))
fig2 <- AUC_sig
fig2
ggsave(fig2, file=here("Output","Fig2.tiff"),units="cm", width=25, height=15, compression='lzw')

```


#Figure 3 - miRNA modify bacterial composition and L-lysine consumption

```{r}
stack<-readRDS(file=here('Main', 'Bars_mean_10uM.rds'))
ASV_diff<-readRDS(file=here('Main', 'ASVs_sig_stat.rds'))
PCA<-readRDS(file=here('Main', 'PCA_16S_10uM.rds'))
Lys_use<-readRDS(file=here('Main','Lysine_use.rds'))
coeff<-50000
fig3 <- ggarrange(ggarrange(Lys_use,PCA, ncol = 2, labels = c("A", "B")),stack,ASV_diff,
          labels = c("","C","D"),common.legend = F, nrow=3, font.label=list(color="black",size=14))
fig3
ggsave(fig3, filename = here("Output" ,"Fig3.tiff"), compression = "lzw", dpi = 600, device = "tiff", height = 16, width = 13.5, units = "in")
```

#Figure 4 - miRNAs affect how isolates grow and the rate at which they uptake amino acids from the media.

```{r}
Iso_AUC_Growth<-readRDS(file=here('Main', 'Isolates_AUC_Growth.rds'))
fig4<-Iso_AUC_Growth
ggsave(fig4, file=here("Output","Fig4.tiff"),dpi = 600, device = "tiff",units="cm", width = 36, height = 36, compression='lzw')
```

#Figure 5 - Raoultella delayed the germination of Arabidopsis and in time killed the plants

```{r}
Germination<-readRDS(file=here('Main', 'Fig_Arabi_isolates.rds'))
fig5<-Germination
ggsave(fig5, file=here("Output","Fig5.tiff"),dpi = 600, device = "tiff",units="cm", width = 18, height = 18, compression='lzw')
```


#Supplementary figures

##Figure S1 - Relative abundance of the N responding miRNAs in roots

```{r}
miRNAs_N<-readRDS(file=here('Supplementary','N_responding_miRNAs_sig.rds'))
figS1<- miRNAs_N
ggsave(figS1, filename = here("Output" ,"FigS1.tiff"), compression = "lzw", dpi = 600, device = "tiff", height = 10, width = 10, units = "in")
```

##Figure S2 - Relative abundance of the most abundant miRNAs in roots

```{r}
miRNAs_abund<-readRDS(file=here('Supplementary','Arabidopsis_TOP_miRNAs_sig.rds'))
figS2<-ggarrange(miRNAs_abund, common.legend = T, nrow=1, font.label=list(color="black",size=14), legend='right')
figS2

ggsave(figS2, filename = here("Output" ,"FigS2.tiff"), compression = "lzw", dpi = 600, device = "tiff", height = 6, width = 10, units = "in")

```

#Figure S3- Correlations between the relative abundance root miRNAs and bacterial taxa

```{r}
Corr<-readRDS(file=here('Supplementary','All_asv_vs_miRAra.rds'))
figS3<- Corr
figS3
ggsave(figS3, filename = here("Output" ,"FigS3.tiff"), compression = "lzw", dpi = 600, device = "tiff", width = 30, height = 35, units = "cm")
```

##Figure S4 bacterial taxa in the roots of A. thaliana

```{r}
Correlated_ASVs<-readRDS(file=here('Supplementary','ASVs_Endosphere_sig.rds'))
PCA_16S_roots<-readRDS(file=here('Supplementary','PCA_root_16S_plantexp.rds'))

figS4<-ggarrange(Correlated_ASVs,PCA_16S_roots, labels = c("A","B"),common.legend = T,font.label=list(color="black",size=14),ncol=1, legend='right',heights=c(1,0.8))
figS4
ggsave(figS4, filename = here("Output" ,"figS4.tiff"), compression = "lzw", dpi = 600, device = "tiff", height = 12, width = 9, units = "in")
```

##Figure S5 - A mix of 5 miRNAs modify microbial growth

```{r}
Growth_10uM<-readRDS(file = here('Supplementary','L-AA_screen10uM.rds'))

figS5 <- Growth_10uM

ggsave(figS5, filename = here("Output" ,"figS5.tiff"), compression = "lzw", dpi = 600, device = "tiff", height = 20, width = 15, units = "in")
```

##Figure S6 - A single miRNA modifies microbial growth

```{r}
Growth2uM<-readRDS(file = here('Supplementary','L-AA_screen2uM.rds'))

figS6<- Growth2uM

ggsave(figS6, filename = here("Output" ,"figS6.tiff"), compression = "lzw", dpi = 600, device = "tiff", height = 14, width = 14, units = "in")
```

#Figure S7- Amino acid consumption of the simplified microbial community

```{r}
Comm_DualYaxis<-readRDS(file=here('Supplementary', 'All_everymiARN_dualY.rds'))
figS7<-Comm_DualYaxis
figS7
ggsave(figS7, file=here("Output","FigS7.tiff"),width = 40, height = 30, units = "cm")
```


#Figure S8- Shifts in bacterial community composition exposed to single miRNAs

```{r}
StackSinglemiR<-readRDS(file=here('Supplementary', 'Bars_mean_2uM.rds'))
figS8<-StackSinglemiR
figS8
ggsave(figS8, file=here("Output","FigS8.tiff"), width=32, height=12, units = "cm")
```


#Figure S9 - Impact of miRNAs on the growth of isolates 

```{r}
boxASVGrowth<-readRDS(file=here('Supplementary', 'boxisolates_growth_mostsig.rds'))
figS9<-boxASVGrowth
figS9
ggsave(figS9, file=here("Output","FigS9.tiff"),width = 22, height = 18, units = "cm")
```
